### 2019-10-12 Paper/paper.tex
added base draft for paper

\documentclass{article}% use option titlepage to get the title on a page of its own.
\title{Lab 1: Symmetric Encryption}
\date{\today}
\author{Lars Van Roy\\s0161083@ad.ua.ac.be}

\begin{document}
	\maketitle

	\begin{abstract}
		In this paper we will address a set of reachability problems within a subset of c. These problems will be addressed by a set of tools that allow us to convert the code into one counter machines. These one counter machines can be analyzed for dead code as described by Daniel Bundala and Joal Ouaknine. The code itself will first be analyzed by a compiler. This compiler will result in an abstract syntax tree that can be converted into the final one counter machine. The analysis of those one counter machines will not be part of this paper.
	\end{abstract}

	\newpage

	\tableofcontents

	\newpage

	\section{Introduction}
	This paper will give a brief description of the process that is used to generate one counter machines starting from c code. The conversion will start of by making use of a compiler, followed by a sequence of conversions which will eventually result in a one counter machine. These one counter machines can be used to perform dead code analysis as described by Daniel Bundela and Joal Ouaknine.

\end{document}

### 2019-10-12 C_code/array.c
added test suit for first loop

@@ -3,4 +3,6 @@
 int main(){
     char* array = "teststring";
     printf("%c", array[2]);
+
+    char* array = {'a', 'b', 'c'};
 }

### 2019-10-12 C_code/assignments.c

@@ -1,3 +1,4 @@
 int main(){
     int a = (int){'c'};
+    _Alignas(16) int b;
 }

### 2019-10-12 C_code/conditions.c

@@ -1,0 +1,36 @@
+bool main(){
+    int x = 0;
+    int y = 0;
+    for((x(0)); x < 10; x ++){
+        y ++;
+    }
+    for(x=5, x=3;x<20; ++x){
+        --y;
+    }
+
+    LOOP: for(void x();x<5; x++){
+        goto Loop;
+    }
+
+    if(x > 20 && x >= 10 || y <= 25){
+        return false;
+    }
+
+    if(x == 5 && y != 10){
+        return true;
+    }
+
+    if(x & 5 && y | 4 && y ^ 5){
+        return true;
+    }
+
+    int a = true ? x : y;
+
+    a *= 5;
+
+    _Static_assert(0, "lalala");
+
+    do {a++;} while (a < 300);
+
+    return true;
+}

### 2019-10-12 C_code/function_calls.c

@@ -2,5 +2,5 @@ int main(){
     a(5, 4);
 }
 
-void a(int b, int c){
+inline void a(int b, int c){
 }

### 2019-10-12 C_code/generic.c

@@ -3,11 +3,7 @@ int main(void)
 {
     // _Generic keyword acts as a switch that chooses
     // operation based on data type of argument.
-    printf("%d\n", _Generic( 1.0L, float:1, double:2,
-                            long double:3, default:0));
-    printf("%d\n", _Generic( 1L, float:1, double:2,
-                            long double:3, default:0));
-    printf("%d\n", _Generic( 1.0L, float:1, double:2,
+    printf("%d\n", _Generic( 1.0L, float:1, double (*):2,
                                       long double:3));
     return 0;
 }

### 2019-10-12 C_code/operations.c

@@ -1,8 +1,9 @@
 int main(){
-    int a = 2;
-    int b = 3;
+    _Atomic(int) a = 2;
+    auto b = 3;
+    int c, d = 4;
 
-    int c = a*b;
+    int * const volatile c = a*b;
     int d = c/b;
     int e = d%c;
 

### 2019-10-12 C_code/simple_for.c

@@ -1,14 +1,0 @@
-bool main(){
-    int x = 0;
-    int y = 0;
-    for((x(0)); x < 10; x ++){
-        y ++;
-    }
-    for(;x<20; ++x){
-        --y;
-    }
-    if(x > 20 && x >= 10 || y <= 25){
-        return False;
-    }
-    return true;
-}

### 2019-10-12 C_code/structs.c

@@ -1,11 +1,27 @@
-struct TestClass{
-int value;
-double value2;
-};
+struct TestStruct{
+    int value       :8;
+    double value2   :32;
+} instance5, instance6;
+
+enum TestEnum {val1, val2 = 0};
+
+union Data {
+    int value;
+    double value2;
+}
 
 int main(){
-    struct TestClass instance;
-    struct TestClass* instance2 = &instance;
+    int a,b;
+    struct TestStruct instance, instance7;
+    struct TestStruct* instance2 = &instance;
+    struct TestStruct instane7 = {.value .value2 = 5};
+
+    enum TestEnum instance3(a, b);
+
+    union Data instance4;
+
+    customfloat f = 5.0;
+    __typeof__(f) g;
 
     instance.value = 5;
     instance2->value2 = 5.3;

### 2019-10-12 C_code/switch.c

@@ -1,0 +1,11 @@
+int main(){
+    int a;
+    switch(a) {
+        case 5:
+            return 5;
+        case 3:
+            return 3;
+        default:
+            return 3;
+    }
+}

### 2019-10-12 Tree/ASTConstructor.py

@@ -153,14 +153,6 @@ class ASTConstructor(CListener):
                     self.grow_on_index("++", ctx, -1)
                 elif ctx.MinusMinus():
                     self.grow_on_index("--", ctx, -1)
-            else:
-                if ctx.LeftParen():
-                    self.grow_on_index("(", ctx, 0)
-                    self.grow_on_index(")", ctx, 2)
-                    self.grow_on_index("{", ctx, 3)
-                    self.grow_on_index("}", ctx, -1)
-                if ctx.Comma():
-                    self.grow_on_index(",", ctx, -2)
 
             self.__node_stack.pop(0)
 
@@ -183,8 +175,6 @@ class ASTConstructor(CListener):
             if ctx.LeftParen() and not ctx.Alignof():
                 self.grow_on_index("(", ctx, -2)
                 self.grow_on_index(")", ctx, -1)
-            if ctx.Identifier():
-                self.grow_tree(str(ctx.Identifier()), ctx)
 
     def exitUnaryExpression(self, ctx: CParser.UnaryExpressionContext):
         top_node = self.__node_stack[0]
@@ -255,7 +245,7 @@ class ASTConstructor(CListener):
             self.__node_stack.pop(0)
 
     def enterRelationalExpression(self, ctx: CParser.RelationalExpressionContext):
-        if not ctx.relationalExpression():
+        if ctx.relationalExpression():
             new_node = self.grow_tree("Relational Expression", ctx)
             self.__node_stack.insert(0, new_node)
 
@@ -273,13 +263,13 @@ class ASTConstructor(CListener):
             self.__node_stack.pop(0)
 
     def enterEqualityExpression(self, ctx: CParser.EqualityExpressionContext):
-        if not ctx.relationalExpression():
+        if ctx.equalityExpression():
             new_node = self.grow_tree("Equality Expression", ctx)
             self.__node_stack.insert(0, new_node)
 
     def exitEqualityExpression(self, ctx: CParser.EqualityExpressionContext):
         top_node = self.__node_stack[0]
-        if type(top_node.get_ctx()) == CParser.EqualityExpressionContext:
+        if type(top_node.get_ctx()) == CParser.EqualityExpressionContext and ctx.equalityExpression():
             if top_node.get_ctx().Equal():
                 self.grow_on_index("==", ctx, 1)
             elif top_node.get_ctx().NotEqual():
[…]

### 2019-10-12 Compiler.py
added platform support for windows and other

@@ -11,6 +11,7 @@ For the software to properly work, the grammars start rule needs to be compilati
 
 import sys
 import os
+import platform
 
 from antlr4 import *
 from Antlr_files.CParser import CParser
@@ -24,8 +25,12 @@ trace = False
 def grammar(grammar_file):
     if not os.path.exists("./Antlr_files"):
         os.mkdir("./Antlr_files")
-    os.system("cd ./Grammar")
-    os.system("java -jar ./antlr.jar -visitor -Dlanguage=Python3 -o ../Antlr_files {}".format(grammar_file))
+    if platform.system() == 'Windows':
+        os.system("cd Grammar&java -jar antlr.jar -visitor -Dlanguage=Python3 -o ../Antlr_files {}"
+                  .format(grammar_file))
+    else:
+        os.system("cd Grammar;java -jar antlr.jar -visitor -Dlanguage=Python3 -o ../Antlr_files {}"
+                  .format(grammar_file))
     return 0
 
 

### 2019-10-12 Compiler.py
added first test suite

@@ -5,7 +5,7 @@ The program consists of two main functionalities being generating the needed cod
   and analyzing c code given the generated code for a grammar
 usage:
     python Compiler.py grammar file.g4
-    python Compiler.py analysis file.c trace=False
+    python Compiler.py analysis file.c trace=False image_output=False
 For the software to properly work, the grammars start rule needs to be compilationUnit
 """
 
@@ -20,6 +20,7 @@ from Antlr_files.CLexer import CLexer
 from Tree.ASTConstructor import ASTConstructor
 
 trace = False
+image_output = False
 
 
 def grammar(grammar_file):
@@ -68,7 +69,8 @@ def analysis(code_file):
     f.write(ast.to_dot())
     f.close()
 
-    os.system("dot -Tpng output.dot -o temp.png")
+    if image_output:
+        os.system("dot -Tpng output.dot -o temp.png")
 
     if trace:
         print("AST generation finished.")

### 2019-10-12 Tests/FirstLoopTests.py

@@ -1,0 +1,73 @@
+import unittest
+
+from Compiler import analysis
+
+
+class TestCases(unittest.TestCase):
+    def test_array(self):
+        analysis("./C_code/array.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/array.dot') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_assignments(self):
+        analysis("./C_code/assignments.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/assignments.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_conditions(self):
+        analysis("./C_code/conditions.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/conditions.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_function_calls(self):
+        analysis("./C_code/function_calls.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/function_calls.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_generic(self):
+        analysis("./C_code/generic.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/generic.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_operations(self):
+        analysis("./C_code/operations.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/operations.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_structs(self):
+        analysis("./C_code/structs.c")
+        with open('output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('Tests/ExpectedOutput/structs.dot', 'r') as myFile:
[…]

### 2019-10-12 Tests/MainTestSuite.py

@@ -1,0 +1,6 @@
+import unittest
+
+from Tests import FirstLoopTests
+
+suite = unittest.TestLoader().loadTestsFromModule(FirstLoopTests)
+unittest.TextTestRunner(verbosity=2).run(suite)

### 2019-10-12 Antlr_files/CLexer.py
added antlr files

@@ -1,0 +1,849 @@
+# Generated from ./C.g4 by ANTLR 4.7.2
+from antlr4 import *
+from io import StringIO
+from typing.io import TextIO
+import sys
+
+
+
+def serializedATN():
+    with StringIO() as buf:
+        buf.write("\3\u608b\ua72a\u8133\ub9ed\u417c\u3be7\u7786\u5964\2t")
+        buf.write("\u0521\b\1\4\2\t\2\4\3\t\3\4\4\t\4\4\5\t\5\4\6\t\6\4\7")
+        buf.write("\t\7\4\b\t\b\4\t\t\t\4\n\t\n\4\13\t\13\4\f\t\f\4\r\t\r")
+        buf.write("\4\16\t\16\4\17\t\17\4\20\t\20\4\21\t\21\4\22\t\22\4\23")
+        buf.write("\t\23\4\24\t\24\4\25\t\25\4\26\t\26\4\27\t\27\4\30\t\30")
+        buf.write("\4\31\t\31\4\32\t\32\4\33\t\33\4\34\t\34\4\35\t\35\4\36")
+        buf.write("\t\36\4\37\t\37\4 \t \4!\t!\4\"\t\"\4#\t#\4$\t$\4%\t%")
+        buf.write("\4&\t&\4\'\t\'\4(\t(\4)\t)\4*\t*\4+\t+\4,\t,\4-\t-\4.")
+        buf.write("\t.\4/\t/\4\60\t\60\4\61\t\61\4\62\t\62\4\63\t\63\4\64")
+        buf.write("\t\64\4\65\t\65\4\66\t\66\4\67\t\67\48\t8\49\t9\4:\t:")
+        buf.write("\4;\t;\4<\t<\4=\t=\4>\t>\4?\t?\4@\t@\4A\tA\4B\tB\4C\t")
+        buf.write("C\4D\tD\4E\tE\4F\tF\4G\tG\4H\tH\4I\tI\4J\tJ\4K\tK\4L\t")
+        buf.write("L\4M\tM\4N\tN\4O\tO\4P\tP\4Q\tQ\4R\tR\4S\tS\4T\tT\4U\t")
+        buf.write("U\4V\tV\4W\tW\4X\tX\4Y\tY\4Z\tZ\4[\t[\4\\\t\\\4]\t]\4")
+        buf.write("^\t^\4_\t_\4`\t`\4a\ta\4b\tb\4c\tc\4d\td\4e\te\4f\tf\4")
[…]

### 2019-10-12 Antlr_files/CListener.py

@@ -1,0 +1,793 @@
+# Generated from ./C.g4 by ANTLR 4.7.2
+from antlr4 import *
+if __name__ is not None and "." in __name__:
+    from .CParser import CParser
+else:
+    from CParser import CParser
+
+# This class defines a complete listener for a parse tree produced by CParser.
+class CListener(ParseTreeListener):
+
+    # Enter a parse tree produced by CParser#primaryExpression.
+    def enterPrimaryExpression(self, ctx:CParser.PrimaryExpressionContext):
+        pass
+
+    # Exit a parse tree produced by CParser#primaryExpression.
+    def exitPrimaryExpression(self, ctx:CParser.PrimaryExpressionContext):
+        pass
+
+
+    # Enter a parse tree produced by CParser#genericSelection.
+    def enterGenericSelection(self, ctx:CParser.GenericSelectionContext):
+        pass
+
+    # Exit a parse tree produced by CParser#genericSelection.
+    def exitGenericSelection(self, ctx:CParser.GenericSelectionContext):
+        pass
+
+
+    # Enter a parse tree produced by CParser#genericAssocList.
+    def enterGenericAssocList(self, ctx:CParser.GenericAssocListContext):
+        pass
+
+    # Exit a parse tree produced by CParser#genericAssocList.
+    def exitGenericAssocList(self, ctx:CParser.GenericAssocListContext):
+        pass
+
+
+    # Enter a parse tree produced by CParser#genericAssociation.
+    def enterGenericAssociation(self, ctx:CParser.GenericAssociationContext):
+        pass
+
+    # Exit a parse tree produced by CParser#genericAssociation.
+    def exitGenericAssociation(self, ctx:CParser.GenericAssociationContext):
+        pass
+
+
+    # Enter a parse tree produced by CParser#postfixExpression.
+    def enterPostfixExpression(self, ctx:CParser.PostfixExpressionContext):
+        pass
+
+    # Exit a parse tree produced by CParser#postfixExpression.
+    def exitPostfixExpression(self, ctx:CParser.PostfixExpressionContext):
+        pass
+
+
+    # Enter a parse tree produced by CParser#argumentExpressionList.
+    def enterArgumentExpressionList(self, ctx:CParser.ArgumentExpressionListContext):
+        pass
+
+    # Exit a parse tree produced by CParser#argumentExpressionList.
[…]

### 2019-10-12 Antlr_files/CVisitor.py

@@ -1,0 +1,448 @@
+# Generated from ./C.g4 by ANTLR 4.7.2
+from antlr4 import *
+if __name__ is not None and "." in __name__:
+    from .CParser import CParser
+else:
+    from CParser import CParser
+
+# This class defines a complete generic visitor for a parse tree produced by CParser.
+
+class CVisitor(ParseTreeVisitor):
+
+    # Visit a parse tree produced by CParser#primaryExpression.
+    def visitPrimaryExpression(self, ctx:CParser.PrimaryExpressionContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#genericSelection.
+    def visitGenericSelection(self, ctx:CParser.GenericSelectionContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#genericAssocList.
+    def visitGenericAssocList(self, ctx:CParser.GenericAssocListContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#genericAssociation.
+    def visitGenericAssociation(self, ctx:CParser.GenericAssociationContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#postfixExpression.
+    def visitPostfixExpression(self, ctx:CParser.PostfixExpressionContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#argumentExpressionList.
+    def visitArgumentExpressionList(self, ctx:CParser.ArgumentExpressionListContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#unaryExpression.
+    def visitUnaryExpression(self, ctx:CParser.UnaryExpressionContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#unaryOperator.
+    def visitUnaryOperator(self, ctx:CParser.UnaryOperatorContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#castExpression.
+    def visitCastExpression(self, ctx:CParser.CastExpressionContext):
+        return self.visitChildren(ctx)
+
+
+    # Visit a parse tree produced by CParser#multiplicativeExpression.
+    def visitMultiplicativeExpression(self, ctx:CParser.MultiplicativeExpressionContext):
[…]

### 2019-10-12 Antlr_files/CLexer.py
fixed some coverage issues, as well as some incorrect output

@@ -8,8 +8,8 @@ import sys
 
 def serializedATN():
     with StringIO() as buf:
-        buf.write("\3\u608b\ua72a\u8133\ub9ed\u417c\u3be7\u7786\u5964\2t")
-        buf.write("\u0521\b\1\4\2\t\2\4\3\t\3\4\4\t\4\4\5\t\5\4\6\t\6\4\7")
+        buf.write("\3\u608b\ua72a\u8133\ub9ed\u417c\u3be7\u7786\u5964\2r")
+        buf.write("\u0509\b\1\4\2\t\2\4\3\t\3\4\4\t\4\4\5\t\5\4\6\t\6\4\7")
         buf.write("\t\7\4\b\t\b\4\t\t\t\4\n\t\n\4\13\t\13\4\f\t\f\4\r\t\r")
         buf.write("\4\16\t\16\4\17\t\17\4\20\t\20\4\21\t\21\4\22\t\22\4\23")
         buf.write("\t\23\4\24\t\24\4\25\t\25\4\26\t\26\4\27\t\27\4\30\t\30")
@@ -32,112 +32,109 @@ def serializedATN():
         buf.write("\4\u008b\t\u008b\4\u008c\t\u008c\4\u008d\t\u008d\4\u008e")
         buf.write("\t\u008e\4\u008f\t\u008f\4\u0090\t\u0090\4\u0091\t\u0091")
         buf.write("\4\u0092\t\u0092\4\u0093\t\u0093\4\u0094\t\u0094\4\u0095")
-        buf.write("\t\u0095\4\u0096\t\u0096\4\u0097\t\u0097\4\u0098\t\u0098")
-        buf.write("\4\u0099\t\u0099\3\2\3\2\3\2\3\2\3\2\3\2\3\2\3\3\3\3\3")
-        buf.write("\3\3\3\3\3\3\3\3\3\3\3\3\4\3\4\3\4\3\4\3\4\3\4\3\4\3\4")
-        buf.write("\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3\5\3")
-        buf.write("\5\3\6\3\6\3\6\3\6\3\6\3\6\3\6\3\6\3\6\3\6\3\6\3\7\3\7")
-        buf.write("\3\7\3\7\3\7\3\7\3\7\3\7\3\7\3\7\3\7\3\b\3\b\3\b\3\b\3")
[…]

### 2019-10-12 Antlr_files/CListener.py

@@ -449,51 +449,6 @@ class CListener(ParseTreeListener):
         pass
 
 
-    # Enter a parse tree produced by CParser#gccDeclaratorExtension.
-    def enterGccDeclaratorExtension(self, ctx:CParser.GccDeclaratorExtensionContext):
-        pass
-
-    # Exit a parse tree produced by CParser#gccDeclaratorExtension.
-    def exitGccDeclaratorExtension(self, ctx:CParser.GccDeclaratorExtensionContext):
-        pass
-
-
-    # Enter a parse tree produced by CParser#gccAttributeSpecifier.
-    def enterGccAttributeSpecifier(self, ctx:CParser.GccAttributeSpecifierContext):
-        pass
-
-    # Exit a parse tree produced by CParser#gccAttributeSpecifier.
-    def exitGccAttributeSpecifier(self, ctx:CParser.GccAttributeSpecifierContext):
-        pass
-
-
-    # Enter a parse tree produced by CParser#gccAttributeList.
-    def enterGccAttributeList(self, ctx:CParser.GccAttributeListContext):
-        pass
-
-    # Exit a parse tree produced by CParser#gccAttributeList.
-    def exitGccAttributeList(self, ctx:CParser.GccAttributeListContext):
-        pass
-
-
-    # Enter a parse tree produced by CParser#gccAttribute.
-    def enterGccAttribute(self, ctx:CParser.GccAttributeContext):
-        pass
-
-    # Exit a parse tree produced by CParser#gccAttribute.
-    def exitGccAttribute(self, ctx:CParser.GccAttributeContext):
-        pass
-
-
-    # Enter a parse tree produced by CParser#nestedParenthesesBlock.
-    def enterNestedParenthesesBlock(self, ctx:CParser.NestedParenthesesBlockContext):
-        pass
-
-    # Exit a parse tree produced by CParser#nestedParenthesesBlock.
-    def exitNestedParenthesesBlock(self, ctx:CParser.NestedParenthesesBlockContext):
-        pass
-
-
     # Enter a parse tree produced by CParser#pointer.
     def enterPointer(self, ctx:CParser.PointerContext):
         pass
@@ -536,15 +491,6 @@ class CListener(ParseTreeListener):
 
     # Exit a parse tree produced by CParser#parameterDeclaration.
     def exitParameterDeclaration(self, ctx:CParser.ParameterDeclarationContext):
-        pass
-
-
[…]

### 2019-10-12 Antlr_files/CVisitor.py

@@ -254,31 +254,6 @@ class CVisitor(ParseTreeVisitor):
         return self.visitChildren(ctx)
 
 
-    # Visit a parse tree produced by CParser#gccDeclaratorExtension.
-    def visitGccDeclaratorExtension(self, ctx:CParser.GccDeclaratorExtensionContext):
-        return self.visitChildren(ctx)
-
-
-    # Visit a parse tree produced by CParser#gccAttributeSpecifier.
-    def visitGccAttributeSpecifier(self, ctx:CParser.GccAttributeSpecifierContext):
-        return self.visitChildren(ctx)
-
-
-    # Visit a parse tree produced by CParser#gccAttributeList.
-    def visitGccAttributeList(self, ctx:CParser.GccAttributeListContext):
-        return self.visitChildren(ctx)
-
-
-    # Visit a parse tree produced by CParser#gccAttribute.
-    def visitGccAttribute(self, ctx:CParser.GccAttributeContext):
-        return self.visitChildren(ctx)
-
-
-    # Visit a parse tree produced by CParser#nestedParenthesesBlock.
-    def visitNestedParenthesesBlock(self, ctx:CParser.NestedParenthesesBlockContext):
-        return self.visitChildren(ctx)
-
-
     # Visit a parse tree produced by CParser#pointer.
     def visitPointer(self, ctx:CParser.PointerContext):
         return self.visitChildren(ctx)
@@ -301,11 +276,6 @@ class CVisitor(ParseTreeVisitor):
 
     # Visit a parse tree produced by CParser#parameterDeclaration.
     def visitParameterDeclaration(self, ctx:CParser.ParameterDeclarationContext):
-        return self.visitChildren(ctx)
-
-
-    # Visit a parse tree produced by CParser#identifierList.
-    def visitIdentifierList(self, ctx:CParser.IdentifierListContext):
         return self.visitChildren(ctx)
 
 

### 2019-10-12 C_code/conditions.c

@@ -1,7 +1,7 @@
 bool main(){
     int x = 0;
     int y = 0;
-    for((x(0)); x < 10; x ++){
+    for(((x(0))); x < 10; x ++){
         y ++;
     }
     for(x=5, x=3;x<20; ++x){
@@ -17,11 +17,19 @@ bool main(){
     }
 
     if(x == 5 && y != 10){
+        continue;
         return true;
     }
 
     if(x & 5 && y | 4 && y ^ 5){
         return true;
+    }
+    else{
+        return false;
+    }
+
+    while(true){
+        break;
     }
 
     int a = true ? x : y;

### 2019-10-12 C_code/function_calls.c

@@ -1,4 +1,4 @@
-int main(){
+__declspec(dllexport) int main()int d; int e;{
     a(5, 4);
 }
 

### 2019-10-12 C_code/generic.c

@@ -4,6 +4,7 @@ int main(void)
     // _Generic keyword acts as a switch that chooses
     // operation based on data type of argument.
     printf("%d\n", _Generic( 1.0L, float:1, double (*):2,
-                                      long double:3));
+                                      long double:3,
+                                      default: 4));
     return 0;
 }

### 2019-10-12 C_code/operations.c

@@ -12,5 +12,7 @@ int main(){
 
     int h = g<<4;
     int i = h>>20;
+
+    int j = i--;
     return 0;
 }

### 2019-10-12 C_code/structs.c

@@ -8,7 +8,7 @@ enum TestEnum {val1, val2 = 0};
 union Data {
     int value;
     double value2;
-}
+};
 
 int main(){
     int a,b;
@@ -27,6 +27,7 @@ int main(){
     instance2->value2 = 5.3;
 
     printf("%d\n", (int)sizeof(instance));
+    printf("%d\n", (int)sizeof(int));
     printf("%d\n", (int) _Alignof(struct TestClass));
 
     return 0;

### 2019-10-12 Compiler.py

@@ -36,9 +36,6 @@ def grammar(grammar_file):
 
 
 def analysis(code_file):
-    """
-        Initial antlr compilation
-    """
     if trace:
         print("Initial antlr compilation started.")
 
@@ -88,10 +85,13 @@ if __name__ == '__main__':
         grammar(file)
 
     elif handler == "analysis":
-        if len(sys.argv) != 3 and len(sys.argv) != 4:
+        if len(sys.argv) != 3 and len(sys.argv) != 4 and len(sys.argv) != 5:
             print("Error: incorrect number of arguments.")
-        elif len(sys.argv) == 4:
+        if len(sys.argv) >= 4:
             trace = sys.argv[3]
+        if len(sys.argv) >= 5:
+            image_output = sys.argv[4]
+
         file = sys.argv[2]
         analysis(file)
 

### 2019-10-12 Tests/FirstLoopTests.py

@@ -1,9 +1,14 @@
 import unittest
 
 from Compiler import analysis
+from Tree.AbstractSyntaxTree import AbstractSyntaxTree
 
 
 class TestCases(unittest.TestCase):
+    def setUp(self):
+        instance = AbstractSyntaxTree
+        instance.node_count = 0
+
     def test_array(self):
         analysis("./C_code/array.c")
         with open('output.dot', 'r') as myFile:

### 2019-10-12 Tree/ASTConstructor.py

@@ -172,14 +172,14 @@ class ASTConstructor(CListener):
             self.__node_stack.insert(0, new_node)
             if not ctx.unaryOperator():
                 self.grow_tree(str(ctx.getChild(0)), ctx)
-            if ctx.LeftParen() and not ctx.Alignof():
-                self.grow_on_index("(", ctx, -2)
-                self.grow_on_index(")", ctx, -1)
 
     def exitUnaryExpression(self, ctx: CParser.UnaryExpressionContext):
         top_node = self.__node_stack[0]
         if type(top_node.get_ctx()) == CParser.UnaryExpressionContext:
             if ctx.Alignof():
+                self.grow_on_index("(", ctx, 1)
+                self.grow_on_index(")", ctx, -1)
+            if ctx.LeftParen() and not ctx.Alignof():
                 self.grow_on_index("(", ctx, 1)
                 self.grow_on_index(")", ctx, -1)
             self.__node_stack.pop(0)
@@ -528,10 +528,12 @@ class ASTConstructor(CListener):
         pass
 
     def enterFunctionSpecifier(self, ctx: CParser.FunctionSpecifierContext):
-        if not ctx.gccAttributeSpecifier():
-            self.grow_tree(str(ctx.getChild(0)), ctx)
+        # if not ctx.gccAttributeSpecifier():
+        #     self.grow_tree(str(ctx.getChild(0)), ctx)
         if ctx.Identifier():
+            self.__node_stack.insert(0, self.grow_tree("function specifier", ctx))
             self.grow_tree(str(ctx.Identifier()), ctx)
+            self.__node_stack.pop(0)
 
     def exitFunctionSpecifier(self, ctx: CParser.FunctionSpecifierContext):
         pass
@@ -555,43 +557,11 @@ class ASTConstructor(CListener):
             self.__node_stack.insert(0, new_node)
         if ctx.Identifier():
             self.grow_tree(str(ctx.Identifier()), ctx)
-        if ctx.DigitSequence():
-            self.grow_tree(str(ctx.DigitSequence()), ctx)
 
     def exitDirectDeclarator(self, ctx: CParser.DirectDeclaratorContext):
         top_node = self.__node_stack[0]
         if type(top_node.get_ctx()) == CParser.DirectDeclaratorContext:
             self.__node_stack.pop(0)
-
-    def enterGccDeclaratorExtension(self, ctx: CParser.GccDeclaratorExtensionContext):
-        pass
-
[…]

### 2019-10-12 Tree/AbstractSyntaxTree.py

@@ -20,9 +20,6 @@ class AbstractSyntaxTree:
             index = len(self.__children)
         self.__children.insert(index, node)
 
-    def get_child_count(self):
-        return len(self.__children)
-
     def get_ctx(self):
         return self.__ctx
 

### 2020-02-15 Documentation/paper.tex
finished program

\documentclass[12pt]{article}

\usepackage{biblatex}
\addbibresource{bibliography.bib}

\usepackage{multicol}

\usepackage{amsfonts}
\usepackage{amsmath}

\usepackage{xcolor}
\usepackage{listings}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
	backgroundcolor=\color{backgroundColour},   
	commentstyle=\color{mGreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{mGray},
	stringstyle=\color{mPurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2,
	language=C
}

\title{Reachability problems for counter automata}
\author{Lars Van Roy\\
\textit{dept. of Mathematics and Computer Science} \\
\textit{University of Antwerp}\\
lars.vanroy@student.uantwerpen.be}
\date{\today}

\begin{document}
\maketitle{}

\begin{abstract}
\noindent
Reachability is a known problem that can heavily affect the efficiency of code. It has been proven that reachability is decidable for one counter timed automata and to exploit this, we will create a program which will convert c code into such automata. In case the code conforms to the restrictions, enforced by the need of it being a one counter automata, a reachability test can be performed, but the latter will not be part of this research.
\end{abstract}

\section{Introduction}
A well known problem in writing code is the reachability of specific lines in set written code. It is often impossible to properly determine whether or not a line of code guarded by a condition statement is going to be reachable in any possible execution of the code. Unreachable code, due to unsatisfiable conditions, is an obvious issue for time restrained environments such as embedded computer systems. In order to upgrade the efficiency of code that is affected by time constraints, or code in general, a proper reachability analysis would be of great use. \newpage

In order to analyze code reachability, we will make use of a property proven by Daniel Bundala and Joal Ouaknine \cite{danialandjoel}, in which they state that reachability is decidable for timed automata with a single parametric clock. Adding the restriction of only allowing a single parametric clock has a big effect on the types of code we can analyse, but is unavoidable, since there is no proof for two counter machines. Three counter machines and up have been proven to be undecidable.

In this paper we will give an overview of a program which will be able to convert c code to such an automaton. The program will go through the following iterations on the path to generating a counter automaton.

\begin{enumerate}
	\item convert c code into a parse tree, using antlr
	\item perform context free reductions on this parse tree
	\item perform context sensitive reductions on this parse tree
	\item validate the resulting parse tree, to be conforming to the code constraints
	\item generate the counter automaton
\end{enumerate}

The c code can at most contain one counter (and preferably exactly one, as zero counter programs are assumed to be trivial when considering reachability). Furthermore, the operations on the counter will be restricted, the counter can only be altered via assignments with parameters or constants, and the counter can only be compared using equality, inequality, strict less than, strict greater than, less than or equal, greater than or equal, and only to paremeters or constants. Furthermore, these parameters can never be altered throughout the duration of the code.

Other then the described code constraint, functions must also have a boolean return type, and integer parameter types (if any) to be converted into a counter automaton.

\section{One counter automata}
The automata used in this project are a specific subset of the generally defined automata. The general definition for an automaton A is given by the tuple (S, $s_0$, $\delta$, F, Op, $\lambda$) where
\begin{itemize}
	\item S is the set of states
	\item $s_0$ is the set of initial states
	\item $\delta$ is the set of edges
	\item F is the set of final states
	\item Op is the set of operations
	\item $\lambda$ is the mapping for every edge to an element of the set of operations
\end{itemize}

A class of automata derived from the general automaton is the class of timed automata. Before we can consider a definition for these automata, we need to introduce a few additional concepts as described Martin Fr\^anzle et al. \cite{informationprocessingletters} and Uli Fahrenberg \cite{higherdimensionaltimedautomata}.

Consider a set of clocks $\chi$, the corresponding set $\phi(\chi)=\{x_1,...,x_n\}$ of clock constraints is generated corresponding to the following grammar $\varphi ::= true | x<k | x = k | x>k | \varphi\land\varphi$. where $k \in \mathbb{N}$ and $x \in \chi$. Hence $\phi(\chi)$ is nothing but a set of constraints based on conjunctions of comparisons with clocks to integers.

A clock valuation is a mapping $v:\chi \rightarrow \mathbb{R}_{\geq 0}$ where $\mathbb{R}_{\geq 0}$ is the set of non-negative real numbers. We denote $\mathbb{R}^{\chi}_{\geq 0}$ as the set of all clock valuations. Furthermore we write $v \models \varphi$ to denote that $v \in \mathbb{R}^{\chi}_{\geq 0}$ satisfies the constraint $\varphi$. We denote by 0 the valuation such that 0(x) = 0 for all $x \in \chi$. Given $t \in \mathbb{R}^{\chi}_{\geq 0}$, we let v+t be the clock valuation such that (v+t)(x) = v(x) + t for all clocks $x \in \chi$. Given $\lambda \subseteq \chi$, let v[$\lambda \leftarrow 0$] be the clock valuation such that
\[
	v[\lambda \leftarrow 0](x) = 
	\begin{cases}
		0,& \text{if } x \in \lambda\\
		v(x),& \text{if } x \notin \lambda
	\end{cases}
\]
A timed automaton B is defined by a tuple B = $(Q, q^0, Q^f, I, E)$, where
\begin{itemize}
	\item $Q$ is a finite set of locations
	\item $q^0$ represents the initial location, $q^0 \in Q$
	\item $Q^f$ represents the set of accepting locations, $Q^f \subseteq Q$
	\item $I$ assigns invariants to states, $I: Q \rightarrow \phi(\chi)$
	\item $E$ is the set of guarded transitions, $E \subseteq Q$ x $\phi(\chi)$ x $\Sigma$ x $2^\chi$ x $Q$
\end{itemize}

A run in a timed automaton is a sequence $\pi$ of configurations $c_1c_2 ... c_k$ such that each configuration is a direct successor of the previous configuration or, in other words, $c_i \rightarrow c_{i+1}$. We call a run accepting \textsl{accepting} if for a run $c_1c_2...c_k$ it holds that $c_1$ is the initial state and $c_k$ is the final state.

A one-counter automaton is a tuple $\mathcal{A}$ = $(Q, q_0, \sigma, F)$ where
\begin{itemize}
	\item $Q$ is a finite set of states
	\item $q_0 \in Q$ is the initial state
	\item $F \subseteq Q$ is the set of accepting states
	\item $\sigma \subseteq Q $ x $ L $ x $ Q $ is the transition relation with L the set of instructions
\end{itemize}

A counter valuation v is an element of $\mathbb{N}$ and a configuration of $\mathcal{A}$ is a pair in Q x $\mathbb{N}$. The initial configuration is the pair ($q_i$, 0).

Finally, we will consider the following set of allowed operations where P is the set of parameters, the $\wedge$ symbol will be used to represent an empty label.
\[
 op = \{+c, -c, +p, -p, \leq c, =c, \geq c, \leq p, =p, \geq p: c \in \mathbb{N}, p \in P\} \cup \{\wedge\}
\]

The automata we will consider will be one-counter automata. The set $Q$ will contain a state for each line of code. The initial state $q_0$ will be the state corresponding with the first line of code. For now the set of final states $F$ will be empty, but the intended definition of the final state is the line(s) of which the reachability will be checked. The transition relation will consist of elements of the form $(q_i, l, q_{i+1})$ where $q_i, q_{i+1} \in Q$ and $l \in op$. For each element it will hold that we can reach line $q_{i+1}$ from $q_i$. The l element or operation can either be blank, in which case there is a statement on line $q_i$ but it has no effect on the evaluation of our counter and will therefore be disregarded, or not blank. The operation will always be part of the \textit{op} set described earlier.

There are a few exception to the above described states, some segments will have additional nodes to avoid confusion. In a loop there can be a pre loop, which will signify the state after the initial \textit{for condition} is performed, a start node for the inner segment, an end node to the inner segment, a post loop node, that will signify the state after the post statement has been evaluated, and finally a \textit{post iteration node}, which will signify the end of the statements. Same holds for selection statements (eg. if statements) which will have a start node, a start of success node, which signifies the body of the if statement, a start of else node, which will signify possible if else or else statements, and an end of selection node. Other states can be added for statements that require multiple steps, like assignments etc. These will be further explained in the generator section.
\subsection{division example}
Consider the following code segment, this code snippet will attempt to determine whether or not a given integer a, is greater or equal compared to a given integer b. Throughout the paper, the different steps will be described which will ultimately yield the automaton displayed in figure \ref{fig:greater_or_equal}.

\begin{lstlisting}[style=CStyle]
bool is_greater_or_equal(int a, int b){
	if(a >= b){
		return true;
	}
	return false;
}
\end{lstlisting}

\begin{figure}[h]
	\includegraphics[width=\linewidth]{is_greater_or_equal_counter_automaton}
	\caption{A counter automaton corresponding with the is\_greater\_or\_equal function.}
	\label{fig:greater_or_equal}
\end{figure}

This example automaton $\mathcal{A}$ is defined by the tuple $(Q, q_0, \sigma, F)$, where
\begin{align*}
	Q &= \{1, 1.97, 1.98, 1.99, 2, 2.01, 2.02, 2.03, 2.04, 3, 5\} \\
	q_0 &= 1 \\
	\sigma &= \left\{ \begin{array}{l}
		(1, \wedge, 1.97), (1.97, \text{\textless =a}, 1.98), (1.98, \text{+1}, 1.98), (1.98, \text{=a}, 2), \\
		(1.97, \text{\textgreater =a}, 1.99), (1.99, \text{-1}, 1.99), (1.99, \text{=a}, 2), (2, \text{\textgreater =b}, 2.01),\\ (2.01, \wedge, 3), (2, \text{+1}, 2.03), (2.03, \text{\textless =b}, 2.04), (2.04, \text{-1}, 2.02),\\ (2.04, \wedge, 5)
	\end{array} \right\}\\
	F &= \emptyset
\end{align*}

\section{Program}
\subsection{Program overview}
The program that will perform the conversion from c code to a one counter automaton, will do this in five steps.

The first step, the initialization, will simply generate a parse tree, using the default c grammar, with the addition of the boolean type, and the removal of some gcc extensions.

The second step, the context-free abstract syntax tree generation, will generate an abstract syntax tree without any regard for neighboring nodes.

In the third step, the abstract syntax tree generated in the previous step will be simplified in a context-sensitive manner, which means that the program will now look at all neighboring nodes. All redundant nodes will be removed, so that only important nodes with unambiguous meaning remain.

The fourth step will be an analysis on whether or not the resulting abstract syntax tree conforms to all earlier specified requirements and, if this is the case, we will continue with the fifth step, which will be the generation of the counter automaton.

We will allow all counter operations that can directly be supported by the $op$ set described earlier. We will add assignment and inequality to this, as these can easily be represented as sequences of operations in the $op$ list. Along with these we will also need support for strict less than and greater than, which can also be implemented using the operations in the \textit{op} list. The full explanation on how this can be done, can be found in the generator section.

\subsection{Initialization}
The program will start of by running the generator antlr compilation unit on the given c code. In case there are any issues regarding simple compilation rules, the program will exit with an error, indicating the issues in the code. For the remainder of the execution, the code is assumed to be correct, and there will be no regard for potential issues within the code.

\subsection{Context-free abstract syntax tree generation}
Using the parse tree resulting from the antlr compilation, we will try to generate an abstract syntax tree that is as simple as possible without regarding any context.

First of all, the code uses the notion of a node stack, this node stack will be used to store the nodes that are currently being evaluated.

The first loop will operate as a visitor, which will traverse the parse tree in a depth first manner. The first discovery of a node is done by calling the enter function corresponding to the type of node. As soon as all children of set node have been evaluated, the corresponding exit function will be called.

However, the creation of nodes is not the same in all situations, in some cases, a specific kind of node will be created, and in other cases a specific kind of node will not be created, depending on the rule used for the current node (which we can determine from the context of the current node). In order to know whether or not we need to pop a node from the node stack, we will allow the code to look at the top node in the stack, and evaluate the type of set node. No other context related evaluations will be allowed.

\subsubsection{Context-free analysis assignmentExpression example}
To look at a concrete example, consider the following rule in the grammar:
\begin{align*}
	&assignmentExpression\\
	&\text{:}\indent \text{conditionalExpression}\\
	&|\indent \text{unaryExpression assignmentOperator assignmentExpression}\\
	&|\indent \text{Digitsequence}; \\
\end{align*}
The rule for conditionalExpression needs to be there, as there is a chain of expressions, and some expressions need to be higher in the order than others, therefore all expressions with a higher priority need to be evaluated before the lower priority expressions. This is done by adding a rule to a lower priority expression in each expression class. It is however undesirable for these nodes to be added. Without regard for context in other nodes, we can simply look at the current node to see whether or not the conditionalExpression line is used (which antlr generated context allows us to do).

Since there is a chance no new node was added within the enter function, we will also be required to evaluate the top of the stack, to see whether or not the top of the stack is a node we need to pop, the code will do the same check that was done in the enter function of the traversal.

\subsection{Context-sensitive abstract syntax tree reduction}
Now that all obviously redundant nodes have been eliminated, there is still the need for context sensitive reductions. We will attempt to implement constant propagation and substitution, in which we compute constant expressions, and replace variables with known value, by their actual value. Furthermore we will try to rephrase expressions by expressions with the same meaning, so that all expressions, if possible, are in an acceptable format for the counter automaton.

The context-sensitive reduction will also keep track of a lot of data about the variables in a symbol table. It will track whether or not variables are current initialized with a known value, values at certain points within the execution, it will track struct, union and enum definitions used for folding and so on. It will keep track of the kind of variables we have (eg. counters and parameters). All of this info will be used to enable the operations this cycle will perform, but will also be used in the validation loop.

The program will do this by traversing the abstract syntax tree resulting from the previous step, but will now specifically go through the children of relevant expressions (eg. assignment expressions, additive expressions, ...).

Important to note is that no folding/substitution will occur within loops, as these operations occur a variable number of times, and since there is no way of determining the exact number of times without evaluating the expression, this is considered too complex and often impossible, as counters may depend on parameters, which need to be chosen at evaluation time.

\subsubsection{Context-sensitive reduction example constant propagation}
Another example of a needed reduction, is constant propagation and folding. It is possible that a code segment would initially be rejected, due to use of unwanted variables, while in essence, these variables are nothing but variable representations of results of constant expressions. Consider the code snippet below. It would initially be rejected, because the counter variable is initialized with a variable that is neither a constant nor a parameter.
\newpage
\begin{lstlisting}[style=CStyle]
bool divide(int p, int n){
	int variable = 5;
	variable += 20;
	int counter = variable;
	while(counter > 0){
		counter -= n;
	}
	counter += 1;
	counter -= 1;
	if(counter == 0){
		return true;
	}
	return false;
}
\end{lstlisting}

However, due to constant propagation and folding, we can simplify the two statements on line 2 and line 3, so that they become.

\begin{lstlisting}[style=CStyle]
int variable = 25;
\end{lstlisting}

Now that the variable is just a constant, we can substitute this variable in the declaration of counter, so that we now have the following.
\begin{lstlisting}[style=CStyle]
int variable = 25;
int counter = 25;
\end{lstlisting}

The new code segment is acceptable, but we will not stop here, as the first line of the code is useless. It has no further benefit for the execution and will therefore be dropped. The final counter assignment will not be folded. Whenever a variable gets altered within a conditional scope, the variable is considered to be uncertain, and further folding based on earlier values will not be allowed. The final code segment is as described below, which is trivially accepted to be converted to a counter automaton.

\begin{lstlisting}[style=CStyle]
bool divide(int p, int n){
	int counter = 25;
	while(counter > 0){
		counter -= n;
	}
	counter += 1;
	counter -= 1;
	if(counter == 0){
		return true;
	}
	return false;
}
\end{lstlisting}

\subsubsection{Context-sensitive reduction example addition folding}
As described earlier, we do allow additions and subtractions of the form - v and + v, where $v \in P$ or $v \in \mathbb{N}$ with $P$ the set of parameters. Given that the formation described in figure \ref{fig:unfolded_addition} occurs in the automaton, we would technically not be allowed to accept this, as this is not directly in the specified format.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\linewidth]{unfolded_addition}
	\caption{An Assignment Expression with counter addition as value.}
	\label{fig:unfolded_addition}
\end{figure}

However, the context-sensitive reduction will be able to reduce the earlier specified example to the automaton in figure \ref{fig:folded_addition} This automaton will be acceptable, as this is a direct use of an allowed operation.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\linewidth]{folded_addition}
	\caption{An Assignment Expression with constant as value.}
	\label{fig:folded_addition}
\end{figure}
\newpage
\subsubsection{Nodes}
After the cleaning cycle has finished, there will only be a relatively small set of nodes remaining. Below a quick overview and their meaning within the syntax tree.

\begin{multicols}{2}
	\noindent
	\textbf{Compilation Unit} indicates the root of each Abstract Syntax Tree.\\
	\textbf{Function Definition} indicates the definition of a new function.\\
	\textbf{Function Specifier} indicates specifier of function.\\
	\textbf{Generic} head node for generic specification.\\
	\textbf{Generic Association} indicates a generic association.\\
	\textbf{Parameter Type List} head of the specification of all parameters of a function.\\
	\textbf{Parameter Declaration} head node of the declaration of a single parameter.\\
	\textbf{Compound Statement} indicates a scope defined by \{ \} brackets.\\
	\textbf{Type Specifier} indicates that the child(ren) of this node need to be regarded as being known type(s).\\
	\textbf{Type Name} indicates that the child(ren) of this node need to be regarded as being a type(s).\\
	\textbf{Type Def Name} indicates the definition of a type.\\
	\textbf{Declaration} indicates a declaration, this can contain multiple types and identifiers. In case of a function, the function name and parameter types plus identifiers will all belong to a single declarator node.\\
	\textbf{Init Declarator} defines a declaration of a variable with an initial value.\\
	\textbf{Direct Declarator} defines a declaration of a variable with a second variable.\\
	\textbf{Declarator} head node for the variable name part of the declaration.\\
	\textbf{Initializer} head node for the value part of the declaration.\\
	\textbf{Primary Expression} defines the most basic expression, eg. brackets, identifiers, constants, ... .\\
	\textbf{Postfix Expression} defines a postfix expression.\\
	\textbf{Unary Expression} defines a unary expression.\\
	\textbf{Cast Expression} defines a cast expression.\\
	\textbf{Multiplicative Expression} defines a multiplicative expression.\\
	\textbf{Additive Expression} defines an additive expression.\\
	\textbf{Shift Expression} defines a shift expression.\\
	\textbf{Relational Expression} defines a relational expression.\\
	\textbf{Equality Expression} defines an equality expression.\\
	\textbf{Bitwise And Expression} defines a bitwise and expression.\\
	\textbf{Bitwise Xor Expression} defines a bitwise exclusive or expression.\\
	\textbf{Bitwise Or Expression} defines a bitwise inclusive or expression.\\
	\textbf{Logical And Expression} defines a logical and expression.\\
	\textbf{Logical Or Expression} defines a logical or expression.\\
	\textbf{Conditional Expression} defines a conditional expression.\\
	\textbf{Assignment Expression} defines an assignment expression.\\
	\textbf{Expression} head node in case of multiple expressions.\\
	\textbf{For Declaration} head node for the first clause of a for loop.\\
	\textbf{For Expression} head node for a clause of a for loop.\\
	\textbf{For Condition} head node for the condition part of the second clause of a for loop.\\
	\textbf{Iteration Statement} defines an iteration statement (for, while, do while).\\
	\textbf{Jump Statement} defines a jump statement.\\
	\textbf{return} indicates return statement.\\
	\textbf{Labeled Statement} indicates a labeled statement.\\
	\textbf{Struct or Union Specifier} indicates the specification of a struct or union.\\
	\textbf{Enum Specifier} indicates the specification of an enumerator.\\
	\textbf{Struct Declaration} head node for a struct declaration.\\
	\textbf{Struct Declarator} head node for a struct declarator.\\
	\textbf{Static Assert Declaration} defines static assertion.\\
	\textbf{Enumerator} specifies variables part of an enumerator.\\
	\textbf{Size} head for array size.\\
	\textbf{Default} defines the default option for switch statement.\\
	\textbf{Alignment Specifier} defines an alignment restriction to an identifier.\\
	\textbf{Atomic Type Specifier} defines an atomic type.\\
	\textbf{Arguments} head node for arguments part of a function call.\\
	\textbf{sizeof} defines sizeof operation.\\
	\textbf{\_Alignof} defines \_alignof operation.\\
	\textbf{Val = $<$value$>$} defines a constant. \\
	\textbf{ID = $<$id$>$} defines a variable name.
\end{multicols}

\subsection{Abstract syntax tree validation}
The fourth loop will iterate over the abstract syntax tree resulting from the previous step, and while doing so, it will evaluate the nodes that occur and the context in which they occur.

The majority of the node evaluation is represented in a list of unsupported nodes. Most of these nodes are head nodes for certain kinds of expressions which will never be supported.

\begin{align*}
	unsupported = \left\{ \begin{array}{l}
		Multiplication\ Expression, sizeof, \_Alignof, \\
		\&, *, -, +, ., ->, !, ~, Cast\ Expression, \\
		Shift\ Expression, Bitwise\ And\ Expression, \\
		Bitwise\ Or\ Expression, Bitwise\ Xor\ Expression, \\
		*=, /=, \%=, <<=, >>=, \&=, ^=, |=, \\
		Logical\ And\ Expression, Logical\ Or\ Expression, \\
		Additive\ Expression
	\end{array} \right\}
\end{align*}

Whenever such a node occurs, the current situation will be inspected. We can either be assigning to a counter, or in a restricted conditional expression. The correct error will be chosen if either of the two situations is relative.

Furthermore, all variable usage will be tracked. We will allow multiple counters to exist, as long as we can substitute one general counter without having any conflicts, in other words, there can't be any overlap between counter usages. This is simply tracked by tracking the nodes in which the counter variables occur, with the exception of when they occur within conditional scopes. If this is the case, their first usage is set to the first line of the scope, so that overlap does occur when a different counter is used for the condition of the scope.

Finally, the initial value will be tracked. In case there is a declaration with an initial value, this value will be chosen, otherwise it will be set to 0, which is the default integer value in C. This initial value allows us to skip over declarations in the generator. We can simply set the counter value to the initial value of the used counter at that point in time, just before its first usage.

Another aspect that will be tested, is the function definition. A function needs to have a boolean return type, and can only have integer parameters. If this not the case, an error status will be added.

These conditions will all be tracked separately for each function. Whenever the status list is empty at the end of the evaluation, we assume that no issues occurred, and we say that the function satisfies the requirements, if there are any issues, no counter automaton will be generated, and the errors will be printed to the terminal.

Important to note is that there is no regard for global statements. These are considered to be variable and undetermined. It could be that they can perfectly be used as counters, and that they will never be altered by other functions, but it is impossible to determine this efficiently. Therefore, a counter must be declared within the function scope.

\subsubsection{validation example}
When we go back to the earlier mentioned segment of code. We obtain the automaton displayed in figure \ref{fig:divide_cleaned}.

\begin{lstlisting}[style=CStyle]
bool divide(int p, int n){
	int counter = p;

	while(counter > 0){
		counter -= n;
	}

	if(counter == 0){
		return true;
	}
	return false;
}
\end{lstlisting}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{divide_cleaned}
	\caption{The cleaned Abstract Syntax Tree of the divide function.}
	\label{fig:divide_cleaned}
\end{figure}

We can immediately see that the function conforms to the required function definition, as the return type is boolean, as can be seen from the leftmost node. The parameters are also of type int, which can be seen from the parameters defined underneath the 'Parameter Type List' node.

From the cleaner we know which variables are counters, and we can see that the first declaration is a counter, but we will skip the declaration, as we know the value which is stored in the initial value, the initialization will happen before the first operation on the counter occurs.

Next thing we encounter is the Iteration statement, for which we will check the condition with the constrained conditional variable enabled. With this variable enabled, we can simply continue traversing the nodes, and in case there are any unsupported nodes, the corresponding error would automatically be generated. However, there will be no corresponding nodes, so we will leave the Relational Expression without any error statuses, and we will disable the constrained conditional variable.

Next we will enter the compound statement, which symbolizes the inner scope of the iteration statement. We will encounter an Assignment Expression with a variable that we know is a counter, we will therefore enable the counter assignment variable, while traversing the children of this node. No invalid nodes will appear, and we will disable the counter assignment variable when leaving the Assignment Expression node.

The selection statement will be evaluated in the exact same manner as the Iteration Statement was evaluated, and as the jump statement holds no special operations, we can conclude that this function is ok for counter automaton generation.

\subsection{Counter automaton generation}
The final section of the program will be the counter generation itself. In this loop, there will be no more regards to possible invalid statements. At this point we assume everything to be known, and we can therefore simplify things drastically. Recall that the following list is the collection of allowed labels for the counter automaton.
\[
op = \{+c, -c, +p, -p, \leq c, =c, \geq c, \leq p, =p, \geq p: c \in \mathbb{N}, p \in P\} \cup \{\wedge\}
\]
This allows us to just check the head nodes related to such expressions.

An important thing to remark, is that we are not interested in general properties of runs for these automata. We are interested in the possibility of reachability or in other words, the existence of one path that will take us to a given node. This assumption is later on used to justify certain compositions.

\subsubsection{Functions}
First of all, we need the notion of the Function Definition statements. The generator will generate a counter automaton for each function, and needs to know when these start.

\subsubsection{Assignments}
Other than Functions, we will also need to know when assignments to counters occur, so that we can add the proper transition labels. We only need to check whether or not we are assigning to a counter, if so, we read the operation used, and the variable that gets assigned, and the manner $\in \{=, +=, -=\}$ gets used.

As mentioned earlier, assignments are not in the set of operations, but they can be represented using the operators displayed earlier, as can be seen in figure \ref{fig:counter_assignment}. This can be done by using a reset operation, where we first check whether or not the counter is smaller or equal to the desired value, if so, it is either already satisfied, in which case we can just carry on, or it is smaller than the desired value, for which we will add a self loop with $+1$ as a label, so that we will eventually reach the desired value. The same sequence of events occur in case the counter is larger or equal to the desired value, with the exception that we will use $-1$ as an in between operation.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.48\linewidth]{counter_assignment}
	\caption{Assignment of a value p to a counter.}
	\label{fig:counter_assignment}
\end{figure}

The same thing can be done when the counter is larger or equal to the desired value, if so, it is either already satisfied, in which case we can just carry on, or it is larger than the desired value, at which point we will decrement the counter with a self loop of -1, until the condition is satisfied.

This can be done without adding additional weightings to transitions, due to the remark made earlier. We are not interested in properties for every single run, yes there are runs where the counter can loop infinitely, but there will also be a run where the counter gets to the correct value, after which it will continue onward.

\subsubsection{Loop statements}
We will also need the notion of selection statements. These will make use of a maximum of 5 nodes to enforce everything related to the loops.

The first node will be the $start$ of the conditional statement, the second node is the pre node. This node symbolizes the state after the precondition of the for loop has been evaluated.

Next we need a node to identify the $start\ of\ the\ inner\ segment$, which will be reached by a transition with the condition as a label.

After this node the inner segment will follow, and it will be finalized with the $stop\ inner\ segment$ node, in case this one is needed. This stop node will symbolize the state after the post expression of the for loop has been evaluated, after this node, a transition will occur to the pre node, to reevaluate the loop condition.

Finally, one more node is needed, and this node will symbolize the \textit{end of the loop}. This node will always be the last node that gets generated, so that any nodes generated beyond this point will start from this point.

Consider the following segment of code.
\begin{lstlisting}[style=CStyle]
bool test(int a){
	int counter = 25;
	for(counter = 0; counter < 5; counter ++){
		continue;
	}
	counter = counter + 5;
	return true;
}
\end{lstlisting}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{test_counter_automaton}
	\caption{Example of an Iteration Statement.}
	\label{fig:test_counter_automaton}
\end{figure}

This will result in the counter automaton seen in figure \ref{fig:test_counter_automaton}. The iteration start node will be node 3.01, the start of the inner segment will be node 3.06 and the end of this same segment 3.02.

The inner segment itself consists out of one single node, being node 4.

The end of the iteration is denoted by node 3.03, and the first node beyond the iteration statement, being node 6, will follow after this one.

\subsubsection{If statements}
Another important construct are the if statements. These statements will, just as the loop statements did, require additional nodes to be able to be modeled. If statements require a total of 4 nodes to be modeled.

First of all, we need a $start\ of\ the\ iteration\ statement$ node, from which the conditions will start.

We will need an $if\ node$ and an $else\ node$ which will both signify the start of the if and possible else segment.

After the inner segment, they will all end up at the $end\ of\ the\ iteration\ statement$ from which point they will continue with the next line of code.

Consider the test2 function, it contains an if statement, an else if statement and an else statement.
\begin{lstlisting}[style=CStyle]
bool test2(){
	int counter = 25;
	if(counter == 23){
		counter += 3;
	}
	else if(counter == 24){
		counter += 2;
	}
	else{
		counter += 1;
	}
	return true;
}
\end{lstlisting}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{test2_counter_automaton}
	\caption{Example of Selection Statements.}
	\label{fig:test2_counter_automaton}
\end{figure}

The program will return a counter automaton as displayed in figure \ref{fig:test2_counter_automaton}. The iteration start node of the outer if will be node 3, the if node and else node of the same if will be 3.01 and 3.04 respectively. The end node of this if statement will be 3.02.

The else if will have 6 as a start node, 6.01 and 6.04 will function as if and else nodes respectively. Node 6.02 will signify the end of the else if statement.

Finally, the else statement will start at node 7, since this is no conditional statement, it will just behave as regular code.

\subsubsection{Inequality condtions}
Another statement we will need to support, are inequality conditions. If we want our conditional statements to be properly functioning, we will need to be able to generate opposing conditions, but the opposing condition of the equality condition, is the inequality condition, which we can not directly model using the given operations.

The following code segment makes use of an if statement which has an equality condition in it. This means that the edge going towards the else node, will have the opposing condition as a label.

\begin{lstlisting}[style=CStyle]
bool is_ten(int a){
	int counter = a;

	if(counter == 10){
		return true;
	}

	return false;
}
\end{lstlisting}

When looking at part of the resulting counter automaton in figure \ref{fig:inequality_expression}, we will notice the transitions going from the start of the if statement, being node 4, towards the end of the if statement, being node 4.02. There will not be an else node, as there is no else if or else statement.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{inequality_expression}
	\caption{Example of an inequality expression.}
	\label{fig:inequality_expression}
\end{figure}

The first transition chain starts with \textit{+1} followed by \textit{\textless =10}, followed by \textit{-1}, which results in the same expression as saying the original counter is strictly smaller than 10. The final \textit{-1} is there to reset the counter, so that the counter is back to what it originally was.

The second transition chain start with \textit{-1}, followed by \textit{\textgreater =10}, followed by \textit{+1}. This chain states that the counter must be strictly greater than 10.

If either of these can be taken, we can state that the counter must be different to the compared value (in this case 10), as these both express a strict inequality.

\subsubsection{less than and greater than}
The final additional expressions that will be added to the program described within his paper, are the less than and greater than expressions. These are needed to model the opposing conditions to greater than or equal and less than or equal respectively.

\begin{lstlisting}[style=CStyle]
bool is_ten(int a){
	int counter = 10;

	if(counter <= a){
		if(counter < a){
			return false;
		}
		return true;
	}

	return false;
}
\end{lstlisting}

The is\_ten code segment models both a less than or equal condition and a less than condition. This will mean that the first will need to be opposed with a strictly greater than condition, and the second one with a greater than or equal condition.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{less_than_greater_than}
	\caption{Example of a less than expression and a greater than expression.}
	\label{fig:less_than_greater_than}
\end{figure}

Part of the counter automaton of the is\_ten function can be seen in figure \ref{fig:less_than_greater_than}. This automaton has 3 as the start of the outer if and it has 3.01 and 3.02 as respective if and end nodes. The inner if has 4 as the start node, 4.01 as the start of the if segment, and 4.02 as the end node.

The strict greater than condition, originating from node 3 and ending in node 3.02, consists of 3 different transitions. The first transition \textit{-1} and \textit{\textgreater =a}, test if the counter is strictly greater. The third transition \textit{+1} is there to make sure that the counter goes back to its original value.

The strict less than condition, originating from node 4 and ending in node 4.01, consists of \textit{+1} and \textit{\textless =a} as their first two conditions, which can only be satisfied in case the counter is strictly less than a. The final condition \textit{-1} is there to make sure the counter goes back to its original value.

\section{Conclusion}
In this paper we gave a brief description of a program capable of converting a small subset of the c language to counter automata, to be used in later evaluation of reachability.

This subset consists of all functions who contain a maximum of one counter (and preferably exactly one, as reachability analysis without a single counter is considered trivial). The operations allowed on the counter are limited to addition and subtraction of parameters and constants, as well as assignment with parameters and constants. The conditional evaluations that are allowed are equality, inequality, strict less than, strict greater than, less than or equal and greater than or equal. All of these conditions must either be compared to constants or variables. Finally, variables can not be altered during the execution of the code and must remain constant.

The paper gives a description on all the steps the program goes through in order to achieve this counter automaton, as well as a brief insight in why things are the way they are.

The usability of this program without any further additions is very limited. The restrictions enforced on the c code make it fairly useless in more complex situations, where reachability analysis would be far more desired however, it is very effective in case the program is applicable. Big conditional statements or a large amount of conditional statements can make the reachability of certain sub segments hard, and with the addition of a reachability checker, they could definitely lead to improvements in coding.

\section{Future work}
In a future research, we will attempt to improve the given program, so that it will be more efficient, and most importantly, more useful. The program is too restrictive to be practically usable, and should therefore be expanded to support further c code.

Furthermore, in this same research we will add an expansion to the program, which will allow the evaluation of counter automata, so that actual reachability conclusions can be made.
\printbibliography
\end{document}

### 2020-02-15 Automaton/Automaton.py

@@ -1,0 +1,119 @@
+class Automaton:
+    def __init__(self):
+        self.root = None
+        self.nodes = list()
+        self.transitions = list()
+        self.initial = None
+
+    def add_node(self, name):
+        node = Node(name, len(self.nodes))
+        self.nodes.append(node)
+
+        if len(self.nodes) == 1:
+            self.initial = node
+
+        return node
+
+    def get_node(self, name):
+        for node in self.nodes:
+            if node.name == name:
+                return node
+        return None
+
+    def get_last_node(self):
+        return self.nodes[-1]
+
+    def get_index_for_label(self, name):
+        for node in self.nodes:
+            if node.name == name:
+                return node.index
+        return None
+
+    def add_transition(self, start, finish, label="", condition=""):
+        transition = Transition(start, finish, label, condition)
+        self.transitions.append(transition)
+        return transition
+
+    def remove_transition(self, start, finish):
+        for transition in self.transitions:
+            if transition.start == start and transition.finish == finish:
+                index = self.transitions.index(transition)
+                self.transitions.pop(index)
+                return True
+        return False
+
+    def get_transition_label(self, start, finish):
+        for transition in self.transitions:
+            if transition.start == start and transition.finish == finish:
+                return transition.label
+        return None
+
+    def set_transition_label(self, start, finish, new_label):
+        for transition in self.transitions:
+            if transition.start == start and transition.finish == finish:
+                transition.label = new_label
+
+    def add_to_transition_label(self, start, finish, new_label):
+        for transition in self.transitions:
+            if transition.start == start and transition.finish == finish:
+                if transition.label == "":
+                    transition.label = new_label
+                else:
+                    transition.label += ", " + new_label
+
+    def add_to_transition_condition(self, start, finish, new_condition):
+        for transition in self.transitions:
+            if transition.start == start and transition.finish == finish:
+                if transition.condition == "":
+                    transition.condition = new_condition
+                else:
+                    transition.condition += "\n" + new_condition
+
+    def to_dot(self):
+        result = "digraph G {\n\t\t"
+        result += "rankdir=LR\n\t\t"
+
+        if len(self.nodes) > 0:
+
+            for node in self.nodes:
+                result += "Q{0}[label=\"{1}\"];\n\t\t".format(node.index, node.name)
+
+            result += "Qi[style=invis];\n\t\t"
+
+            result += "Qi -> Q{0} [label=\"\"]\n\t\t".format(self.get_index_for_label(self.initial.name))
+
[…]

### 2020-02-15 Automaton/Generator.py

@@ -1,0 +1,593 @@
+from Automaton.Automaton import Automaton
+
+from math import floor
+
+"""
+This class is intended to generate all the nodes and transitions that are in the automaton. It will 
+iterate through the tree that was generated during earlier steps. 
+
+We will create one node for each lien in the code. Depending on what the line of code does, there will be
+a label added to the transition originating from the state. It is also possible for a node to have two
+outgoing conditional transition in case the line of code symbolised a conditional statement. Finally
+a transition might have no label whatsoever, in case the line of code had nothing to do with counters,
+as this is al we care about.
+"""
+
+
+class Generator:
+    def __init__(self, code, root, counters, parameters, functions):
+        f = open(code, "r")
+        self.__nr_of_lines = len(f.readlines())
+        f.close()
+
+        self.__function_names = dict()
+
+        # store an automaton per function
+        self.__automatons = dict()
+
+        self.__root = root
+
+        # list of all counters
+        self.__counters = counters
+
+        # list of all parameters
+        self.__parameters = parameters
+
+        # counter for the nr of encountered functions, this will be used as a key to destiniguish between
+        # function scopes
+        self.__functions_counter = 0
+
+        # this are the lines that have valuable code in it, this list will be used to generate the
+        # set of nodes for the counter automaton
+        self.__lines = list()
+        self.__lines.append(0)
+
+        # to support breaking in deeper statements, we need to be able to track which line the last break was, in order
+        # to know which line we should go towards.
+        self.__for_lines = list()
+
+        # during the iteration of the nodes, we can alter this value
+        # every time we reach a new line, this label will be used for the transition, and the
+        # variable will be reset to the empty string
+        self.__next_label = ""
+
+        # during the iteration of the nodes, we can alter this  value
+        # every time we reach a new line, this condition will be used for the transition,
+        # and the variable will be reset to the empty string
+        self.__next_condition = ""
+
+        self.__functions = functions
+
+        # keep track of the last node generated for a line, so that we can easily generate unique new ones
+        self.__last_nodes = dict()
+
+    @staticmethod
+    def get_negation(condition):
+        if condition == ">":
+            return "<="
+        elif condition == "<":
+            return ">="
+        elif condition == "<=":
+            return ">"
+        elif condition == ">=":
+            return "<"
+        elif condition == "&&":
+            return "||"
+        elif condition == "||":
+            return "&&"
+        elif condition == "=":
+            return "!="
+        elif condition == "!=":
+            return "="
[…]

### 2020-02-15 C_code/conditions.c

@@ -1,18 +1,18 @@
-long double main(){
+long double test(){
     int x = 0;
     int y = 0;
-    for(((x(0))); x < 10; x ++){
+    for(((func(5))); x < 10; x ++){
         y ++;
     }
-    for(x=5, x=3;x<20; ++x){
+    for(x=5, x=3;x<20, y>10; ++x){
         --y;
     }
 
-    LOOP: for(void x();x<5; x++){
-        goto Loop;
+    LOOP: for(void x();y<5; y++){
+        goto LOOP;
     }
 
-    for(int q; q < 10; q++){}
+    for(; q < 10; q++){}
 
     if(x > 20 && x >= 10 || y <= 25){
         return false;
@@ -26,11 +26,8 @@ long double main(){
     if(x & 5 && y | 4 && y ^ 5){
         return true;
     }
-    else{
-        return false;
-    }
 
-    while(true){
+    while(x > 5, x++){
         break;
     }
 
@@ -40,7 +37,7 @@ long double main(){
 
     _Static_assert(0, "test");
 
-    do {a++;} while (a < 300);
+    do {a++;} while (a < 300, b < 200);
 
     return true;
 }

### 2020-02-15 Compiler.py

@@ -21,6 +21,8 @@ from Tree.ASTConstructor import ASTConstructor
 from Tree.ASTCleaner import ASTCleaner
 from Tree.ASTValidator import ASTValidator
 
+from Automaton.Generator import Generator
+
 
 class Compiler:
     trace = False
@@ -29,6 +31,7 @@ class Compiler:
     cleaned_ast = None
     cleaner = None
     validator = None
+    generator = None
 
     @staticmethod
     def grammar(grammar_file):
@@ -98,7 +101,8 @@ class Compiler:
                     file_name = temp[:-2]
 
             f = open("./TreePlots/{}_cleaned_output.dot".format(file_name), "w")
-            f.write(self.cleaned_ast.to_dot())
+            temp = self.cleaned_ast.to_dot()
+            f.write(temp)
             f.close()
 
             os.system("dot -Tpng ./TreePlots/{0}_cleaned_output.dot -o ./TreePlots/{0}_cleaned.png"
@@ -111,12 +115,48 @@ class Compiler:
             print("Counter validation loop started.")
 
         self.validator = ASTValidator(self.cleaned_ast, self.cleaner.get_symbol_table())
-        self.validator.validate()
+        validity = self.validator.validate()
 
         if self.trace:
             print("Counter Validation loop finished.")
             print("The following functions where found:")
             self.validator.print_functions()
+
+        if not validity and self.trace:
+            print("Since at least one of the functions was found to be invalid, "
+                  "no counter automaton will be generated.")
+            return 0
+
+        if self.trace:
+            print("Automaton generator started.")
+
+        counters = self.validator.get_counters()
+        parameters = self.validator.get_parameters()
+        functions = self.validator.get_functions()
+        self.generator = Generator(code_file, self.cleaned_ast, counters, parameters, functions)
+        self.generator.generate_automaton()
+
+        if self.image_output:
+            file_name = ""
+            file_names = code_file.split("/")
+            for temp in file_names:
+                if temp[-2:] == '.c':
+                    file_name = temp[:-2]
+            function_names = self.generator.get_function_names()
+            dots = self.generator.to_dot()
+            for counter in function_names.keys():
+                function_name = function_names[counter]
+                dot = dots[counter]
+                f = open("./TreePlots/{}_reachability_automaton_{}.dot".format(file_name, function_name), "w")
+                f.write(dot)
+                f.close()
+
[…]

### 2020-02-15 SymbolTable/SymbolTable.py

@@ -58,6 +58,9 @@ class SymbolTable:
     def get_scopes(self):
         return self.__scopes.keys()
 
+    def get_current_scope(self):
+        return self.__current_scope
+
     def clear_symbols(self):
         self.__symbols = dict()
         for scope in self.__scopes:
@@ -157,6 +160,16 @@ class SymbolTable:
         else:
             return self.is_initialized(symbol_name, scope.get_parent())
 
+    def set_initialized(self, symbol_name, initialized, scope=None):
+        if scope is None:
+            scope = self.__current_scope
+        if self.__scopes["0"] == scope:
+            return False
+        if symbol_name in self.__symbols[scope]:
+            return self.__symbols[scope][symbol_name].set_initialized(initialized)
+        else:
+            return self.set_initialized(symbol_name, initialized, scope.get_parent())
+
     def get_value(self, symbol_name, scope=None):
         if scope is None:
             scope = self.__current_scope
@@ -207,7 +220,7 @@ class SymbolTable:
         else:
             return self.is_used(symbol_name, scope.get_parent())
 
-    def is_counter(self, symbol_name, scope):
+    def is_counter(self, symbol_name, scope=None):
         if type(scope) == str:
             scope = self.__scopes[scope]
         elif scope is None:
@@ -225,7 +238,55 @@ class SymbolTable:
         if symbol_name in self.__symbols[scope]:
             return self.__symbols[scope][symbol_name].set_counter(counter_val)
         else:
+            if scope.get_label() == "0":
+                return False
             return self.set_counter(counter_val, symbol_name, scope.get_parent())
+
+    def symbol_has_initial_value(self, symbol_name, scope=None):
+        if scope is None:
+            scope = self.__current_scope
+        if symbol_name in self.__symbols[scope]:
+            return self.__symbols[scope][symbol_name].has_initial_value()
+        else:
+            return self.symbol_has_initial_value(symbol_name, scope.get_parent())
+
+    def set_initial_value(self, symbol_name, initial_value, scope=None):
+        if scope is None:
+            scope = self.__current_scope
+        if symbol_name in self.__symbols[scope]:
+            self.__symbols[scope][symbol_name].set_initial_value(initial_value)
+        else:
+            if scope.get_label() == "0":
+                return False
+            self.set_initial_value(symbol_name, initial_value, scope.get_parent())
+
+    def get_initial_value(self, symbol_name, scope=None):
+        if scope is None:
[…]

### 2020-02-15 Tree/ASTCleaner.py

@@ -10,11 +10,15 @@ class ASTCleaner:
 
         self.__scope_counter = 0  # this value is used to give scopes unique names
 
-        self.__declarations = dict()  # this dict keeps track of the node that declared a variable
+        self.__declarations = dict()  # this dict keeps tra²ck of the node that declared a variable
 
         self.__changes_occurred = True  # this value tracks whether or not something changes in a cycle
 
         self.__queued_for_pop = list()  # list that keeps track of which nodes are ready to get popped
+
+        self.__entered_branch = False  # this value checks if inside branch statement, if so, condition => counter
+
+        self.__assigning_to_counter = False  # track whether or not we are assigning to a counter
 
         AbstractSyntaxTree.node_count = 0
 
@@ -50,11 +54,11 @@ class ASTCleaner:
                             for temp in staged_for_pop:
                                 self.__declarations.pop(temp)
 
-                    for instance in self.__symbol_table.get_group_instances(scope):
-                        if not self.__symbol_table.is_instance_used(instance, scope) and instance in self.__declarations \
-                                and self.__declarations[instance] not in self.__queued_for_pop:
-                            self.remove_node(self.__declarations[instance])
-                            removed_node = self.__declarations[instance]
+                    for inst in self.__symbol_table.get_group_instances(scope):
+                        if not self.__symbol_table.is_instance_used(inst, scope) and inst in self.__declarations\
+                                and self.__declarations[inst] not in self.__queued_for_pop:
+                            self.remove_node(self.__declarations[inst])
+                            removed_node = self.__declarations[inst]
 
                             staged_for_pop = list()
                             for temp in self.__declarations:
@@ -182,6 +186,13 @@ class ASTCleaner:
     def update_assigned_value(self, variable_name, assignment_node, value):
         # set the assignment node equal to the desired value, and move the declaration to be the next statement
         # in the current scope
+        if self.__symbol_table.is_counter(variable_name, self.__symbol_table.get_current_scope()):
+            if assignment_node.get_label() == "Assignment Expression" and assignment_node.get_children()[1] != "=":
+                assignment_node.get_children()[2].set_label(value)
+                assignment_node.get_children()[1].set_label("=")
+
[…]

### 2020-02-15 Tree/ASTConstructor.py

@@ -771,6 +771,23 @@ class ASTConstructor(CListener):
         self.__node_stack.insert(0, new_node)
 
     def exitForCondition(self, ctx: CParser.ForConditionContext):
+        # we have the rule of the form forDeclaration ';' forExpression? ';' forExpression?
+        if ctx.forDeclaration():
+            if not isinstance(list(ctx.getChildren())[2], CParser.ForExpressionContext):
+                self.grow_on_index("For Expression", ctx, 1)
+            if not isinstance(list(ctx.getChildren())[-1], CParser.ForExpressionContext):
+                self.grow_on_index("For Expression", ctx, 2)
+
+        # we have the rule of the form expression? ';' forExpression? ';' forExpression?
+        else:
+            if not ctx.expression():
+                self.grow_on_index("For Expression", ctx, 0)
+            if not ctx.expression() and not isinstance(list(ctx.getChildren())[1], CParser.ForExpressionContext):
+                self.grow_on_index("For Expression", ctx, 1)
+            if ctx.expression() and not isinstance(list(ctx.getChildren())[2], CParser.ForExpressionContext):
+                self.grow_on_index("For Expression", ctx, 1)
+            if not isinstance(list(ctx.getChildren())[-1], CParser.ForExpressionContext):
+                self.grow_on_index("For Expression", ctx, 2)
         self.__node_stack.pop(0)
 
     def enterForDeclaration(self, ctx: CParser.ForDeclarationContext):

### 2020-02-15 Tree/ASTValidator.py

@@ -13,102 +13,334 @@ class ASTValidator:
     def __init__(self, root, symbol_table):
         self.__root = root
 
+        # counters used to generate unique names for functions, nodes and loop scopes
         self.__functions_counter = 0
         self.__node_counter = 0
         self.__loop_counter = 0
 
+        # dictionary that stores all function objects
         self.__functions = dict()
 
+        # symbol table object that keeps track of all variables
         self.__symbol_table = symbol_table
 
+        # dictionary that keeps track of the counters and parameters part of each function scope
         self.__counters = dict()
+        self.__parameters = dict()
 
+        # dictionary that keeps track of all scopes
         self.__scopes = dict()
+
+        # this variables will be set to true in case we are assigning to a counter or function parameter
+        # the target assignment will keep track of what variable we are currently assigning too
+        self.__counter_assignment_operation = False
+        self.__target_assignment_variable = list()
+
+        # this variable will be set to true in case we are evaluating a condition in a iteration or evaluation statement
+        self.__constrained_conditional_statement = False
+
+        # keep track of all nodes that defined unsupported counter operations (all operations except addition and
+        # assignment)
+        self.__unsupported_nodes = {"Multiplication Expression", "sizeof", "_Alignof", "&", "*", "-", "+",
+                                    ".", "->", "!", "~", "Cast Expression", "Shift Expression",
+                                    "Bitwise And Expression", "Bitwise Or Expression", "Bitwise Xor Expression",
+                                    "*=", "/=", "%=", "<<=", ">>=", "&=", "^=", "|=", "Logical And Expression",
+                                    "Logical Or Expression", "Additive Expression"}
+
+        # store the first line in which the most outer conditional statement was opened
+        self.__first_outer_line = None
 
     def validate(self, node=None):
         # track the number of nodes we have passed, this is used to properly define the first and last usage
         self.__node_counter += 1
+        success = True
 
         if node is None:
             node = self.__root
 
-        elif node.get_label() == "Function Definition":
+        # register assignments
+        if node.get_label() == "Assignment Expression":
+            assigned_var = node.get_children()[0].get_label()
+
+            # check whether or not we are assigning to a counter variable
+            if self.__symbol_table.is_counter(assigned_var[5:]):
+                self.__counter_assignment_operation = True
+                self.__target_assignment_variable.append(assigned_var[5:])
+
+                # if so, ensure that the second operator is either a parameter, or a constant
[…]

### 2020-02-15 Tree/AbstractSyntaxTree.py

@@ -8,6 +8,7 @@ class AbstractSyntaxTree:
         self.__parent = None
         self.__children = list()
         self.__ctx = ctx
+        self.__line = ctx.start.line
 
     def set_parent(self, node):
         self.__parent = node
@@ -44,11 +45,14 @@ class AbstractSyntaxTree:
     def is_parent(self, label):
         return self.__parent.get_label() == label
 
+    def get_line(self):
+        return self.__line
+
     def to_dot(self):
         result = ""
         node_id = AbstractSyntaxTree.node_count
 
-        if not self.__parent:
+        if not self.__parent and self.__label == "CompilationUnit":
             result += "digraph G {\n\t\t"
 
         label = self.__label
@@ -88,7 +92,7 @@ class AbstractSyntaxTree:
             result += "Q{0} -> Q{1}\n\t\t".format(node_id, AbstractSyntaxTree.node_count)
             result += child.to_dot()
 
-        if not self.__parent:
+        if not self.__parent and self.__label == "CompilationUnit":
             result += "\n}"
 
         return result

### 2020-02-15 test.py

@@ -10,6 +10,7 @@ class TestFirstLoop(unittest.TestCase):
     instance = AbstractSyntaxTree
     compiler = Compiler()
     compiler.image_output = True
+    maxDiff = None
 
     def setUp(self):
         self.instance.node_count = 0
@@ -85,6 +86,8 @@ class TestCleanerLoop(unittest.TestCase):
     compiler.image_output = True
     compiler.trace = True
 
+    maxDiff = None
+
     def setUp(self):
         self.instance.node_count = 0
 
@@ -93,8 +96,8 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/declarations_int.c")
         sys.stdout = sys.__stdout__
-        # with open("ExpectedTestOutput/declarations_int_trace.txt", 'w') as text_file:
-        #     text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/declarations_int_trace.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/declarations_int_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/declarations_int_output.dot', 'r') as myFile:
@@ -113,8 +116,8 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/declarations_float.c")
         sys.stdout = sys.__stdout__
-        # with open("ExpectedTestOutput/declarations_float_trace.txt", 'w') as text_file:
-        #     text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/declarations_float_trace.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/declarations_float_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/declarations_float_output.dot', 'r') as myFile:
@@ -133,8 +136,8 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/declarations_char.c")
         sys.stdout = sys.__stdout__
-        # with open("ExpectedTestOutput/declarations_char_trace.txt", 'w') as text_file:
-        #     text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/declarations_char_trace.txt", 'w') as text_file:
[…]

### 2020-02-15 C_code/declarations_char.c
fixed tests

@@ -60,7 +60,7 @@ int main(){
     printf("%d \n", p);
 
     // cast initializer
-    char q = (char) 92;
+    char q = (char) 72;
     printf("%d \n", q);
 
     // unary initializer

### 2020-02-15 Tree/ASTCleaner.py

@@ -2,6 +2,8 @@ from Tree.AbstractSyntaxTree import AbstractSyntaxTree
 
 from SymbolTable.SymbolTable import SymbolTable
 
+import os
+
 
 class ASTCleaner:
     def __init__(self, root):
@@ -10,7 +12,7 @@ class ASTCleaner:
 
         self.__scope_counter = 0  # this value is used to give scopes unique names
 
-        self.__declarations = dict()  # this dict keeps tra²ck of the node that declared a variable
+        self.__declarations = dict()  # this dict keeps track of the node that declared a variable
 
         self.__changes_occurred = True  # this value tracks whether or not something changes in a cycle
 
@@ -402,7 +404,7 @@ class ASTCleaner:
             if operand_2 != "" and operand_2[:5] == "ID = " and self.__symbol_table.is_initialized(operand_2[5:]):
                 operand_2 = "Val = {}".format(self.__symbol_table.get_value(operand_2[5:]))
 
-            if operand_1[5:] == "Val = ":
+            if operand_1[:6] == "Val = ":
                 operand_1_val = operand_1
 
             if operand_1 != "" and operand_2 != "" and operand_1[:5] == "ID = " and operand_2[:6] == "Val = " \
@@ -415,43 +417,43 @@ class ASTCleaner:
                     if operator == "*=":
                         value = self.perform_optimal_cast(operand_1_val[6:]) * self.perform_optimal_cast(operand_2[6:])
                         self.update_assigned_value(operand_1[5:], node, "Val = {}".format(value))
-                        return value
+                        return "Val = {}".format(value)
                     elif operator == "/=":
                         value = self.perform_optimal_cast(operand_1_val[6:]) / self.perform_optimal_cast(operand_2[6:])
                         self.update_assigned_value(operand_1[5:], node, "Val = {}".format(value))
-                        return value
+                        return "Val = {}".format(value)
                     elif operator == "%=":
                         value = self.perform_optimal_cast(operand_1_val[6:]) % self.perform_optimal_cast(operand_2[6:])
                         self.update_assigned_value(operand_1[5:], node, "Val = {}".format(value))
-                        return value
+                        return "Val = {}".format(value)
                     elif operator == "+=":
                         value = self.perform_optimal_cast(operand_1_val[6:]) + self.perform_optimal_cast(operand_2[6:])
                         self.update_assigned_value(operand_1[5:], node, "Val = {}".format(value))
-                        return value
[…]

### 2020-02-16 C_code/test_1.c
added first full test

@@ -1,0 +1,113 @@
+#include <stdbool.h>
+#include <cstdio>
+
+bool for_loops(int a){
+    int i = 0;
+    int k = 0;
+
+    for(int j = 0, l = 5; j < 3; j ++){
+        j += 1;
+    }
+
+    for(i = 2;i != 5; k++, i++){
+        continue;
+        i += 1;
+        break;
+    }
+
+    for(i=5, k = 10;;){
+    break;
+    }
+
+    for(i = a;;){
+    break;
+    }
+
+    for(;i < 500;){break;}
+
+    for(;;i++, k++){
+        if(i == 10){
+            i = 9;
+            break;
+        }
+        else{
+            i = 10;
+        }
+    }
+
+    return true;
+}
+
+bool while_loops(int b){
+    int i = 0;
+
+
+
+    while(i <= b){
+        i ++;
+
+    }
+
+    while((i != b)){
+
+        i--;
+        break;
+    }
+
+    while(i == b){
+
+        i --;
+    }
+
+    while(i > 0){i -= 1;i-=1;}
+
+    return true;
+}
+
+bool do_while_loops(int c){
+    int i = 10;
+
+    do {
+        i++;
+    }
+    while(i <= c);
+
+    do {
+        i--;
+        break;
+    }
+    while(i == 0);
+
+    do{
+        i --;
+    }
+    while(i == c);
+
+    do{i -= 1;}while(i>0);
+
+    return true;
+}
+
+bool if_statements(int d){
+    int i;
+
+    if(i != 0){
+        i = 6;
+    }
+
+    if(i == 5){
+        i -= 5;
+    }
+
+    if(i > 3){
+        i = d;
+    }
+    else if(i <= 4){
+        return true;
+    }
+    else{
+        i = 5;
+    }
+
+    return true;
+}

### 2020-02-16 Compiler.py

@@ -71,17 +71,17 @@ class Compiler:
 
         self.ast = constructor.get_ast()
 
+        file_name = ""
+        file_names = code_file.split("/")
+        for temp in file_names:
+            if temp[-2:] == '.c':
+                file_name = temp[:-2]
+
+        f = open("./TreePlots/{}_output.dot".format(file_name), "w")
+        f.write(self.ast.to_dot())
+        f.close()
+
         if self.image_output:
-            file_name = ""
-            file_names = code_file.split("/")
-            for temp in file_names:
-                if temp[-2:] == '.c':
-                    file_name = temp[:-2]
-
-            f = open("./TreePlots/{}_output.dot".format(file_name), "w")
-            f.write(self.ast.to_dot())
-            f.close()
-
             os.system("dot -Tpng ./TreePlots/{0}_output.dot -o ./TreePlots/{0}.png".format(file_name))
 
         if self.trace:
@@ -92,19 +92,18 @@ class Compiler:
         self.cleaner.perform_full_clean(self.trace)
         self.cleaned_ast = self.cleaner.get_ast()
 
+        file_name = ""
+        file_names = code_file.split("/")
+        for temp in file_names:
+            if temp[-2:] == '.c':
+                file_name = temp[:-2]
+
+        f = open("./TreePlots/{}_cleaned_output.dot".format(file_name), "w")
+        temp = self.cleaned_ast.to_dot()
+        f.write(temp)
+        f.close()
+
         if self.image_output:
-
-            file_name = ""
-            file_names = code_file.split("/")
-            for temp in file_names:
-                if temp[-2:] == '.c':
-                    file_name = temp[:-2]
-
-            f = open("./TreePlots/{}_cleaned_output.dot".format(file_name), "w")
-            temp = self.cleaned_ast.to_dot()
-            f.write(temp)
-            f.close()
-
             os.system("dot -Tpng ./TreePlots/{0}_cleaned_output.dot -o ./TreePlots/{0}_cleaned.png"
                       .format(file_name))
 
@@ -136,21 +135,22 @@ class Compiler:
         self.generator = Generator(code_file, self.cleaned_ast, counters, parameters, functions)
         self.generator.generate_automaton()
 
-        if self.image_output:
-            file_name = ""
-            file_names = code_file.split("/")
-            for temp in file_names:
-                if temp[-2:] == '.c':
-                    file_name = temp[:-2]
-            function_names = self.generator.get_function_names()
-            dots = self.generator.to_dot()
-            for counter in function_names.keys():
[…]

### 2020-02-16 Tree/ASTCleaner.py

@@ -1418,33 +1418,9 @@ class ASTCleaner:
 
             op = node.get_children()[1].get_label()
 
-            if self.__entered_branch:
-                if self.__symbol_table.is_counter(original[5:]) and op in {"++", "--"}:
-                    node.set_label("Assignment Expression")
-                    if op == "++":
-                        node.get_children()[1].set_label("+=")
-                    else:
-                        node.get_children()[1].set_label("-=")
-                    value_node = AbstractSyntaxTree("Val = 1", node.get_ctx())
-                    node.add_child(value_node)
-                    value_node.set_parent(node)
-                return ""
-
             if operand_1 != "" and operand_1[:5] == "ID = " and op in {"++", "--"} \
                     and self.__symbol_table.is_initialized(operand_1[5:]):
                 operand_1 = "Val = {}".format(self.__symbol_table.get_value(operand_1[5:]))
-
-            if self.__symbol_table.is_counter(original[5:]) and op in {"++", "--"} and operand_1[6:] != "Val = ":
-                node.set_label("Assignment Expression")
-                if op == "++":
-                    node.get_children()[1].set_label("+=")
-                else:
-                    node.get_children()[1].set_label("-=")
-                value_node = AbstractSyntaxTree("Val = 1", node.get_ctx())
-                node.add_child(value_node)
-                value_node.set_parent(node)
-
-                return ""
 
             if len(node.get_children()) > 1:
                 operator = node.get_children()[1].get_label()

### 2020-02-16 test.py

@@ -9,7 +9,8 @@ from Tree.AbstractSyntaxTree import AbstractSyntaxTree
 class TestFirstLoop(unittest.TestCase):
     instance = AbstractSyntaxTree
     compiler = Compiler()
-    compiler.image_output = True
+    compiler.image_output = False
+    compiler.trace = False
     maxDiff = None
 
     def setUp(self):
@@ -83,7 +84,7 @@ class TestFirstLoop(unittest.TestCase):
 class TestCleanerLoop(unittest.TestCase):
     instance = AbstractSyntaxTree
     compiler = Compiler()
-    compiler.image_output = True
+    compiler.image_output = False
     compiler.trace = True
 
     maxDiff = None
@@ -96,8 +97,6 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/declarations_int.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/declarations_int_trace.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/declarations_int_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/declarations_int_output.dot', 'r') as myFile:
@@ -116,8 +115,6 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/declarations_float.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/declarations_float_trace.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/declarations_float_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/declarations_float_output.dot', 'r') as myFile:
@@ -136,8 +133,6 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/declarations_char.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/declarations_char_trace.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/declarations_char_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
[…]

### 2020-02-16 Compiler.py
attempted test fix

@@ -150,7 +150,7 @@ class Compiler:
             f.close()
 
         if self.image_output:
-            for function_name in function_names:
+            for function_name in function_names.values():
                 os.system("dot -Tpng ./TreePlots/{0}_reachability_automaton_{1}.dot -o \
                           ./TreePlots/{0}_reachability_automaton_{1}.png"
                           .format(file_name, function_name))

### 2020-02-16 test.py

@@ -9,7 +9,7 @@ from Tree.AbstractSyntaxTree import AbstractSyntaxTree
 class TestFirstLoop(unittest.TestCase):
     instance = AbstractSyntaxTree
     compiler = Compiler()
-    compiler.image_output = False
+    compiler.image_output = True
     compiler.trace = False
     maxDiff = None
 
@@ -84,7 +84,7 @@ class TestFirstLoop(unittest.TestCase):
 class TestCleanerLoop(unittest.TestCase):
     instance = AbstractSyntaxTree
     compiler = Compiler()
-    compiler.image_output = False
+    compiler.image_output = True
     compiler.trace = True
 
     maxDiff = None
@@ -276,7 +276,7 @@ class TestCleanerLoop(unittest.TestCase):
 class FullProgramTest(unittest.TestCase):
     instance = AbstractSyntaxTree
     compiler = Compiler()
-    compiler.image_output = False
+    compiler.image_output = True
     compiler.trace = True
 
     maxDiff = None
@@ -286,8 +286,6 @@ class FullProgramTest(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/test_1.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/test_1_trace.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/test_1_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/test_1_output.dot', 'r') as myFile:

### 2020-02-19 C_code/assignments_group.c
added two mroe tests

@@ -1,0 +1,118 @@
+#include "stdio.h"
+
+union numberRepresentation{
+    int option1;
+    float option2;
+};
+
+int main(){
+    union numberRepresentation a;
+    int b = 6;
+
+    // base assignment operation
+    a.option1 = 7;
+    printf("%d \n", a.option1);
+
+    // assignments using special assignment operator
+    a.option1 *= 8;
+    printf("%d \n", a);
+//    a.option1 /= 4;
+//    printf("%d \n", a);
+//    a.option1 %= 3;
+//    printf("%d \n", a);
+//    a.option1 += 3;
+//    printf("%d \n", a);
+//    a.option1 -= 2;
+//    printf("%d \n", a);
+//    a.option1 <<= 2;
+//    printf("%d \n", a);
+//    a.option1 >>= 1;
+//    printf("%d \n", a);
+//    a.option1 &= 4;
+//    printf("%d \n", a);
+//    a.option1 |= 13;
+//    printf("%d \n", a);
+//    a.option1 ^= 4;
+//    printf("%d \n", a);
+//
+//    // assignment using assignment expression
+//    a.option1 = b = 20;
+//    printf("%d \n", a);
+//    printf("%d \n", b);
+//
+//    // conditional assignment
+//    a.option1 = a.option1 == 20 ? 3 : 4;
+//    printf("%d \n", a);
+//
+//    // logical or assignment
+//    a.option1 = 5 || 0;
+//    printf("%d \n", a);
+//
+//    // logical and assignment
+//    a.option1 = 2 && 3;
+//    printf("%d \n", a);
+//
+//    // inclusive or assignment
+//    a.option1 = 2 | 0;
+//    printf("%d \n", a);
+//
+//    // exclusive or assignment
+//    a.option1 = 2 ^ 0;
+//    printf("%d \n", a);
+//
+//    // and assignment
+//    a.option1 = 2 ^ 0 && 5;
+//    printf("%d \n", a);
+//
+//    // equality assignment
+//    a.option1 = 2 == 3;
+//    printf("%d \n", a);
+//
+//    // relational assignment
+//    a.option1 = 2 < 3;
+//    printf("%d \n", a);
+//
+//    // shift assignment
+//    a.option1 = 2 << 2;
+//    printf("%d \n", a);
+//
+//    // additive assignment
+//    a.option1 = a.option1 + 5;
+//    printf("%d \n", a);
[…]

### 2020-02-19 C_code/test_1.c

@@ -1,4 +1,4 @@
-#include <stdbool.h>
+ #include <stdbool.h>
 #include <cstdio>
 
 bool for_loops(int a){

### 2020-02-19 C_code/test_invalid_conditions.c

@@ -1,0 +1,47 @@
+bool test_invalid_conditions(int a){
+    int counter = a;
+
+    if(counter > 5){
+        return true;
+    }
+
+    if(counter >= 5){
+        return true;
+    }
+
+    if(counter == 5){
+        return true;
+    }
+
+    if(counter != 5){
+        return true;
+    }
+
+    if(counter < 5){
+        return true;
+    }
+
+    if(counter <= 5){
+        return true;
+    }
+
+    if(counter & 5){
+        return false;
+    }
+
+    if(counter | 5){
+        return false;
+    }
+
+    if(counter ^ 5){
+        return false;
+    }
+
+    if(counter == 5 && counter != 5){
+        return false;
+    }
+
+    if(counter == 5 || counter != 5){
+        return false;
+    }
+}

### 2020-02-19 C_code/test_too_many_counters.c

@@ -1,0 +1,12 @@
+int test_too_many_counters(int a, int b){
+    int counter1 = a;
+    int counter2 = a;
+
+    if(counter1 < counter2){
+        return false;
+    }
+
+    if(a < b){
+        return true;
+    }
+}

### 2020-02-19 test.py

@@ -312,6 +312,8 @@ class FullProgramTest(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/test_invalid_expressions.c")
         sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/test_invalid_expressions_trace.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/test_invalid_expressions_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/test_invalid_expressions_output.dot', 'r') as myFile:
@@ -322,6 +324,46 @@ class FullProgramTest(unittest.TestCase):
         with open('./TreePlots/test_invalid_expressions_cleaned_output.dot', 'r') as myFile:
             actual_output = myFile.read()
         with open('ExpectedTestOutput/test_invalid_expressions_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_invalid_conditions(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/test_invalid_conditions.c")
+        sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/test_invalid_conditions_trace.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/test_invalid_conditions_trace.txt", 'r') as text_file:
+            self.assertEqual(text_file.read(), output.getvalue())
+        with open('./TreePlots/test_invalid_conditions_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_invalid_conditions_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/test_invalid_conditions_cleaned_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_invalid_conditions_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_too_many_counters(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/test_too_many_counters.c")
[…]

### 2020-02-19 Automaton/Automaton.py
added switch tests

@@ -4,8 +4,18 @@ class Automaton:
         self.nodes = list()
         self.transitions = list()
         self.initial = None
+        self.enabled = True
+
+    def disable(self):
+        self.enabled = False
+
+    def enable(self):
+        self.enabled = True
 
     def add_node(self, name):
+        if not self.enabled:
+            return None
+
         node = Node(name, len(self.nodes))
         self.nodes.append(node)
 
@@ -30,11 +40,15 @@ class Automaton:
         return None
 
     def add_transition(self, start, finish, label="", condition=""):
+        if not self.enabled:
+            return None
         transition = Transition(start, finish, label, condition)
         self.transitions.append(transition)
         return transition
 
     def remove_transition(self, start, finish):
+        if not self.enabled:
+            return None
         for transition in self.transitions:
             if transition.start == start and transition.finish == finish:
                 index = self.transitions.index(transition)
@@ -49,11 +63,17 @@ class Automaton:
         return None
 
     def set_transition_label(self, start, finish, new_label):
+        if not self.enabled:
+            return None
+
         for transition in self.transitions:
             if transition.start == start and transition.finish == finish:
                 transition.label = new_label
 
     def add_to_transition_label(self, start, finish, new_label):
+        if not self.enabled:
+            return None
+
         for transition in self.transitions:
             if transition.start == start and transition.finish == finish:
                 if transition.label == "":
@@ -62,6 +82,9 @@ class Automaton:
                     transition.label += ", " + new_label
 
     def add_to_transition_condition(self, start, finish, new_condition):
+        if not self.enabled:
+            return None
+
         for transition in self.transitions:
             if transition.start == start and transition.finish == finish:
                 if transition.condition == "":

### 2020-02-19 Automaton/Generator.py

@@ -197,56 +197,104 @@ class Generator:
             # get the automaton object for the current function
             automaton = self.__automatons[self.__functions_counter - 1]
 
-            # add the start node for the inner selection segment
-            if_node = self.get_new_node(node.get_line())
-            self.__lines.append(if_node)
-            automaton.add_node(if_node)
+            if node.get_children()[0].get_label() == "switch":
+                variable = node.get_children()[1].get_label()
 
-            # evaluate the inner segment
-            self.generate_automaton(node.get_children()[2])
+                if variable[:5] == "ID = ":
+                    start_of_condition = "{}".format(variable[5:])
+                else:
+                    start_of_condition = "{}".format(variable[6:])
 
-            selection_end = self.get_new_node(node.get_line())
+                end_node = self.get_new_node(node.get_line())
+                all_return = True
 
-            return1 = False
-            return2 = False
+                for child in node.get_children()[2].get_children():
+                    if child.get_children()[0].get_label() == "case":
+                        condition = child.get_children()[1].get_label()
 
-            # add a transition from the last node, to the end node of the selection statement, in case the
-            # last statement of the inner scope was not return, if this would have been the case, we do not add
-            # any transition as this is the end of the code
-            if self.__next_label != "return" and self.__next_label != "break":
-                # add an end node for the selection statement
-                start = self.__lines[-1]
-                automaton.add_transition(start, selection_end, self.__next_label, "")
-                self.__next_label = ""
+                        start = self.__lines[-1]
 
-            elif self.__next_label == "break":
-                start = self.__lines[-1]
-                automaton.add_transition(start, self.__for_lines[-1], "", "")
-                self.__next_label = ""
+                        if_node = self.get_new_node(node.get_line())
+                        self.__lines.append(if_node)
+                        automaton.add_node(if_node)
 
-            # if label is return, we just end the transitions here, as this is the end of the execution
-            elif self.__next_label == "return":
-                self.__next_label = ""
-                return1 = True
+                        if condition[:6] == "Val = ":
+                            condition_statement = "{} = {}".format(start_of_condition, condition[6:])
+                            opposite_condition = "{} != {}".format(start_of_condition, condition[6:])
+                        else:
+                            condition_statement = "{} = {}".format(start_of_condition, condition[5:])
+                            opposite_condition = "{} != {}".format(start_of_condition, condition[5:])
 
-            else_node = None
+                        automaton.add_transition(start, if_node, "", condition_statement)
 
-            # check for potential else statement
[…]

### 2020-02-19 C_code/switch.c

@@ -1,11 +1,24 @@
-int main(){
-    int a;
-    switch(a) {
-        case 5:
-            return 5;
-        case 3:
-            return 3;
-        default:
-            return 3;
+bool test_switch(){
+    int a = 0;
+    if(a == 0){
+        switch(a) {
+            case 5:
+                a ++;
+                a ++;
+                return true;
+                break;
+                a++;
+            case 3:
+                return true;
+            default:
+                return true;
+        }
+
+        a ++;
+        return true;
+    }
+    else{
+        a += 5;
+        return true;
     }
 }

### 2020-02-19 Tree/ASTCleaner.py

@@ -1144,8 +1144,11 @@ class ASTCleaner:
     def clean_jump_statement(self, node):
         index = node.get_parent().find_child(node)
         size = len(node.get_parent().get_children())
-        for i in reversed(range(index + 1, size)):
-            node.get_parent().pop_child(i)
+        for i in range(index + 1, size):
+            child = node.get_parent().get_children()[index+1]
+            if child.get_label() == "Labeled Statement" and child.get_children()[0].get_label() in {"case", "default"}:
+                break
+            node.get_parent().pop_child(index+1)
 
         func = node.get_children()[0].get_label()
         if func == "return":
@@ -1252,6 +1255,27 @@ class ASTCleaner:
                 return output[:-2]
 
     def clean_selection_statement(self, node):
+        if node.get_children()[0].get_label() == "switch":
+            variable = node.get_children()[1].get_label()
+            if variable[:5] == "ID = ":
+                self.__symbol_table.set_used(variable[5:], True)
+                self.__symbol_table.set_counter(True, variable[5:])
+
+            max_i = len(node.get_children()[2].get_children())
+            i = 0
+
+            temp = node.get_children()[2]
+
+            while i < max_i:
+                statement = temp.get_children()[i]
+                if statement.get_label() != "Labeled Statement":
+                    temp.pop_child(i)
+                    statement.set_parent(temp.get_children()[i-1])
+                    temp.get_children()[i-1].add_child(statement)
+                    max_i -= 1
+                else:
+                    i += 1
+
         if self.__entered_branch:
             self.clean(node.get_children()[1])
             self.clean(node.get_children()[2])
@@ -1524,7 +1548,8 @@ class ASTCleaner:
 
         # head node for a labeled statement
         elif node.get_label() == "Labeled Statement":
-            self.clean(node.get_children()[-1])
+            for i in reversed(range(2, len(node.get_children()))):
+                self.clean(node.get_children()[i])
             return ""
 
         # head node for a logical and comparison, needed for condition evaluation

### 2020-02-19 test.py

@@ -72,14 +72,6 @@ class TestFirstLoop(unittest.TestCase):
             expected_output = myFile.read()
         self.assertEqual(expected_output, actual_output)
 
-    def test_switch(self):
-        self.compiler.analysis("./C_code/switch.c")
-        with open('./TreePlots/switch_output.dot', 'r') as myFile:
-            actual_output = myFile.read()
-        with open('ExpectedTestOutput/switch_output.dot', 'r') as myFile:
-            expected_output = myFile.read()
-        self.assertEqual(expected_output, actual_output)
-
 
 class TestCleanerLoop(unittest.TestCase):
     instance = AbstractSyntaxTree
@@ -307,13 +299,36 @@ class FullProgramTest(unittest.TestCase):
                 expected_output = myFile.read()
             self.assertEqual(expected_output, actual_output)
 
+    def test_test_switch(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/switch.c")
+        sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/switch_trace.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/switch_trace.txt", 'r') as text_file:
+            self.assertEqual(text_file.read(), output.getvalue())
+        with open('./TreePlots/switch_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/switch_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/switch_cleaned_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/switch_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/switch_reachability_automaton_test_switch.dot', 'r') as myfile:
+            actual_output = myfile.read()
+        with open('./ExpectedTestOutput/switch_reachability_automaton_test_switch.dot', 'r') as myfile:
+            expected_output = myfile.read()
+        self.assertEqual(actual_output, expected_output)
+
     def test_invalid_expressions(self):
         output = io.StringIO()
         sys.stdout = output
[…]

### 2020-02-19 Automaton/Generator.py
altered switch test

@@ -205,18 +205,62 @@ class Generator:
                 else:
                     start_of_condition = "{}".format(variable[6:])
 
+                start_node = self.__lines[-1]
+
                 end_node = self.get_new_node(node.get_line())
                 all_return = True
 
-                for child in node.get_children()[2].get_children():
+                branch_nodes = list()
+                last_node = None
+
+                compound = node.get_children()[2].get_children()
+
+                # generate the linked chain of inner statements
+                for child in compound:
+                    new_node = self.get_new_node(node.get_line())
+                    self.__lines.append(new_node)
+                    automaton.add_node(new_node)
+
+                    if last_node is not None:
+                        automaton.add_transition(last_node, new_node, "", "")
+
+                    branch_nodes.append(new_node)
+
                     if child.get_children()[0].get_label() == "case":
-                        condition = child.get_children()[1].get_label()
+                        for i in range(2, len(child.get_children())):
+                            self.generate_automaton(child.get_children()[i])
+                    else:
+                        for i in range(1, len(child.get_children())):
+                            self.generate_automaton(child.get_children()[i])
 
-                        start = self.__lines[-1]
+                    if self.__next_label != "return" and self.__next_label != "break":
+                        new_node = self.get_new_node(node.get_line())
 
-                        if_node = self.get_new_node(node.get_line())
-                        self.__lines.append(if_node)
-                        automaton.add_node(if_node)
+                        automaton.add_transition(self.__lines[-1], new_node, self.__next_label, "")
+
+                        self.__lines.append(new_node)
+                        automaton.add_node(new_node)
+
+                        self.__next_label = ""
+                        last_node = new_node
+
+                    elif self.__next_label == "break":
+                        all_return = False
+                        automaton.add_transition(self.__lines[-1], end_node, "", "")
+                        self.__next_label = ""
+                        last_node = None
+
+                    elif self.__next_label == "return":
+                        self.__next_label = ""
+                        last_node = None
+
+                    automaton.enable()
+
+                # link the conditional branches to the proper part of the chain
+                for i in range(len(compound)):
+                    labeled_statement = compound[i]
+                    if labeled_statement.get_children()[0].get_label() == "case":
+                        condition = labeled_statement.get_children()[1].get_label()
 
                         if condition[:6] == "Val = ":
                             condition_statement = "{} = {}".format(start_of_condition, condition[6:])
@@ -225,62 +269,31 @@ class Generator:
                             condition_statement = "{} = {}".format(start_of_condition, condition[5:])
[…]

### 2020-02-19 C_code/switch.c

@@ -9,9 +9,9 @@ bool test_switch(){
                 break;
                 a++;
             case 3:
-                return true;
+                a++;
             default:
-                return true;
+                a++;
         }
 
         a ++;
@@ -21,4 +21,6 @@ bool test_switch(){
         a += 5;
         return true;
     }
+
+    return true;
 }

### 2020-02-19 test.py

@@ -304,8 +304,6 @@ class FullProgramTest(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/switch.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/switch_trace.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/switch_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/switch_output.dot', 'r') as myFile:

### 2020-02-19 Documentation/paper.tex
altered paper

@@
 
+\subsubsection{Switch statements}
+A second conditional expression that exists in c, are \textit{switch statements}.
+These statements allow a variable to be compared against multiple values.
+What is special about the switch statements, is that if matched with one case, the code of all consequential cases will also be executed, until the end of the switch, or until a jump occurs.
+
+Consider the following code snippet. In this case, a variable a will be compared with multiple values, and depending on the matched case, a number of prints will occur.
+
+\begin{lstlisting}[style=CStyle]
+bool test(int a){
+	switch(a){
+		case 5:
+			printf("The parameter is greater than 4.");
+		case 3:
+			printf("The parameter is greater than 2.");
+		default:
+			printf("The parameter value is %d", a);
+	}
+
+	return true;
+}
+\end{lstlisting}
+
+To generate a counter automaton for a switch statement, we will start by generating a chain for the statements in the cases.
+This is represented by the chain starting from node 4, all the way to node 8, in figure \ref{fig:counter_switch}.
+
+After that we need to add the conditional branches that correspond to the different cases.
+A first branch originates from node 2, and can either go to node 2.02 in case the counter is equal to 5, or to 2.08 in case the counter is not.
+
+There is a second branch from 2.08 where we can either go to 2.04 in case the counter is equal to 3, or to 2.06 in case the counter is not.
+
+The case starting points are represented by 2.02, 2.04 and 2.06 respectively, and their respective code follows directly beyond these nodes.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{counter_switch}
+	\caption{Example of a switch statement.}
+	\label{fig:counter_switch}
+\end{figure}
 \subsubsection{If statements}
@@
 	\includegraphics[width=\linewidth]{test2_counter_automaton}
-	\caption{Example of Selection Statements.}
+	\caption{Example of if statements.}
 	\label{fig:test2_counter_automaton}

### 2020-02-20 Automaton/Generator.py
added all return test

@@ -165,10 +165,10 @@ class Generator:
                     elif assigned_value[:6] == "Val = ":
                         self.__next_label += "{} {}".format(op, assigned_value[6:])
 
-        elif "break" in node.get_label():
+        elif "break" == node.get_label():
             self.__next_label = "break"
 
-        elif "return" in node.get_label():
+        elif "return" == node.get_label():
             self.__next_label = "return"
 
         elif node.get_label() == "Postfix Expression":
@@ -213,7 +213,11 @@ class Generator:
                 branch_nodes = list()
                 last_node = None
 
-                compound = node.get_children()[2].get_children()
+                if node.get_children()[2].get_label() == "Compound Statement":
+                    compound = node.get_children()[2].get_children()
+                else:
+                    compound = list()
+                    compound.append(node.get_children()[2])
 
                 # generate the linked chain of inner statements
                 for child in compound:

### 2020-02-20 C_code/test_all_return.c

@@ -1,0 +1,35 @@
+bool if_all_return(int a){
+    if(a == 5){
+        a++;
+        return true;
+    }
+    else{
+        a--;
+        return true;
+    }
+    a = 10;
+    return false;
+}
+
+bool switch_all_return(int a){
+    switch(a)
+        default:
+            return true;
+
+    a ++;
+    return false;
+}
+
+bool switch_all_return_2(int a){
+    switch(a){
+        case 5:
+            return true;
+        case 10:
+            return true;
+        default:
+            return true;
+    }
+
+    a ++;
+    return false;
+}

### 2020-02-20 Tree/ASTCleaner.py

@@ -1266,15 +1266,16 @@ class ASTCleaner:
 
             temp = node.get_children()[2]
 
-            while i < max_i:
-                statement = temp.get_children()[i]
-                if statement.get_label() != "Labeled Statement":
-                    temp.pop_child(i)
-                    statement.set_parent(temp.get_children()[i-1])
-                    temp.get_children()[i-1].add_child(statement)
-                    max_i -= 1
-                else:
-                    i += 1
+            if temp.get_label() == "Compound Statement":
+                while i < max_i:
+                    statement = temp.get_children()[i]
+                    if statement.get_label() != "Labeled Statement":
+                        temp.pop_child(i)
+                        statement.set_parent(temp.get_children()[i-1])
+                        temp.get_children()[i-1].add_child(statement)
+                        max_i -= 1
+                    else:
+                        i += 1
 
         if self.__entered_branch:
             self.clean(node.get_children()[1])

### 2020-02-20 test.py

@@ -376,6 +376,27 @@ class FullProgramTest(unittest.TestCase):
             expected_output = myFile.read()
         self.assertEqual(expected_output, actual_output)
 
+    def test_all_branches_return(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/test_all_return.c")
+        sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/test_all_return_trace.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/test_all_return_trace.txt", 'r') as text_file:
+            self.assertEqual(text_file.read(), output.getvalue())
+        with open('./TreePlots/test_all_return_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_all_return_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/test_all_return_cleaned_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_all_return_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+
 
 if __name__ == '__main__':
     unittest.main(verbosity=2)

### 2020-02-20 C_code/test_counter_types.c
added test for incorrect counter types

@@ -1,0 +1,7 @@
+bool test_counter_type_1(){
+    char counter;
+
+    if(counter == 'c'){
+        return false;
+    }
+}

### 2020-02-20 Tree/ASTValidator.py

@@ -197,12 +197,13 @@ class ASTValidator:
             variable_name = node.get_label()[5:]
             if self.__symbol_table.is_counter(variable_name, None):
                 if variable_name not in self.__counters[self.__functions_counter - 1]:
+                    var_type = self.__symbol_table.get_type(variable_name)
                     if self.__first_outer_line is None:
                         iv = self.__symbol_table.get_initial_value(variable_name)
-                        counter = Counter(variable_name, self.__node_counter, node.get_line(), iv)
+                        counter = Counter(variable_name, var_type, self.__node_counter, node.get_line(), iv)
                     else:
                         iv = self.__symbol_table.get_initial_value(variable_name)
-                        counter = Counter(variable_name, self.__node_counter, self.__first_outer_line, iv)
+                        counter = Counter(variable_name, var_type, self.__node_counter, self.__first_outer_line, iv)
                     self.__counters[self.__functions_counter - 1][variable_name] = counter
                 self.__counters[self.__functions_counter - 1][variable_name].set_last_usage(self.__node_counter)
                 self.__counters[self.__functions_counter - 1][variable_name].set_last_usage_line(node.get_line())
@@ -308,6 +309,7 @@ class ASTValidator:
     def validate_functions(self):
         temp = 0
         success = True
+
         for function_def in self.__functions.values():
             return_type = function_def.get_return_type()
             if return_type != "bool":
@@ -337,6 +339,10 @@ class ASTValidator:
                                             "number of counters equal to 1.")
                     success = False
                     break
+
+            for counter in self.__counters[temp].values():
+                if counter.get_type() != "int":
+                    function_def.add_status("Incorrect counter type, this tool can only handle counters of type int.")
 
             if len(function_def.get_statuses()) == 0:
                 function_def.add_status("OK")
@@ -434,13 +440,17 @@ this function is a one counter function.
 
 
 class Counter:
-    def __init__(self, name, first, first_line, initial_value):
+    def __init__(self, name, counter_type, first, first_line, initial_value):
         self.__name = name
+        self.__type = counter_type
         self.__first_used = first
         self.__last_used = 0
         self.__first_used_line = first_line
         self.__last_used_line = 0
         self.__initial_value = initial_value
+
+    def get_type(self):
+        return self.__type
 
     def set_last_usage(self, last_used):
         self.__last_used = last_used

### 2020-02-20 test.py

@@ -381,8 +381,6 @@ class FullProgramTest(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/test_all_return.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/test_all_return_trace.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/test_all_return_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/test_all_return_output.dot', 'r') as myFile:
@@ -396,6 +394,25 @@ class FullProgramTest(unittest.TestCase):
             expected_output = myFile.read()
         self.assertEqual(expected_output, actual_output)
 
+    def test_counter_types(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/test_all_return.c")
+        sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/test_counter_types.txt", 'w') as text_file:
+            text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/test_all_return_trace.txt", 'r') as text_file:
+            self.assertEqual(text_file.read(), output.getvalue())
+        with open('./TreePlots/test_all_return_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_all_return_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/test_all_return_cleaned_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_all_return_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
 
 
 if __name__ == '__main__':

### 2020-02-20 C_code/test_parameter_types.c
added parameter types test

@@ -1,0 +1,3 @@
+bool test_parameter_types(char a, float b, bool c, double d){
+    return true;
+}

### 2020-02-20 Compiler.py

@@ -114,17 +114,12 @@ class Compiler:
             print("Counter validation loop started.")
 
         self.validator = ASTValidator(self.cleaned_ast, self.cleaner.get_symbol_table())
-        validity = self.validator.validate()
+        self.validator.validate()
 
         if self.trace:
             print("Counter Validation loop finished.")
             print("The following functions where found:")
             self.validator.print_functions()
-
-        if not validity and self.trace:
-            print("Since at least one of the functions was found to be invalid, "
-                  "no counter automaton will be generated.")
-            return 0
 
         if self.trace:
             print("Automaton generator started.")

### 2020-02-20 Tree/ASTValidator.py

@@ -308,13 +308,11 @@ class ASTValidator:
 
     def validate_functions(self):
         temp = 0
-        success = True
 
         for function_def in self.__functions.values():
             return_type = function_def.get_return_type()
             if return_type != "bool":
                 function_def.add_status("Incorrect return type, return type must be boolean.")
-                success = False
 
             combinations = itertools.combinations(range(len(self.__counters[temp])), 2)
             counter_names = list(self.__counters[temp].keys())
@@ -337,19 +335,23 @@ class ASTValidator:
                 if len(intersection) != 0:
                     function_def.add_status("Incorrect number of counters, this tool can only handle a maximal "
                                             "number of counters equal to 1.")
-                    success = False
                     break
 
             for counter in self.__counters[temp].values():
                 if counter.get_type() != "int":
                     function_def.add_status("Incorrect counter type, this tool can only handle counters of type int.")
 
+            for parameter_type in function_def.get_function_parameter_types():
+                if parameter_type != "int":
+                    function_def.add_status("Incorrect parameter type found, this tool can only handle parameters"
+                                            "of type int.")
+
             if len(function_def.get_statuses()) == 0:
                 function_def.add_status("OK")
 
             temp += 1
 
-        return success
+        return
 
     def print_functions(self):
         temp = 0
@@ -405,6 +407,9 @@ class Function:
 
     def set_function_parameter_types(self, function_parameter_types):
         self.__parameter_types = function_parameter_types
+
+    def get_function_parameter_types(self):
+        return self.__parameter_types
 
     def add_status(self, status):
         self.__status_list.append(status)

### 2020-02-20 test.py

@@ -161,8 +161,6 @@ class TestCleanerLoop(unittest.TestCase):
         sys.stdout = output
         self.compiler.analysis("./C_code/assignments_int.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/assignments_int_trace.txt", "w") as text_file:
-            text_file.write(output.getvalue())
         with open("ExpectedTestOutput/assignments_int_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
         with open('./TreePlots/assignments_int_output.dot', 'r') as myFile:
@@ -397,20 +395,36 @@ class FullProgramTest(unittest.TestCase):
     def test_counter_types(self):
         output = io.StringIO()
         sys.stdout = output
-        self.compiler.analysis("./C_code/test_all_return.c")
+        self.compiler.analysis("./C_code/test_counter_types.c")
         sys.stdout = sys.__stdout__
-        with open("ExpectedTestOutput/test_counter_types.txt", 'w') as text_file:
-            text_file.write(output.getvalue())
-        with open("ExpectedTestOutput/test_all_return_trace.txt", 'r') as text_file:
+        with open("ExpectedTestOutput/test_counter_types_trace.txt", 'r') as text_file:
             self.assertEqual(text_file.read(), output.getvalue())
-        with open('./TreePlots/test_all_return_output.dot', 'r') as myFile:
+        with open('./TreePlots/test_counter_types_output.dot', 'r') as myFile:
             actual_output = myFile.read()
-        with open('ExpectedTestOutput/test_all_return_output.dot', 'r') as myFile:
+        with open('ExpectedTestOutput/test_counter_types_output.dot', 'r') as myFile:
             expected_output = myFile.read()
         self.assertEqual(expected_output, actual_output)
-        with open('./TreePlots/test_all_return_cleaned_output.dot', 'r') as myFile:
+        with open('./TreePlots/test_counter_types_cleaned_output.dot', 'r') as myFile:
             actual_output = myFile.read()
-        with open('ExpectedTestOutput/test_all_return_cleaned_output.dot', 'r') as myFile:
+        with open('ExpectedTestOutput/test_counter_types_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_parameter_types(self):
+        output = io.StringIO()
+        sys.stdout = output
[…]

### 2020-02-20 Automaton/Generator.py
added tests for constant conditions

@@ -2,6 +2,8 @@ from Automaton.Automaton import Automaton
 
 from math import floor
 
+import operator
+
 """
 This class is intended to generate all the nodes and transitions that are in the automaton. It will 
 iterate through the tree that was generated during earlier steps. 
@@ -79,9 +81,27 @@ class Generator:
             return "!="
         elif condition == "!=":
             return "="
-        else:
-            print("no negation found for condition {}".format(condition))
-            return ""
+
+    @staticmethod
+    def get_operator(op):
+        return {
+            '+': operator.add,
+            '-': operator.sub,
+            '*': operator.mul,
+            '/': operator.truediv,
+            '%': operator.mod,
+            "<<": operator.lshift,
+            ">>": operator.rshift,
+            "&": operator.and_,
+            "^": operator.xor,
+            "|": operator.or_,
+            "==": operator.eq,
+            "!=": operator.ne,
+            "<": operator.lt,
+            "<=": operator.le,
+            ">": operator.gt,
+            ">=": operator.ge
+        }[op]
 
     def generate_automaton(self, node=None):
         if node is None:
@@ -298,39 +318,42 @@ class Generator:
             else:
                 all_return = True
 
+                condition, opposite_condition = self.evaluate_condition(node.get_children()[1])
                 if_node = self.get_new_node(node.get_line())
-                self.__lines.append(if_node)
-                automaton.add_node(if_node)
-
-                self.generate_automaton(node.get_children()[2])
-
-                automaton.enable()
 
                 selection_end = self.get_new_node(node.get_line())
 
                 return1 = False
                 return2 = False
 
-                if self.__next_label != "return" and self.__next_label != "break":
-                    all_return = False
-                    start = self.__lines[-1]
-                    automaton.add_transition(start, selection_end, self.__next_label, "")
-                    self.__next_label = ""
+                if condition != "false":
+                    self.__lines.append(if_node)
+                    automaton.add_node(if_node)
 
-                elif self.__next_label == "break":
-                    all_return = False
-                    start = self.__lines[-1]
-                    automaton.add_transition(start, self.__for_lines[-1], "", "")
-                    self.__next_label = ""
+                    self.generate_automaton(node.get_children()[2])
 
-                elif self.__next_label == "return":
-                    self.__next_label = ""
-                    return1 = True
+                    automaton.enable()
+
+                    if self.__next_label != "return" and self.__next_label != "break":
+                        all_return = False
[…]

### 2020-02-20 C_code/test_constant_conditions_do_while.c

@@ -1,0 +1,25 @@
+bool test_constant_conditions(){
+    int i = 0;
+    do{
+        i=5;
+    }
+    while(10 < 5);
+
+    if(i == 5){
+        return false;
+    }
+    return true;
+}
+
+bool test_constant_conditions_2(){
+    int i = 0;
+    do{
+        i=5;
+    }
+    while(5 < 10);
+
+    if(i == 5){
+        return true;
+    }
+    return false;
+}

### 2020-02-20 C_code/test_constant_conditions_for.c

@@ -1,0 +1,21 @@
+bool test_constant_conditions(){
+    int i = 0;
+    for(int i = 0; 10 < 5; i++){
+        i = 5;
+    }
+    if(i == 5){
+        return false;
+    }
+    return true;
+}
+
+bool test_constant_conditions_2(){
+    int i = 0;
+    for(int i = 0; 5 < 10; i++){
+        i = 5;
+    }
+    if(i == 5){
+        return true;
+    }
+    return false;
+}

### 2020-02-20 C_code/test_constant_conditions_if.c

@@ -1,0 +1,28 @@
+bool test_constant_conditions(){
+    int i = 0;
+    if(5 < 10){
+        i ++;
+    }
+    else if(10 < 20){
+        i ++;
+    }
+    if(i == 1){
+        return true;
+    }
+    return false;
+}
+
+bool test_constant_conditions_2(){
+    int i = 0;
+    if(10 < 5){
+        i ++;
+    }
+    else if(10 < 20){
+        i ++;
+    }
+    if(i == 1){
+        return true;
+    }
+    return false;
+
+}

### 2020-02-20 C_code/test_constant_conditions_while.c

@@ -1,0 +1,21 @@
+bool test_constant_conditions(){
+    int i = 0;
+    while(10 < 5){
+        i = 5;
+    }
+    if(i == 5){
+        return false;
+    }
+    return true;
+}
+
+bool test_constant_conditions_2(){
+    int i = 0;
+    while(5 < 10){
+        i = 5;
+    }
+    if(i == 5){
+        return true;
+    }
+    return false;
+}

### 2020-02-20 test.py

@@ -428,6 +428,86 @@ class FullProgramTest(unittest.TestCase):
             expected_output = myFile.read()
         self.assertEqual(expected_output, actual_output)
 
+    def test_constant_conditions_if(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/test_constant_conditions_if.c")
+        sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/test_constant_conditions_if_trace.txt", "w") as text_file:
+            text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/test_constant_conditions_if_trace.txt", 'r') as text_file:
+            self.assertEqual(text_file.read(), output.getvalue())
+        with open('./TreePlots/test_constant_conditions_if_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_constant_conditions_if_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/test_constant_conditions_if_cleaned_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_constant_conditions_if_cleaned_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+
+    def test_constant_conditions_for(self):
+        output = io.StringIO()
+        sys.stdout = output
+        self.compiler.analysis("./C_code/test_constant_conditions_for.c")
+        sys.stdout = sys.__stdout__
+        with open("ExpectedTestOutput/test_constant_conditions_for_trace.txt", "w") as text_file:
+            text_file.write(output.getvalue())
+        with open("ExpectedTestOutput/test_constant_conditions_for_trace.txt", 'r') as text_file:
+            self.assertEqual(text_file.read(), output.getvalue())
+        with open('./TreePlots/test_constant_conditions_for_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
+        with open('ExpectedTestOutput/test_constant_conditions_for_output.dot', 'r') as myFile:
+            expected_output = myFile.read()
+        self.assertEqual(expected_output, actual_output)
+        with open('./TreePlots/test_constant_conditions_for_cleaned_output.dot', 'r') as myFile:
+            actual_output = myFile.read()
[…]

### 2020-02-28 Documentation/paper.tex
updated incorrect images in paper

@@
 \noindent
-Reachability is a known problem that can heavily affect the efficiency of code.
-It has been proven that reachability is decidable for one counter timed automata and to exploit this, we will create a program which will convert c code into such automata.
-In case the code conforms to the restrictions, enforced by the need of it being a one counter automata, a reachability test can be performed, but the latter will not be part of this research.
+\noindent
+Code reachability is a known problem within computer science. It affects the efficiency and readability of code and is therefore a relevant aspect to analyse.
+
+\noindent
+This paper will try to provide a clear overview of a means in which we can convert c code into a counter automaton.
+It has been proven by Daniel Bundala and Joal Ouaknine that the reachability for these can be determined as long as they are restricted to one counter.
+It will show the different steps taken in an example set up, with explanations with how it works, and why it works.
 \end{abstract}
@@
 	int counter = 10;
-
 	if(counter <= a){
@@
 	}
-
 	return false;
@@
 \end{figure}
-
+\newpage
 Part of the counter automaton of the is\_ten function can be seen in figure \ref{fig:less_than_greater_than}.

### 2020-02-28 Automaton/Generator.py

@@ -191,7 +191,7 @@ class Generator:
         elif "return" == node.get_label():
             self.__next_label = "return"
 
-        elif node.get_label() == "Postfix Expression":
+        elif node.get_label() == "Postfix Expression" or node.get_label() == "Unary Expression":
             if len(node.get_children()) > 1:
                 variable = node.get_children()[0].get_label()
                 op = node.get_children()[1].get_label()
@@ -199,18 +199,7 @@ class Generator:
                 if variable[5:] in self.__counters[self.__functions_counter - 1] and op in {"++", "--"}:
                     first_use = self.__counters[self.__functions_counter - 1][variable[5:]].get_first_used_line()
                     last_use = self.__counters[self.__functions_counter - 1][variable[5:]].get_last_used_line()
-                    if first_use < node.get_line() < last_use:
-                        self.__next_label = "{} {}".format(op[0], 1)
-
-        elif node.get_label() == "Unary Expression":
-            if len(node.get_children()) > 1:
-                op = node.get_children()[0].get_label()
-                variable = node.get_children()[1].get_label()
-
-                if variable[5:] in self.__counters[self.__functions_counter - 1] and op in {"++", "--"}:
-                    first_use = self.__counters[self.__functions_counter - 1][variable[5:]].get_first_used_line()
-                    last_use = self.__counters[self.__functions_counter - 1][variable[5:]].get_last_used_line()
-                    if first_use < node.get_line() < last_use:
+                    if first_use <= node.get_line() <= last_use:
                         self.__next_label = "{} {}".format(op[0], 1)
 
         elif node.get_label() == "Selection Statement":

### 2020-03-12 Automaton/Generator.py
removed redundant nodes in iteration statements

@@ -424,15 +424,20 @@ class Generator:
             else:
                 iteration_start = self.__last_nodes[node.get_line()]
 
-            pre_loop = self.get_new_node(node.get_line())
-            loop_end = self.get_new_node(node.get_line())
+            if node.get_children()[0].get_label() == "for":
+                pre_loop = self.get_new_node(node.get_line())
+                loop_end = self.get_new_node(node.get_line())
+            else:
+                pre_loop = iteration_start
+
             iteration_end = self.get_new_node(node.get_line())
 
             # push the current line on the for_lines stack
             self.__for_lines.append(iteration_end)
 
-            automaton.add_node(pre_loop)
-            self.__lines.append(pre_loop)
+            if node.get_children()[0].get_label() == "for":
+                automaton.add_node(pre_loop)
+                self.__lines.append(pre_loop)
 
             # if working with a for loop, there is a segment that needs to be evaluated before the inner segment starts
             # the for is needed to support comma separated expressions
@@ -453,9 +458,6 @@ class Generator:
                     automaton.add_transition(iteration_start, pre_loop, self.__next_label, "")
 
                 self.__next_label = ""
-
-            else:
-                automaton.add_transition(iteration_start, pre_loop, "", "")
 
             inner_start = self.get_new_node(node.get_line())
 

### 2020-03-12 Documentation/paper.tex
updated paper

@@
 \graphicspath{ {./images/} }
+
+\usepackage{nameref}
+
+\usepackage{lscape}
 
@@
 
-\title{Reachability problems for counter automata}
+\title{C Code Conversion to Counter Automata for Reachability Analysis}
 \author{Lars Van Roy\\
@@
 \section{Introduction}
-A well known problem in writing code is the reachability of specific lines in set written code.
-It is often impossible to properly determine whether or not a line of code guarded by a condition statement is going to be reachable in any possible execution of the code.
-Unreachable code, due to unsatisfiable conditions, is an obvious issue for time restrained environments such as embedded computer systems.
+A well known problem in writing code is the reachability of specific lines in said written code.
+It is often impossible to properly determine whether or not a line of code guarded by a conditional statement is going to be reachable in any possible execution of the code\cite{713323, 10.1145/1292316.1292319}.
+Unreachable code is never desired, but is an ever more pressing issue for energy restrained environments such as embedded computer systems \cite{embeddedefficiency}.
+In these systems, we want our execution to be as efficient as possible, and therefore avoid conditions that can never be satisfied or lines that can never be reached at any cost.
 In order to upgrade the efficiency of code that is affected by time constraints, or code in general, a proper reachability analysis would be of great use.
-\newpage
 
-In order to analyze code reachability, we will make use of a property proven by Daniel Bundala and Joal Ouaknine \cite{danialandjoel}, in which they state that reachability is decidable for timed automata with a single parametric clock.
-Adding the restriction of only allowing a single parametric clock has a big effect on the types of code we can analyse, but is unavoidable, since there is no proof for two counter machines.
-Three counter machines and up have been proven to be undecidable.
+In order to analyse code reachability, we will want to make use of one counter automata.
+The one counter automata are especially interesting as code is easily convertible to counter automata and it has been proven \cite{succintandparametriconecounter, danialandjoel} that reachability is decidable for this type of automata.
+As will be shown in the continuation of this paper, adding the restriction of only allowing a single parametric clock has a big effect on the types of code we can analyse, but is unavoidable, since there is no proof for two counter machines.
+Reachability problems for machines with three or more counters have been proven to be undecidable.
 
-In this paper we will give an overview of a program which will be able to convert c code to such an automaton.
-The program will go through the following iterations on the path to generating a counter automaton.
+To analyse code reachability in (a subset of) c programs, we propose a program that will go through the following iterations on the path to generate a counter automaton.
 
 \begin{enumerate}
-	\item convert c code into a parse tree, using antlr
+	\item convert c code into a parse tree, using ANTLR
 	\item perform context free reductions on this parse tree
@@
 
-The c code can at most contain one counter (and preferably exactly one, as zero counter programs are assumed to be trivial when considering reachability).
-Furthermore, the operations on the counter will be restricted, the counter can only be altered via assignments with parameters or constants, and the counter can only be compared using equality, inequality, strict less than, strict greater than, less than or equal, greater than or equal, and only to paremeters or constants.
-Furthermore, these parameters can never be altered throughout the duration of the code.
+We will only consider a subset of c programs, which contain at most one counter where a counter is a variable that is used inside a conditional statement.
+The program will be able to handle c code with zero counters, but this is considered trivial and will be disregarded for the remainder of this paper.
+Furthermore, the operations on the counter will be restricted, the counter can only be updated via assignments with parameters or constants, and the counter can only be compared using equality, inequality, strict less than, strict greater than, less than or equal, greater than or equal, and only to parameters or constants.
+Furthermore, the function parameters are not allowed to be altered throughout the duration of the code.
 
@@
 
-\section{One counter automata}
-The automata used in this project are a specific subset of the generally defined automata. The general definition for an automaton A is given by the tuple (S, $s_0$, $\delta$, F, Op, $\lambda$) where
+\section{Motivation}
+Popular IDE's do already implement reachability analysis up to a certain degree.
+However, two of the most used IDE's, being Eclipse and Clion, were tested, and they both show that in some code snippets, reachability analysis is not performed up until the degree that could be done using counter automata.
+It is capable to resolve trivial dead code (aka constant conditions or code post return etc), but it is not able to resolve impossible sequences, where no possible counter value would ever satisfy some of the conditions in the sequence.
+
+This proves that there is a definite need for additional research on analysis in code.
+Reachability analysis by using counter automata would not only allow for an expansion of the current reachability analysis as is, but might also allow further expansions based on the results of the counter automaton expansion.
+
+\section{Preliminaries}
+This paper will make use of counter automata and more specifically one counter automata.
+These automata are derived from the general definition of automata and signify an extension by adding the notion of counters.
+
+\subsection{General automata}
+The automata used in this research are a specific subset of the generally defined automata. The general definition for an automaton A is given by the tuple (Q, $\Sigma$, $\delta$, $q_0$, F) where
 \begin{itemize}
-	\item S is the set of states
-	\item $s_0$ is the set of initial states
-	\item $\delta$ is the set of edges
-	\item F is the set of final states
-	\item Op is the set of operations
-	\item $\lambda$ is the mapping for every edge to an element of the set of operations
+	\item Q is the set of states
+	\item $\Sigma$ is a finite set of symbols, called the alphabet of the automaton
+	\item $\delta$ is the transition function, $\delta: Q \times \Sigma \rightarrow Q$
+	\item $q_0$ is the initial state, $q_0 \in Q$
+	\item F is a set of states of Q defining the final states, $F \subseteq Q$
 \end{itemize}
 
-A class of automata derived from the general automaton is the class of timed automata.
-Before we can consider a definition for these automata, we need to introduce a few additional concepts as described Martin Fr\^anzle et al.
-\cite{informationprocessingletters} and Uli Fahrenberg \cite{higherdimensionaltimedautomata}.
+\subsection{Counter automata}
 
-Consider a set of clocks $\chi$, the corresponding set $\phi(\chi)=\{x_1,...,x_n\}$ of clock constraints is generated corresponding to the following grammar $\varphi ::= true | x<k | x = k | x>k | \varphi\land\varphi$.
-where $k \in \mathbb{N}$ and $x \in \chi$.
-Hence $\phi(\chi)$ is nothing but a set of constraints based on conjunctions of comparisons with clocks to integers.
-
-A clock valuation is a mapping $v:\chi \rightarrow \mathbb{R}_{\geq 0}$ where $\mathbb{R}_{\geq 0}$ is the set of non-negative real numbers.
-We denote $\mathbb{R}^{\chi}_{\geq 0}$ as the set of all clock valuations.
-Furthermore we write $v \models \varphi$ to denote that $v \in \mathbb{R}^{\chi}_{\geq 0}$ satisfies the constraint $\varphi$.
-We denote by 0 the valuation such that 0(x) = 0 for all $x \in \chi$.
-Given $t \in \mathbb{R}^{\chi}_{\geq 0}$, we let v+t be the clock valuation such that (v+t)(x) = v(x) + t for all clocks $x \in \chi$.
-Given $\lambda \subseteq \chi$, let v[$\lambda \leftarrow 0$] be the clock valuation such that
-\[
-	v[\lambda \leftarrow 0](x) = 
-	\begin{cases}
-		0,& \text{if } x \in \lambda\\
-		v(x),& \text{if } x \notin \lambda
-	\end{cases}
-\]
-A timed automaton B is defined by a tuple B = $(Q, q^0, Q^f, I, E)$, where
-\begin{itemize}
-	\item $Q$ is a finite set of locations
-	\item $q^0$ represents the initial location, $q^0 \in Q$
-	\item $Q^f$ represents the set of accepting locations, $Q^f \subseteq Q$
-	\item $I$ assigns invariants to states, $I: Q \rightarrow \phi(\chi)$
-	\item $E$ is the set of guarded transitions, $E \subseteq Q$ x $\phi(\chi)$ x $\Sigma$ x $2^\chi$ x $Q$
-\end{itemize}
-
-A run in a timed automaton is a sequence $\pi$ of configurations $c_1c_2 ...
-c_k$ such that each configuration is a direct successor of the previous configuration or, in other words, $c_i \rightarrow c_{i+1}$.
-We call a run accepting \textsl{accepting} if for a run $c_1c_2...c_k$ it holds that $c_1$ is the initial state and $c_k$ is the final state.
-
-A one-counter automaton is a tuple $\mathcal{A}$ = $(Q, q_0, \sigma, F)$ where
+A one-counter automaton is a tuple $\mathcal{A}$ = $(Q, q_0, \sigma, op, F)$ where
 \begin{itemize}
@@
 	\item $F \subseteq Q$ is the set of accepting states
-	\item $\sigma \subseteq Q $ x $ L $ x $ Q $ is the transition relation with L the set of instructions
+	\item $op$ is the set of operations
+	\item $\sigma \subseteq Q \times op \times Q$ is the transition relation with $op$ the set of operations
 \end{itemize}
 
-A counter valuation v is an element of $\mathbb{N}$ and a configuration of $\mathcal{A}$ is a pair in Q x $\mathbb{N}$. The initial configuration is the pair ($q_i$, 0).
+The counter valuation $c \in \mathbb{N}$ is the value that will be analysed, updated during the evaluation of the automaton.
 
-Finally, we will consider the following set of allowed operations where P is the set of parameters, the $\wedge$ symbol will be used to represent an empty label.
+At all times the automaton will be in a configuration $(q, c)$ where $q \in Q$ and $c$ the counter valuation where $(q_0, 0)$ is the initial configuration.
+
+Finally, we will consider the following set of allowed operations where $P$ is the set of parameters, the $\epsilon$ symbol will be used to represent an empty label.
 \[
- op = \{+c, -c, +p, -p, \leq c, =c, \geq c, \leq p, =p, \geq p: c \in \mathbb{N}, p \in P\} \cup \{\wedge\}
+ op = \{+c, -c, +p, -p, \leq c, =c, \geq c, \leq p, =p, \geq p: c \in \mathbb{N}, p \in P\} \cup \{\epsilon\}
 \]
@@
 The initial state $q_0$ will be the state corresponding with the first line of code.
-For now the set of final states $F$ will be empty, but the intended definition of the final state is the line(s) of which the reachability will be checked.
+For now the set of final states $F$ will be empty, but the intended interpretation of a final state will be the line of which the reachability will be checked.
 The transition relation will consist of elements of the form $(q_i, l, q_{i+1})$ where $q_i, q_{i+1} \in Q$ and $l \in op$.
-For each element it will hold that we can reach line $q_{i+1}$ from $q_i$.
-The l element or operation can either be blank, in which case there is a statement on line $q_i$ but it has no effect on the evaluation of our counter and will therefore be disregarded, or not blank.
-The operation will always be part of the \textit{op} set described earlier.
 
-There are a few exception to the above described states, some segments will have additional nodes to avoid confusion.
-In a loop there can be a pre loop, which will signify the state after the initial \textit{for condition} is performed, a start node for the inner segment, an end node to the inner segment, a post loop node, that will signify the state after the post statement has been evaluated, and finally a \textit{post iteration node}, which will signify the end of the statements.
-Same holds for selection statements (eg.
-if statements) which will have a start node, a start of success node, which signifies the body of the if statement, a start of else node, which will signify possible if else or else statements, and an end of selection node.
-Other states can be added for statements that require multiple steps, like assignments etc.
-These will be further explained in the generator section.
-\subsection{division example}
-Consider the following code segment, this code snippet will attempt to determine whether or not a given integer a, is greater or equal compared to a given integer b.
-Throughout the paper, the different steps will be described which will ultimately yield the automaton displayed in figure \ref{fig:greater_or_equal}.
-
-\begin{lstlisting}[style=CStyle]
-bool is_greater_or_equal(int a, int b){
-	if(a >= b){
-		return true;
-	}
-	return false;
-}
-\end{lstlisting}
-
-\begin{figure}[h]
-	\includegraphics[width=\linewidth]{is_greater_or_equal_counter_automaton}
-	\caption{A counter automaton corresponding with the is\_greater\_or\_equal function.}
-	\label{fig:greater_or_equal}
-\end{figure}
-
-This example automaton $\mathcal{A}$ is defined by the tuple $(Q, q_0, \sigma, F)$, where
-\begin{align*}
-	Q &= \{1, 1.97, 1.98, 1.99, 2, 2.01, 2.02, 2.03, 2.04, 3, 5\} \\
-	q_0 &= 1 \\
-	\sigma &= \left\{ \begin{array}{l}
-		(1, \wedge, 1.97), (1.97, \text{\textless =a}, 1.98), (1.98, \text{+1}, 1.98), (1.98, \text{=a}, 2), \\
-		(1.97, \text{\textgreater =a}, 1.99), (1.99, \text{-1}, 1.99), (1.99, \text{=a}, 2), (2, \text{\textgreater =b}, 2.01),\\ (2.01, \wedge, 3), (2, \text{+1}, 2.03), (2.03, \text{\textless =b}, 2.04), (2.04, \text{-1}, 2.02),\\ (2.04, \wedge, 5)
-	\end{array} \right\}\\
-	F &= \emptyset
-\end{align*}
+There are a few exceptions to the above described states, some segments will have additional nodes to avoid confusion.
+These special nodes, and their meaning, will be further explained in their relevant sections inside Section \ref{sec:generation}, \nameref{sec:generation}.
 
 \section{Program}
-\subsection{Program overview}
 The program that will perform the conversion from c code to a one counter automaton, will do this in five steps.
@@
 Along with these we will also need support for strict less than and greater than, which can also be implemented using the operations in the \textit{op} list.
-The full explanation on how this can be done, can be found in the generator section.
+The full explanation on how this can be done, can be found in Section \ref{sec:generation}.
 
 \subsection{Initialization}
-The program will start of by running the generator antlr compilation unit on the given c code.
+The program will start of by running the generator ANTLR compilation unit on the given c code.
 In case there are any issues regarding simple compilation rules, the program will exit with an error, indicating the issues in the code.
@@
 \subsection{Context-free abstract syntax tree generation}
-Using the parse tree resulting from the antlr compilation, we will try to generate an abstract syntax tree that is as simple as possible without regarding any context.
+Using the parse tree resulting from the ANTLR compilation, we will try to generate an abstract syntax tree that is as simple as possible without regarding any context.
 
-First of all, the code uses the notion of a node stack, this node stack will be used to store the nodes that are currently being evaluated.
+First of all, the code uses the notion of a node stack. This node stack will be used to store the nodes that are currently being evaluated.
 
@@
 The first discovery of a node is done by calling the enter function corresponding to the type of node.
-As soon as all children of set node have been evaluated, the corresponding exit function will be called.
+As soon as all children of said node have been evaluated, the corresponding exit function will be called.
 
@@
 It is however undesirable for these nodes to be added.
-Without regard for context in other nodes, we can simply look at the current node to see whether or not the conditionalExpression line is used (which antlr generated context allows us to do).
+Without regard for context in other nodes, we can simply look at the current node to see whether or not the conditionalExpression line is used (which ANTLR generated context allows us to do).
 
@@
 \subsection{Context-sensitive abstract syntax tree reduction}
-Now that all obviously redundant nodes have been eliminated, there is still the need for context sensitive reductions.
+There is still the need for context sensitive reductions.
 We will attempt to implement constant propagation and substitution, in which we compute constant expressions, and replace variables with known value, by their actual value.
@@
 
-\subsubsection{Context-sensitive reduction example constant propagation}
+\subsubsection{Context-sensitive reduction example: constant propagation}
 Another example of a needed reduction, is constant propagation and folding.
@@
 
-\subsubsection{Context-sensitive reduction example addition folding}
-As described earlier, we do allow additions and subtractions of the form - v and + v, where $v \in P$ or $v \in \mathbb{N}$ with $P$ the set of parameters.
-Given that the formation described in figure \ref{fig:unfolded_addition} occurs in the automaton, we would technically not be allowed to accept this, as this is not directly in the specified format.
+\subsubsection{Context-sensitive reduction example: addition folding}
+As described earlier, we do allow additions and subtractions of the form $-x$ and $+x$, where $x \in P$ or $x \in \mathbb{N}$ with $P$ the set of parameters.
+Given that the formation described in Figure \ref{fig:unfolded_addition} occurs in the automaton, we would technically not be allowed to accept this, as this is not directly in the specified format.
 
@@
 
-However, the context-sensitive reduction will be able to reduce the earlier specified example to the automaton in figure \ref{fig:folded_addition} This automaton will be acceptable, as this is a direct use of an allowed operation.
+However, the context-sensitive reduction will be able to reduce the earlier specified example to the automaton in Figure \ref{fig:folded_addition}.
+This automaton will be acceptable, as this is a direct use of an allowed operation.
 
@@
 
-Whenever such a node occurs, the current situation will be inspected.
-We can either be assigning to a counter, or in a restricted conditional expression.
-The correct error will be chosen if either of the two situations is relative.
+Whenever we encounter a node part of the $unsupported$ set, the current situation will be inspected.
+For example, if a \textit{Multiplication Expression} node occurs, inside a subtree of an \textit{Assignment Expression} node where an assignment to a counter was specified, we know that we are in an invalid state, as counters can only be updated via assignments, additions or subtractions.
+
+The same logic holds for subtrees of conditional expressions.
+In case we have a conditional expression where the subtree contains a \textit{Bitwise And Expression} node, we know that this is an invalid state, as constant conditions have already been folded in the previous step, this must mean that there is a counter in the condition, but counter comparisons are not allowed to contain and statements.
 
@@
 \subsubsection{validation example}
-When we go back to the earlier mentioned segment of code. We obtain the automaton displayed in figure \ref{fig:divide_cleaned}.
+When we go back to the earlier mentioned segment of code. We obtain the automaton displayed in Figure \ref{fig:divide_cleaned}.
 
@@
 
-Next thing we encounter is the Iteration statement, for which we will check the condition with the constrained conditional variable enabled.
+Next, we encounter the Iteration statement, for which we will check the condition with the constrained conditional variable enabled.
 With this variable enabled, we can simply continue traversing the nodes, and in case there are any unsupported nodes, the corresponding error would automatically be generated.
@@
 
-The selection statement will be evaluated in the exact same manner as the Iteration Statement was evaluated, and as the jump statement holds no special operations, we can conclude that this function is ok for counter automaton generation.
+The selection statement will be evaluated in the exact same manner as the Iteration Statement was evaluated, and as the jump statement holds no special operations, we can conclude that this function satisfies the requirements for one counter automaton generation.
 
 \subsection{Counter automaton generation}
+\label{sec:generation}
 The final section of the program will be the counter generation itself.
@@
 
-An important thing to remark, is that we are not interested in general properties of runs for these automata.
-We are interested in the possibility of reachability or in other words, the existence of one path that will take us to a given node.
-This assumption is later on used to justify certain compositions.
-
 \subsubsection{Functions}
@@
 \subsubsection{Assignments}
-Other than Functions, we will also need to know when assignments to counters occur, so that we can add the proper transition labels.
-We only need to check whether or not we are assigning to a counter, if so, we read the operation used, and the variable that gets assigned, and the manner $\in \{=, +=, -=\}$ gets used.
+Other than functions, we will also need to know when assignments to counters occur, so that we can add the proper transition labels.
+We only need to check whether or not we are assigning to a counter, if so, we read the operation used, and the variable that gets assigned.
+Valid counter assignments need to be of the form \textit{c op x} where $c$ is the counter, $op \in $ \textit{\{=, +=, -=\}} and $x \in P$ or $x \in \mathbb{N}$.
 
-As mentioned earlier, assignments are not in the set of operations, but they can be represented using the operators displayed earlier, as can be seen in figure \ref{fig:counter_assignment}.
-This can be done by using a reset operation, where we first check whether or not the counter is smaller or equal to the desired value, if so, it is either already satisfied, in which case we can just carry on, or it is smaller than the desired value, for which we will add a self loop with $+1$ as a label, so that we will eventually reach the desired value.
-The same sequence of events occur in case the counter is larger or equal to the desired value, with the exception that we will use $-1$ as an in between operation.
-
+As mentioned earlier, assignments are not in the set of operations, but they can be represented using the operators displayed earlier, as can be seen in Figure \ref{fig:counter_assignment}.
+This can be done by using a reset operation, where we first check whether or not the counter is smaller or equal to the desired value.
+If so, it is either already satisfied, in which case we can just carry on, or it is smaller than the desired value, for which we will add a self loop with $+1$ as a label, so that we will eventually reach the desired value.
 \begin{figure}[h]
@@
 
-This can be done without adding additional weightings to transitions, due to the remark made earlier.
-We are not interested in properties for every single run, yes there are runs where the counter can loop infinitely, but there will also be a run where the counter gets to the correct value, after which it will continue onward.
+An important thing to remark, is that we are not interested in general properties of runs for these automata.
+We are interested in the possibility of reachability or in other words, the existence of one path that will take us to a given node.
+In the given example, there is a path where we would remain in node 3.98 indefinitely but since there is at least one path that would take us to node 4, node 4 is still considered reachable.
 
-\subsubsection{Loop statements}
-We will also need the notion of selection statements. These will make use of a maximum of 5 nodes to enforce everything related to the loops.
+\subsubsection{Iteration statements}
+We will also need the notion of iteration statements, which needs 5 additional special nodes to fully support it's functionality.
+The first node will be the \textit{start of the loop}.
+The second node is the \textit{pre node}, this node symbolizes the state after the precondition of the for loop has been evaluated.
+Next we need a node to identify the \textit{start of the inner segment}, which will be reached by a transition with the condition as a label.
 
-The first node will be the $start$ of the conditional statement, the second node is the pre node. This node symbolizes the state after the precondition of the for loop has been evaluated.
-
-Next we need a node to identify the $start\ of\ the\ inner\ segment$, which will be reached by a transition with the condition as a label.
-
-After this node the inner segment will follow, and it will be finalized with the $stop\ inner\ segment$ node, in case this one is needed.
-This stop node will symbolize the state after the post expression of the for loop has been evaluated, after this node, a transition will occur to the pre node, to reevaluate the loop condition.
+After this node the inner segment will follow, and it will be finalized with the \textit{stop inner segment} node, in case this one is needed.
+This stop node will symbolize the state after the post expression of the for loop has been evaluated, after this node, a transition will occur to the pre node, to re-evaluate the loop condition.
 
@@
 
-Consider the following segment of code.
+Consider the following segment of code, this will result in the automaton in Figure \ref{fig:test_counter_automaton}.
 \begin{lstlisting}[style=CStyle]
-bool test(int a){
-	int counter = 25;
-	for(counter = 0; counter < 5; counter ++){
+bool test(int c){
+	for(c = 0; c < 5; c ++){
 		continue;
 	}
-	counter = counter + 5;
 	return true;
@@
 	\centering
-	\includegraphics[width=\linewidth]{test_counter_automaton}
+	\includegraphics[width=0.95\linewidth]{test_counter_automaton}
 	\caption{Example of an Iteration Statement.}
@@
 
-This will result in the counter automaton seen in figure \ref{fig:test_counter_automaton}.
-The iteration start node will be node 3.01, the start of the inner segment will be node 3.06 and the end of this same segment 3.02.
-
-The inner segment itself consists out of one single node, being node 4.
-
-The end of the iteration is denoted by node 3.03, and the first node beyond the iteration statement, being node 6, will follow after this one.
-
 \subsubsection{Switch statements}
-A second conditional expression that exists in c, are \textit{switch statements}.
-These statements allow a variable to be compared against multiple values.
+A second conditional statement that exists in c, is a \textit{switch statement}.
+This statement allows a variable to be compared against multiple values.
 What is special about the switch statements, is that if matched with one case, the code of all consequential cases will also be executed, until the end of the switch, or until a jump occurs.
@@
 	switch(a){
-		case 5:
-			printf("The parameter is greater than 4.");
 		case 3:
 			printf("The parameter is greater than 2.");
+		case 2:
+			printf("The parameter is greater than 1.");
 		default:
@@
 	}
-
 	return true;
@@
 To generate a counter automaton for a switch statement, we will start by generating a chain for the statements in the cases.
-This is represented by the chain starting from node 4, all the way to node 8, in figure \ref{fig:counter_switch}.
+This is represented by the chain starting from \textit{start\_switch}, all the way to \textit{default}, in Figure \ref{fig:counter_switch}.
 
 After that we need to add the conditional branches that correspond to the different cases.
-A first branch originates from node 2, and can either go to node 2.02 in case the counter is equal to 5, or to 2.08 in case the counter is not.
+A first branch originates from \textit{start\_switch}, and can either go to \textit{case\_3} in case the counter is equal to 3, or to \textit{not\_case\_3} in case the counter is not.
 
-There is a second branch from 2.08 where we can either go to 2.04 in case the counter is equal to 3, or to 2.06 in case the counter is not.
-
-The case starting points are represented by 2.02, 2.04 and 2.06 respectively, and their respective code follows directly beyond these nodes.
+There is a second branch from \textit{not\_case\_3} where we can either go to \textit{case\_2} in case the counter is equal to 2, or to \textit{not\_case\_2} in case the counter is not.
+Finally, from \textit{not\_case\_2} we will always go to the \textit{default} node.
 
@@
 \subsubsection{If statements}
+\label{sec:if}
 Another important construct are the if statements.
-These statements will, just as the loop statements did, require additional nodes to be able to be modeled.
-If statements require a total of 4 nodes to be modeled.
+These statements will, just as the iteration statements did, require additional nodes to be able to be modelled.
+If statements require a total of 4 nodes to be modelled.
 
-First of all, we need a $start\ of\ the\ iteration\ statement$ node, from which the conditions will start.
+First of all, we need a $start\ if$ node, from which the conditions will start.
 
-We will need an $if\ node$ and an $else\ node$ which will both signify the start of the if and possible else segment.
+We will need an $if$ node and an $else$ node which will both signify the start of the if and possible else segment.
 
-After the inner segment, they will all end up at the $end\ of\ the\ iteration\ statement$ from which point they will continue with the next line of code.
+After the inner segment, they will all end up at the $end\ if$ node from which point they will continue with the next line of code.
 
-Consider the test2 function, it contains an if statement, an else if statement and an else statement.
+Consider the test2 function, and the corresponding simplified counter automaton.
 \begin{lstlisting}[style=CStyle]
-bool test2(){
-	int counter = 25;
-	if(counter == 23){
-		counter += 3;
+bool test2(int c){
+	if(c == 1){
+		printf("The counter is equal to 1.");
 	}
-	else if(counter == 24){
-		counter += 2;
-	}
-	else{
-		counter += 1;
+	else if(c == 2){
+		printf("The counter is equal to 2.");
 	}
@@
 
-The program will return a counter automaton as displayed in figure \ref{fig:test2_counter_automaton}.
-The iteration start node of the outer if will be node 3, the if node and else node of the same if will be 3.01 and 3.04 respectively.
-The end node of this if statement will be 3.02.
+The program will return a more in depth version of the simplified counter automaton displayed in Figure \ref{fig:test2_counter_automaton}.
+The first if statement will start from $start\_if\_1$, and end at $end\_if\_1$, the else if will start from $start\_if\_2$, and end at $end\_if\_2$.
 
-The else if will have 6 as a start node, 6.01 and 6.04 will function as if and else nodes respectively. Node 6.02 will signify the end of the else if statement.
-
-Finally, the else statement will start at node 7, since this is no conditional statement, it will just behave as regular code.
-
-\subsubsection{Inequality condtions}
+\subsubsection{Inequality conditions}
+\label{sec:inequality}
 Another statement we will need to support, are inequality conditions.
@@
 
-The following code segment makes use of an if statement which has an equality condition in it. This means that the edge going towards the else node, will have the opposing condition as a label.
+The following code segment makes use of an if statement which has an equality condition in it, being the edge going towards the else node.
 
 \begin{lstlisting}[style=CStyle]
-bool is_ten(int a){
-	int counter = a;
-
-	if(counter == 10){
+bool is_ten(int c){
+	if(c == 10){
 		return true;
@@
 
-When looking at part of the resulting counter automaton in figure \ref{fig:inequality_expression}, we will notice the transitions going from the start of the if statement, being node 4, towards the end of the if statement, being node 4.02.
-There will not be an else node, as there is no else if or else statement.
+When looking at part of a simplified counter automaton in Figure \ref{fig:inequality_expression}, we will notice the transitions going from the \textit{start\_if} node, towards the \textit{end\_if} node.
+There will not be an \textit{else} node, as there is no \textit{else if} or \textit{else} statement.
 
@@
 
-The first transition chain starts with \textit{+1} followed by \textit{\textless =10}, followed by \textit{-1}, which results in the same expression as saying the original counter is strictly smaller than 10.
-The final \textit{-1} is there to reset the counter, so that the counter is back to what it originally was.
+The first transition chain follows the \textit{lte} nodes, which starts with \textit{c += 1} followed by \textit{c \textless =10}, followed by \textit{c -= 1}, which results in the same expression as saying the original counter is strictly smaller than 10.
+The final \textit{c -= 1} is there to reset the counter, so that the counter is back to what it originally was.
 
-The second transition chain start with \textit{-1}, followed by \textit{\textgreater =10}, followed by \textit{+1}. This chain states that the counter must be strictly greater than 10.
+The second transition chain follows the \textit{gte} nodes, with the first transition being \textit{c -= 1}, followed by \textit{c \textgreater =10}, followed by \textit{c += 1}.
+This chain states that the counter must be strictly greater than 10.
 
@@
 \subsubsection{less than and greater than}
-The final additional expressions that will be added to the program described within his paper, are the less than and greater than expressions.
+\label{sec:strict}
+The final addition to the set of supported statements, are the less than and greater than expressions.
 These are needed to model the opposing conditions to greater than or equal and less than or equal respectively.
@@
 \begin{lstlisting}[style=CStyle]
-bool is_ten(int a){
-	int counter = 10;
-	if(counter <= a){
-		if(counter < a){
+bool is_ten(int c){
+	if(c <= 10){
+		if(c < 10){
 			return false;
@@
 The is\_ten code segment models both a less than or equal condition and a less than condition.
-This will mean that the first will need to be opposed with a strictly greater than condition, and the second one with a greater than or equal condition.
+The first condition will need to be opposed with a strictly greater than condition, and the second one with a greater than or equal condition.
 
@@
 \end{figure}
+
+A simplified version of the counter automaton of the is\_ten function can be seen in Figure \ref{fig:less_than_greater_than}.
+This automaton has \textit{start\_if\_1} as the start of the outer if and it has \textit{if\_1} and \textit{end\_if\_1} as respective if and end nodes.
+The inner if has \textit{start\_if\_2} as the start node, \textit{if\_2} as the start of the if segment, and \textit{end\_if\_2} as the end node.
+
+The strict greater than condition, originating from node \textit{start\_if\_1} and ending in node \textit{end\_if\_1}, consists of 3 different transitions.
+The first transitions \textit{c -= 1} and \textit{c \textgreater =10}, test if the counter is strictly greater.
+The third transition \textit{c += 1} is there to make sure that the counter goes back to its original value.
+
+The strict less than condition, originating from node \textit{start\_if\_2} and ending in node \textit{if\_2}, consists of \textit{c += 1} and \textit{c \textless =a} as their first two transitions, which can only be satisfied in case the counter is strictly less than a.
+The final condition \textit{c -= 1} is there to make sure the counter goes back to its original value.
+
+\subsubsection{Counter initialization}
+The counters do not get initialized at the point that they got declared within the code.
+This is a simple improvement that helps to reduce the number of counters.
+Consider the code segment below, in which two different counters are used.
+
+\begin{lstlisting}[style=CStyle]
+bool two_counters(){
+	int c = 0;
+	int c2 = 0;
+	if(c == 2){
+		return false;
+	}
+	else if(c2 == 2){
+		return false;
+	}
+	return true;
+}
+\end{lstlisting}
+The first counter will be initialized just before the if statement gets used.
+The second counter will not be initialized at that point, but will only be initialized just before the second if statement gets used.
+This means that the program will in fact be able to support the given code segment, even though it has two different counters.
+
+\subsubsection{Final overview}
+To give a in depth overview of how the conversion works, we will transform the following code into a counter automaton.
+This code consists of multiple if statements, as well as a loop, it makes use of a single counter value, being \textit{counter}, and two parameters.
+The loop and the final if both use inequality expressions, which are representable in a counter automaton, as was described earlier.
+The first two ifs make use of relational expressions with the $<$ and $>$ operators, which are also representable within a counter automaton.
+The counter is only modified using additions or subtractions with parameters and none of these parameters will ever be modified, which also conforms to the requirements.
+Finally, this function has only integer parameters and a bool return type, which makes us conclude that this entire function is representable in a counter automaton.
+
+\begin{lstlisting}[style=CStyle]
+bool gcm(int a, int b){
+	int counter = a;
+	counter -= b;
+	int i1 = 1;
+	int i2 = 1;
+	while(counter != 0){
+		if(counter > 0){
+			counter -= b;
+			i2 += 1;
+		}
+		else if(counter < 0){
+			counter += a;
+			i1 += 1;
+		}
+		if(counter == 0){
+			printf("the greatest multiple is equal to ");
+			printf("%d * %d = %d * %d = %d.", i1, a, i2, b, i1*a);
+		}
+	}
+	return true;
+}
+\end{lstlisting}
+
+The first line is the function definition, this will just be converted to a node with label 1, representing the first line.
+Since this is the first node added to the counter automaton, it will also be denoted as being the initial node, as can be seen in Figure \ref{fig:final_overview_1}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.2\linewidth]{final_overview_1}
+	\caption{First node in the counter automaton.}
+	\label{fig:final_overview_1}
+\end{figure}
+
+The second line is of interest to the counter machine, as it is a counter modification.
+However it will not directly generate any special counter automaton configuration, as declarations of counters are only displayed as soon as a counter is actually used or modified.
+Since nothing special is generated, it will simply generate a new node representing the current line (being 2), with a transition coming from the last added node before this one, as displayed in Figure \ref{fig:final_overview_2}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\linewidth]{final_overview_2}
+	\caption{Automaton corresponding to the second line of \textit{gcm}.}
+	\label{fig:final_overview_2}
+\end{figure}
+
 \newpage
-Part of the counter automaton of the is\_ten function can be seen in figure \ref{fig:less_than_greater_than}.
-This automaton has 3 as the start of the outer if and it has 3.01 and 3.02 as respective if and end nodes.
-The inner if has 4 as the start node, 4.01 as the start of the if segment, and 4.02 as the end node.
 
-The strict greater than condition, originating from node 3 and ending in node 3.02, consists of 3 different transitions.
-The first transition \textit{-1} and \textit{\textgreater =a}, test if the counter is strictly greater.
-The third transition \textit{+1} is there to make sure that the counter goes back to its original value.
+The third line is an actual modification to the counter, so before we generate any additional nodes regarding the operation specified on this line, we need to add the counter initialization as a \textit{pre} statement for this line, this is represented by the tool by decrementing the current line in steps of 0.01.
+An assignment operation requires three additional nodes, so we will make use of the nodes 2.97, 2.98 and 2.99 to model the assignment functionality, as visualised in Figure \ref{fig:final_overview_3}.
 
-The strict less than condition, originating from node 4 and ending in node 4.01, consists of \textit{+1} and \textit{\textless =a} as their first two conditions, which can only be satisfied in case the counter is strictly less than a.
-The final condition \textit{-1} is there to make sure the counter goes back to its original value.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{final_overview_3}
+	\caption{Counter automaton modelling the initial assignment of the counter.}
+	\label{fig:final_overview_3}
+\end{figure}
+
+The actual operation specified on line three, is a subtraction of the counter by the parameter b, as is modelled in the sub counter automaton in Figure \ref{fig:final_overview_4}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.35\linewidth]{final_overview_4}
+	\caption{Counter automaton modelling the operation on line two.}
+	\label{fig:final_overview_4}
+\end{figure}
+
+Line four and five are both statements that are not of relevance to the counter, and will therefore be simply represented as a sequential chain following from the last added node, being node 3, as can be seen in Figure \ref{fig:final_overview_5}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{final_overview_5}
+	\caption{Counter automaton resulting from line four and five.}
+	\label{fig:final_overview_5}
+\end{figure}
+
+The sixth line defines a while loop.
+This requires us to add several nodes that are all related to the statement on line six.
+The tool will symbolise this by incrementing the current line in steps of 0.01.
+So 4.01 is a node that is used to help model a statement on line four.
+
+First we need two nodes, one symbolising the start of the inner branch, modelled by the node with label 6.02, and one the symbolise the end of the loop, modelled by the node with label 6.01.
+
+The loop ends as soon as the while condition no longer holds, and therefore the transition from start node, 6, to the end of the loop, 6.01 is a condition checking whether or not the condition of the while loop no longer holds, in this case this condition is represented as equality to zero, being the opposite condition to inequality to zero.
+
+The loop continues as long as the condition holds, which is modelled by the sequence going from the start node, 6.01, to the start of the inner loop, being 6.02.
+This configuration models an inequality to zero expression, as described in Section \ref{sec:inequality}, \nameref{sec:inequality}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{final_overview_6}
+	\caption{Counter automaton resulting from line six.}
+	\label{fig:final_overview_6}
+\end{figure}
+
+Lines seven until ten define the first selection statement.
+Selection statements require, as referenced in Section \ref{sec:if}, \nameref{sec:if}, three additional nodes to fully model the needed implementation.
+
+The start of the selection statement, is modelled by the node with label 7.
+From this node, there is a transition going to the node with label 7.03, which symbolises the else branch, and therefore the transition to this node symbolises all counter values for which the if condition would not hold, which in this case are all counters smaller than or equal to zero.
+
+The second transition originating from the start of the selection statement symbolises the cases where the counter satisfies the selection condition.
+The node 7.01 symbolises the start of the inner body of the if statement.
+The chain of transitions starting from 7 and going to node 7.01 model strict greater than, as is explained in Section \ref{sec:strict}, \nameref{sec:strict}.
+
+Finally, there is the \textit{end of if statement} node, being node 7.02. This node symbolises the end of all branches, so if there were any else branches, they will also end in this node.
+
+The inner body is simple and does not need any complex structures to be added.
+The statement on line 8 will result in a transition originating from node 8 with label $-= b$.
+The statement on line 9 has no effect on the counter, and will just be modelled with an empty transition.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{final_overview_7}
+	\caption{Counter automaton resulting from line seven up until line ten.}
+	\label{fig:final_overview_7}
+\end{figure}
+
+The eleventh until fourteenth line models the else branch of the previous selection statement.
+This statement follows the same design principles as the previous selection statement did, and will be inserted in the previous counter automaton, in the place where the current \textit{else\_branch} label is, as can be seen in Figure \ref{fig:final_overview_8}.
+Note that there is no else branch, which was not generated as there are not other \textit{else if} or \textit{else} statements in the code.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{final_overview_8}
+	\caption{Counter automaton resulting from line eleven up until line fourteen.}
+	\label{fig:final_overview_8}
+\end{figure}
+
+The final selection statement can be found on line fifteen until line eighteen.
+This statement includes nothing new, and will simply follow the earlier mentioned specification.
+This selection statement will end with a transition going from the end of the selection, being the node with label 15.02, to the start of the earlier mentioned while statement, being the node with label 6, as can be seen in Figure \ref{fig:final_overview_9}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{final_overview_9}
+	\caption{Counter automaton resulting from line fifteen up until line eighteen.}
+	\label{fig:final_overview_9}
+\end{figure}
+
+After this, all that remains is the return on line twenty.
+This return will simply follow after node 6.01 from the while configuration specified earlier.
+After a return, no nodes will be generated no matter what the kind of these statement is.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.35\linewidth]{final_overview_10}
+	\caption{Counter automaton modelling the return on line twenty.}
+	\label{fig:final_overview_10}
+\end{figure}
+
+The complete overview of the counter automaton can be seen in Figure \ref{fig:final_overview_11}. This is a completely correct counter automaton that is suitable for reachability analysis.
+
+\begin{landscape}
+	\begin{figure}
+		\centering
+		\includegraphics[width=\linewidth]{final_overview_11}
+		\caption{Counter automaton modelling the return on line twenty.}
+		\label{fig:final_overview_11}
+	\end{figure}
+\end{landscape}
+
+\section{Tests}
+The referenced tool has been thoroughly tested using three groups of tests, which are all white box tests. The tests will check the outputted dot and the trace output of the program.
+
+The first group will only test the first loop of the program, and it will check whether or not all nodes get properly generated.
+This purely tests on the generation of nodes, and will not regard any variation in configuration in which these nodes could occur.
+
+The second group will test the cleaner.
+It will test most cases (all common cases) in which folding and substituting should occur as well as the cases where it should not fold anything.
+In this group we will also perform extensive symbol table testing, to check whether or not all values get properly tracked by the symbol table.
+
+The third group will test the full tool.
+It has a few happy day scenarios, where all kinds of statements get tested in multiple configurations.
+As well as a lot of tests where invalid statements occur, where we test whether or not the program is capable of detecting all issues in the code.
 
 \section{Conclusion}
-In this paper we gave a brief description of a program capable of converting a small subset of the c language to counter automata, to be used in later evaluation of reachability.
-
-This subset consists of all functions who contain a maximum of one counter (and preferably exactly one, as reachability analysis without a single counter is considered trivial).
-The operations allowed on the counter are limited to addition and subtraction of parameters and constants, as well as assignment with parameters and constants.
-The conditional evaluations that are allowed are equality, inequality, strict less than, strict greater than, less than or equal and greater than or equal.
-All of these conditions must either be compared to constants or variables.
-Finally, variables can not be altered during the execution of the code and must remain constant.
+In this paper we gave a brief description of a program capable of converting a small subset of the c language to counter automata.
+The resulting automata can be used in reachability analysis within the code.
 
@@
 \section{Future work}
-In a future research, we will attempt to improve the given program, so that it will be more efficient, and most importantly, more useful.
+One of the future aspects that still needs to be worked on, is the precision, efficiency and usefulness of the program.
 The program is too restrictive to be practically usable, and should therefore be expanded to support further c code.
 
-Furthermore, in this same research we will add an expansion to the program, which will allow the evaluation of counter automata, so that actual reachability conclusions can be made.
+Furthermore, before the resulting counter automata have any use, there needs to be an expansion to the tool, which will allow the evaluation of counter automata, so that actual reachability conclusions can be made.
 \printbibliography

### 2020-03-29 Documentation/paper.tex
updated paper

@@
 
-\usepackage{biblatex}
-\addbibresource{bibliography.bib}
+\usepackage[backend=bibtex]{biblatex}
+\addbibresource{bibliography}
 
@@
 
-\title{C Code Conversion to Counter Automata for Reachability Analysis}
+\title{C Code Conversion to One Counter Automata for Reachability Analysis}
 \author{Lars Van Roy\\
@@
 A well known problem in writing code is the reachability of specific lines in said written code.
-It is often impossible to properly determine whether or not a line of code guarded by a conditional statement is going to be reachable in any possible execution of the code\cite{713323, 10.1145/1292316.1292319}.
+It is often impossible to properly determine whether or not a line of code guarded by a conditional statement is going to be reachable in any possible execution of the code \cite{713323, 10.1145/1292316.1292319}.
 Unreachable code is never desired, but is an ever more pressing issue for energy restrained environments such as embedded computer systems \cite{embeddedefficiency}.
 In these systems, we want our execution to be as efficient as possible, and therefore avoid conditions that can never be satisfied or lines that can never be reached at any cost.
-In order to upgrade the efficiency of code that is affected by time constraints, or code in general, a proper reachability analysis would be of great use.
+In order to upgrade the efficiency of code that is affected by time constraints, or code in general, a proper reachability analysis is of great use.
 
-In order to analyse code reachability, we will want to make use of one counter automata.
-The one counter automata are especially interesting as code is easily convertible to counter automata and it has been proven \cite{succintandparametriconecounter, danialandjoel} that reachability is decidable for this type of automata.
-As will be shown in the continuation of this paper, adding the restriction of only allowing a single parametric clock has a big effect on the types of code we can analyse, but is unavoidable, since there is no proof for two counter machines.
-Reachability problems for machines with three or more counters have been proven to be undecidable.
+To analyze reachability in code artificats, we propose a translation from code to one counter automata.
+The one counter automata are especially interesting as code is easily convertible to counter automata and it has been proven that reachability is decidable for this type of automata \cite{succintandparametriconecounter, danialandjoel}.
+As will be shown in the continuation of this paper, adding the restriction of only allowing a single parametric clock has a big effect on the types of code we can analyse, but is unavoidable, since reachability for two counter machines has been proven to be np hard and reachability problems for machines with three or more counters have been proven to be undecidable \cite{FEARNLEY201526}.
 
@@
 
-We will only consider a subset of c programs, which contain at most one counter where a counter is a variable that is used inside a conditional statement.
+We will only consider a subset of c programs, which contain at most one counter.
+Here a counter is a variable that is used inside a conditional statement.
 The program will be able to handle c code with zero counters, but this is considered trivial and will be disregarded for the remainder of this paper.
@@
 
-This proves that there is a definite need for additional research on analysis in code.
-Reachability analysis by using counter automata would not only allow for an expansion of the current reachability analysis as is, but might also allow further expansions based on the results of the counter automaton expansion.
+This shows that there is a definite need for additional research on analysis in code.
+Reachability analysis by using counter automata would allow to detect more cases of dead code than the original dead code analysis techniques could offer.
 
@@
 	\item $\Sigma$ is a finite set of symbols, called the alphabet of the automaton
-	\item $\delta$ is the transition function, $\delta: Q \times \Sigma \rightarrow Q$
-	\item $q_0$ is the initial state, $q_0 \in Q$
-	\item F is a set of states of Q defining the final states, $F \subseteq Q$
+	\item $\delta: Q \times \Sigma \rightarrow Q$ is the transition function
+	\item $q_0 \in Q$ is the initial state
+	\item $F \subseteq Q$ is a set of states of Q defining the final states, 
 \end{itemize}
 
-\subsection{Counter automata}
+\subsection{Parametric counter automata}
 
@@
 
-The counter valuation $c \in \mathbb{N}$ is the value that will be analysed, updated during the evaluation of the automaton.
+The counter valuation $c \in \mathbb{N}$ is the value that will be analysed and updated during the evaluation of the automaton.
 
@@
 
-Finally, we will consider the following set of allowed operations where $P$ is the set of parameters, the $\epsilon$ symbol will be used to represent an empty label.
+Parametric counter automata, as compared to regular counter automata, allow counters to be modified by parameters as well as constants.
+As the counters need to be integers, we will only allow integer type paramters.
+We will consider the following set of allowed operations where $P$ is the set of parameters, the $\epsilon$ symbol will be used to represent an empty label.
 \[
@@
 
-The automata we will consider will be one-counter automata.
+The automata we will consider will be one-counter parametric automata.
 The set $Q$ will contain a state for each line of code.
@@
 \subsubsection{Context-sensitive reduction example: addition folding}
-As described earlier, we do allow additions and subtractions of the form $-x$ and $+x$, where $x \in P$ or $x \in \mathbb{N}$ with $P$ the set of parameters.
-Given that the formation described in Figure \ref{fig:unfolded_addition} occurs in the automaton, we would technically not be allowed to accept this, as this is not directly in the specified format.
+As described earlier, we do allow additions and subtractions of the form $-x, +x, -n$ and $+n$, where $x \in P$ or $n \in \mathbb{N}$ with $P$ the set of parameters.
+Given that the formation, described in Figure \ref{fig:unfolded_addition} occurs in the automaton, we would technically not be allowed to accept this, as this is not directly in the specified format.
 
@@
 We only need to check whether or not we are assigning to a counter, if so, we read the operation used, and the variable that gets assigned.
-Valid counter assignments need to be of the form \textit{c op x} where $c$ is the counter, $op \in $ \textit{\{=, +=, -=\}} and $x \in P$ or $x \in \mathbb{N}$.
+Valid counter assignments need to be of the form \textit{c op x} where $c$ is the counter, $op \in $ \textit{\{=, +=, -=\}} and $x \in P \lor x \in \mathbb{N}$.
 
@@
 In the given example, there is a path where we would remain in node 3.98 indefinitely but since there is at least one path that would take us to node 4, node 4 is still considered reachable.
+
+\subsubsection{Inequality conditions}
+\label{sec:inequality}
+Another statement we will need to support, are inequality conditions.
+If we want our conditional statements to be properly functioning, we will need to be able to generate opposing conditions, but the opposing condition of the equality condition, is the inequality condition, which we can not directly model using the given operations.
+
+The following code segment makes use of an if statement which has an equality condition in it, being the edge going towards the else node.
+
+\begin{lstlisting}[style=CStyle]
+bool is_ten(int c){
+if(c == 10){
+return true;
+}
+
+return false;
+}
+\end{lstlisting}
+
+When looking at part of a simplified counter automaton in Figure \ref{fig:inequality_expression}, we will notice the transitions going from the \textit{start\_if} node, towards the \textit{end\_if} node.
+There will not be an \textit{else} node, as there is no \textit{else if} or \textit{else} statement.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{inequality_expression}
+	\caption{Example of an inequality expression.}
+	\label{fig:inequality_expression}
+\end{figure}
+
+The first transition chain follows the \textit{lte} nodes, which starts with \textit{c += 1} followed by \textit{c \textless =10}, followed by \textit{c -= 1}, which results in the same expression as saying the original counter is strictly smaller than 10.
+The final \textit{c -= 1} is there to reset the counter, so that the counter is back to what it originally was.
+
+The second transition chain follows the \textit{gte} nodes, with the first transition being \textit{c -= 1}, followed by \textit{c \textgreater =10}, followed by \textit{c += 1}.
+This chain states that the counter must be strictly greater than 10.
+
+If either of these can be taken, we can state that the counter must be different to the compared value (in this case 10), as these both express a strict inequality.
+
+\subsubsection{Less than and greater than}
+\label{sec:strict}
+The final addition to the set of supported statements, are the less than and greater than expressions.
+These are needed to model the opposing conditions to greater than or equal and less than or equal respectively.
+
+\begin{lstlisting}[style=CStyle]
+bool is_ten(int c){
+	if(c <= 10){
+		if(c < 10){
+			return false;
+		}
+		return true;
+	}
+	return false;
+}
+\end{lstlisting}
+
+The is\_ten code segment models both a less than or equal condition and a less than condition.
+The first condition will need to be opposed with a strictly greater than condition, and the second one with a greater than or equal condition.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{less_than_greater_than}
+	\caption{Example of a less than expression and a greater than expression.}
+	\label{fig:less_than_greater_than}
+\end{figure}
+
+A simplified version of the counter automaton of the is\_ten function can be seen in Figure \ref{fig:less_than_greater_than}.
+This automaton has \textit{start\_if\_1} as the start of the outer if and it has \textit{if\_1} and \textit{end\_if\_1} as respective if and end nodes.
+The inner if has \textit{start\_if\_2} as the start node, \textit{if\_2} as the start of the if segment, and \textit{end\_if\_2} as the end node.
+
+The strict greater than condition, originating from node \textit{start\_if\_1} and ending in node \textit{end\_if\_1}, consists of 3 different transitions.
+The first transitions \textit{c -= 1} and \textit{c \textgreater =10}, test if the counter is strictly greater.
+The third transition \textit{c += 1} is there to make sure that the counter goes back to its original value.
+
+The strict less than condition, originating from node \textit{start\_if\_2} and ending in node \textit{if\_2}, consists of \textit{c += 1} and \textit{c \textless =a} as their first two transitions, which can only be satisfied in case the counter is strictly less than a.
+The final condition \textit{c -= 1} is there to make sure the counter goes back to its original value.
 
@@
 \end{figure}
+
+\subsubsection{If statements}
+\label{sec:if}
+Another important construct are the if statements.
+These statements will, just as the iteration statements did, require additional nodes to be able to be modelled.
+If statements require a total of 4 nodes to be modelled.
+
+First of all, we need a $start\ if$ node, from which the conditions will start.
+
+We will need an $if$ node and an $else$ node which will both signify the start of the if and possible else segment.
+
+After the inner segment, they will all end up at the $end\ if$ node from which point they will continue with the next line of code.
+
+Consider the test2 function, and the corresponding simplified counter automaton.
+\begin{lstlisting}[style=CStyle]
+bool test2(int c){
+	if(c == 1){
+		printf("The counter is equal to 1.");
+	}
+	else if(c == 2){
+		printf("The counter is equal to 2.");
+	}
+	return true;
+}
+\end{lstlisting}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{test2_counter_automaton}
+	\caption{Example of if statements.}
+	\label{fig:test2_counter_automaton}
+\end{figure}
+
+The program will return a more in depth version of the simplified counter automaton displayed in Figure \ref{fig:test2_counter_automaton}.
+The first if statement will start from $start\_if\_1$, and end at $end\_if\_1$, the else if will start from $start\_if\_2$, and end at $end\_if\_2$.
 
@@
 \end{figure}
-\subsubsection{If statements}
-\label{sec:if}
-Another important construct are the if statements.
-These statements will, just as the iteration statements did, require additional nodes to be able to be modelled.
-If statements require a total of 4 nodes to be modelled.
-
-First of all, we need a $start\ if$ node, from which the conditions will start.
-
-We will need an $if$ node and an $else$ node which will both signify the start of the if and possible else segment.
-
-After the inner segment, they will all end up at the $end\ if$ node from which point they will continue with the next line of code.
-
-Consider the test2 function, and the corresponding simplified counter automaton.
-\begin{lstlisting}[style=CStyle]
-bool test2(int c){
-	if(c == 1){
-		printf("The counter is equal to 1.");
-	}
-	else if(c == 2){
-		printf("The counter is equal to 2.");
-	}
-	return true;
-}
-\end{lstlisting}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\linewidth]{test2_counter_automaton}
-	\caption{Example of if statements.}
-	\label{fig:test2_counter_automaton}
-\end{figure}
-
-The program will return a more in depth version of the simplified counter automaton displayed in Figure \ref{fig:test2_counter_automaton}.
-The first if statement will start from $start\_if\_1$, and end at $end\_if\_1$, the else if will start from $start\_if\_2$, and end at $end\_if\_2$.
-
-\subsubsection{Inequality conditions}
-\label{sec:inequality}
-Another statement we will need to support, are inequality conditions.
-If we want our conditional statements to be properly functioning, we will need to be able to generate opposing conditions, but the opposing condition of the equality condition, is the inequality condition, which we can not directly model using the given operations.
-
-The following code segment makes use of an if statement which has an equality condition in it, being the edge going towards the else node.
-
-\begin{lstlisting}[style=CStyle]
-bool is_ten(int c){
-	if(c == 10){
-		return true;
-	}
-
-	return false;
-}
-\end{lstlisting}
-
-When looking at part of a simplified counter automaton in Figure \ref{fig:inequality_expression}, we will notice the transitions going from the \textit{start\_if} node, towards the \textit{end\_if} node.
-There will not be an \textit{else} node, as there is no \textit{else if} or \textit{else} statement.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\linewidth]{inequality_expression}
-	\caption{Example of an inequality expression.}
-	\label{fig:inequality_expression}
-\end{figure}
-
-The first transition chain follows the \textit{lte} nodes, which starts with \textit{c += 1} followed by \textit{c \textless =10}, followed by \textit{c -= 1}, which results in the same expression as saying the original counter is strictly smaller than 10.
-The final \textit{c -= 1} is there to reset the counter, so that the counter is back to what it originally was.
-
-The second transition chain follows the \textit{gte} nodes, with the first transition being \textit{c -= 1}, followed by \textit{c \textgreater =10}, followed by \textit{c += 1}.
-This chain states that the counter must be strictly greater than 10.
-
-If either of these can be taken, we can state that the counter must be different to the compared value (in this case 10), as these both express a strict inequality.
-
-\subsubsection{less than and greater than}
-\label{sec:strict}
-The final addition to the set of supported statements, are the less than and greater than expressions.
-These are needed to model the opposing conditions to greater than or equal and less than or equal respectively.
-
-\begin{lstlisting}[style=CStyle]
-bool is_ten(int c){
-	if(c <= 10){
-		if(c < 10){
-			return false;
-		}
-		return true;
-	}
-	return false;
-}
-\end{lstlisting}
-
-The is\_ten code segment models both a less than or equal condition and a less than condition.
-The first condition will need to be opposed with a strictly greater than condition, and the second one with a greater than or equal condition.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\linewidth]{less_than_greater_than}
-	\caption{Example of a less than expression and a greater than expression.}
-	\label{fig:less_than_greater_than}
-\end{figure}
-
-A simplified version of the counter automaton of the is\_ten function can be seen in Figure \ref{fig:less_than_greater_than}.
-This automaton has \textit{start\_if\_1} as the start of the outer if and it has \textit{if\_1} and \textit{end\_if\_1} as respective if and end nodes.
-The inner if has \textit{start\_if\_2} as the start node, \textit{if\_2} as the start of the if segment, and \textit{end\_if\_2} as the end node.
-
-The strict greater than condition, originating from node \textit{start\_if\_1} and ending in node \textit{end\_if\_1}, consists of 3 different transitions.
-The first transitions \textit{c -= 1} and \textit{c \textgreater =10}, test if the counter is strictly greater.
-The third transition \textit{c += 1} is there to make sure that the counter goes back to its original value.
-
-The strict less than condition, originating from node \textit{start\_if\_2} and ending in node \textit{if\_2}, consists of \textit{c += 1} and \textit{c \textless =a} as their first two transitions, which can only be satisfied in case the counter is strictly less than a.
-The final condition \textit{c -= 1} is there to make sure the counter goes back to its original value.
 
@@
 This code consists of multiple if statements, as well as a loop, it makes use of a single counter value, being \textit{counter}, and two parameters.
-The loop and the final if both use inequality expressions, which are representable in a counter automaton, as was described earlier.
-The first two ifs make use of relational expressions with the $<$ and $>$ operators, which are also representable within a counter automaton.
-The counter is only modified using additions or subtractions with parameters and none of these parameters will ever be modified, which also conforms to the requirements.
+The loop and the final \textit{if} both use inequality expressions, which are representable in a counter automaton, as was described earlier.
+The first two \textit{ifs} make use of relational expressions with the $<$ and $>$ operators, which are also representable within a counter automaton.
+The counter is only  using additions or subtractions with parameters and none of these parameters will ever be modified, which also conforms to the requirements.
 Finally, this function has only integer parameters and a bool return type, which makes us conclude that this entire function is representable in a counter automaton.
@@
 
-\section{Tests}
-The referenced tool has been thoroughly tested using three groups of tests, which are all white box tests. The tests will check the outputted dot and the trace output of the program.
+\section{Tool Validation}
+To determine the corectness of our tool, we created a test suite consisting out of three groups of tests, which are all white box tests.
+The tests will check the outputted dot and the trace output of the program, against traces and dot files which have been manually generated and verified.
 
@@
 The third group will test the full tool.
-It has a few happy day scenarios, where all kinds of statements get tested in multiple configurations.
-As well as a lot of tests where invalid statements occur, where we test whether or not the program is capable of detecting all issues in the code.
+It will validate the dot file resulting from the cleaner, as well as the dot file(s) resulting from the counter automaton generator.
+It will also evaluate all output regarding the symbol table, and the potential errors of the code validator.
+There are happy day tests where each conditional statement gets tested separately, there are tests where conditional statements get nested and there are tests to see whether we can still evaluate conditional statements with constant conditions.
+Furthermore, there are failure tests that test whether or not we can properly detect incorrect counter types, incorrect parameter types, incorrect number of counters, incorrect conditional operations, incorrect counter modifications and properly detect counters defined in global scopes.
+There are also tests for edge case scenarios, such as returns in every single branch, the cleaner will not be able to detect these, and therefore the generator should be able to stop generating all nodes, once there are no branch that can carry on.
+
+The test coverage was validated using Codecov, which gave a total line coverage of 93\% at the end of development.
+This coverage was used as a metric to determine whether or not there were sufficient tests at each stage of development.
+The remaining 7\% are trivial lines that did not need any testing, such as \textit{\_\_str\_\_} operators.
 
 \section{Conclusion}
-In this paper we gave a brief description of a program capable of converting a small subset of the c language to counter automata.
+In this paper we propose an algorithm for converting a small subset of the c language to counter automata, and discuss its implementation.
 The resulting automata can be used in reachability analysis within the code.
@@
 
-The usability of this program without any further additions is very limited.
-The restrictions enforced on the c code make it fairly useless in more complex situations, where reachability analysis would be far more desired however, it is very effective in case the program is applicable.
-Big conditional statements or a large amount of conditional statements can make the reachability of certain sub segments hard, and with the addition of a reachability checker, they could definitely lead to improvements in coding.
+This proposed algorithm can be used to improve existing static code analysis and will furthermore be usable to solve the halting problem for a subset of c programs.
+It is however only usable in a limited amount of cases, in more complex situations, where reachability analysis would be far more desired, it will most likely not be usable as chances of violated conditions will be high.
+In the situations where it is applicable, big conditional statements or a large amount of conditional statements can make determining the reachability of certain sub segments hard, and with the addition of this algorithm as a reachability checker, it could definitely lead to improvements in coding.
 

### 2020-04-16 Automaton/Automaton.py
added pep8 support

@@ -69,15 +69,19 @@ class Automaton:
         if len(self.nodes) > 0:
 
             for node in self.nodes:
-                result += "Q{0}[label=\"{1}\"];\n\t\t".format(node.index, node.name)
+                result += "Q{0}[label=\"{1}\"];\n\t\t".format(
+                    node.index, node.name)
 
             result += "Qi[style=invis];\n\t\t"
 
-            result += "Qi -> Q{0} [label=\"\"]\n\t\t".format(self.get_index_for_label(self.initial.name))
+            result += "Qi -> Q{0} [label=\"\"]\n\t\t".format(
+                self.get_index_for_label(self.initial.name))
 
             for transition in self.transitions:
-                result += "Q{0} -> Q{1} [label=\"".format(self.get_index_for_label(transition.start),
-                                                          self.get_index_for_label(transition.finish))
+                result += "Q{0} -> Q{1} [label=\"".format(
+                    self.get_index_for_label(
+                        transition.start), self.get_index_for_label(
+                        transition.finish))
                 if transition.label != "":
                     result += "{}".format(transition.label)
                 if transition.label != "" and transition.condition != "":
@@ -108,5 +112,5 @@ class Transition:
         self.condition = condition
 
     def __str__(self):
-        return "from {} to {} with label {} and conditional label {}".format(self.start, self.finish,
-                                                                             self.label, self.condition)
+        return "from {} to {} with label {} and conditional label {}".format(
+            self.start, self.finish, self.label, self.condition)

### 2020-04-16 Automaton/Generator.py

@@ -5,14 +5,16 @@ from math import floor
 import operator
 
 """
-This class is intended to generate all the nodes and transitions that are in the automaton. It will 
-iterate through the tree that was generated during earlier steps. 
+This class is intended to generate all the nodes and transitions that
+are in the automaton. It will iterate through the tree that was generated
+during earlier steps.
 
-We will create one node for each lien in the code. Depending on what the line of code does, there will be
-a label added to the transition originating from the state. It is also possible for a node to have two
-outgoing conditional transition in case the line of code symbolised a conditional statement. Finally
-a transition might have no label whatsoever, in case the line of code had nothing to do with counters,
-as this is al we care about.
+We will create one node for each lien in the code. Depending on what the
+line of code does, there will be a label added to the transition originating
+from the state. It is also possible for a node to have two outgoing
+conditional transition in case the line of code symbolised a conditional
+statement. Finally a transition might have no label whatsoever, in case
+the line of code had nothing to do with counters, as this is al we care about.
 """
 
 
@@ -35,32 +37,35 @@ class Generator:
         # list of all parameters
         self.__parameters = parameters
 
-        # counter for the nr of encountered functions, this will be used as a key to destiniguish between
-        # function scopes
+        # counter for the nr of encountered functions, this will be used
+        # as a key to distinguish between function scopes
         self.__functions_counter = 0
 
-        # this are the lines that have valuable code in it, this list will be used to generate the
-        # set of nodes for the counter automaton
+        # this are the lines that have valuable code in it, this list
+        # will be used to generate the set of nodes for the counter automaton
         self.__lines = list()
         self.__lines.append(0)
 
-        # to support breaking in deeper statements, we need to be able to track which line the last break was, in order
-        # to know which line we should go towards.
+        # to support breaking in deeper statements, we need to be able to
+        # track which line the last break was, in order to know which
+        # line we should go towards.
         self.__for_lines = list()
 
         # during the iteration of the nodes, we can alter this value
-        # every time we reach a new line, this label will be used for the transition, and the
-        # variable will be reset to the empty string
+        # every time we reach a new line, this label will be used for
+        # the transition, and the variable will be reset to the empty string
         self.__next_label = ""
 
         # during the iteration of the nodes, we can alter this  value
-        # every time we reach a new line, this condition will be used for the transition,
-        # and the variable will be reset to the empty string
[…]

### 2020-04-16 SymbolTable/SymbolTable.py

@@ -2,19 +2,23 @@ from math import floor
 
 
 # SymbolTable
-# class that tracks all declared variables, has the scope dictionaries to keep track of the different scopes
-# the current_scope will always refer to the scope we are currently in when tracing a segment of code
-# the symbols themselves will be stored in the symbols dict, each scope will have a separate symbols dict
+# class that tracks all declared variables, has the scope dictionaries
+# to keep track of the different scopes the current_scope will always
+# refer to the scope we are currently in when tracing a segment of code
+# the symbols themselves will be stored in the symbols dict, each scope
+# will have a separate symbols dict
 
 # scope
 # class that defines scope related data
 # has a scope label that defines the name of the scope
-# has a parent reference that references the scope directly above the scope it defines
+# has a parent reference that references the scope directly above the
+# scope it defines
 
 # symbol
 # class that defines the different symbols found in the code
 # a symbol has a type, a name, a value and a counter
-# this counter attribute defines whether or not this variable is referenced in a conditional statement
+# this counter attribute defines whether or not this variable is
+# referenced in a conditional statement
 
 class SymbolTable:
     def __init__(self):
@@ -81,7 +85,8 @@ class SymbolTable:
 
     def add_group_definition(self, group_name, group_type, variables):
         new_definition = GroupDefinition(group_name, group_type, variables)
-        self.__group_definitions[self.__current_scope][group_name] = new_definition
+        self.__group_definitions[self.__current_scope][group_name] = \
+            new_definition
 
     def symbol_exists(self, symbol_name, scope=None):
         if scope is None:
@@ -99,15 +104,28 @@ class SymbolTable:
         if definition_name in self.__group_definitions[scope]:
             return self.__group_definitions[scope][definition_name]
         else:
-            return self.get_group_definition(definition_name, scope.get_parent())
+            return self.get_group_definition(
+                definition_name, scope.get_parent())
 
     def add_group_instance(self, instance_name, instance_type):
-        group_defintion = self.get_group_definition(instance_type.split(" ")[1].replace("*", ""))
-        new_instance = GroupInstance(instance_name, instance_type, group_defintion)
-        self.__group_instances[self.__current_scope][instance_name] = new_instance
+        group_defintion = self.get_group_definition(
+            instance_type.split(" ")[1].replace("*", ""))
+        new_instance = GroupInstance(
[…]

### 2020-04-16 Tree/ASTCleaner.py

@@ -10,17 +10,24 @@ class ASTCleaner:
         self.__root = root
         self.__symbol_table = SymbolTable()
 
-        self.__scope_counter = 0  # this value is used to give scopes unique names
+        # this value is used to give scopes unique names
+        self.__scope_counter = 0
 
-        self.__declarations = dict()  # this dict keeps track of the node that declared a variable
+        # this dict keeps track of the node that declared a variable
+        self.__declarations = dict()
 
-        self.__changes_occurred = True  # this value tracks whether or not something changes in a cycle
+        # this value tracks whether or not something changes in a cycle
+        self.__changes_occurred = True
 
-        self.__queued_for_pop = list()  # list that keeps track of which nodes are ready to get popped
+        # list that keeps track of which nodes are ready to get popped
+        self.__queued_for_pop = list()
 
-        self.__entered_branch = False  # this value checks if inside branch statement, if so, condition => counter
+        # this value checks if inside branch statement, if so, condition =>
+        # counter
+        self.__entered_branch = False
 
-        self.__assigning_to_counter = False  # track whether or not we are assigning to a counter
+        # track whether or not we are assigning to a counter
+        self.__assigning_to_counter = False
 
         AbstractSyntaxTree.node_count = 0
 
@@ -41,13 +48,16 @@ class ASTCleaner:
             for scope in self.__symbol_table.get_scopes():
                 if "for" not in scope:
                     for symbol in self.__symbol_table.get_symbols(scope):
-                        if not self.__symbol_table.is_used(symbol, scope) and symbol in self.__declarations \
-                                and self.__declarations[symbol] not in self.__queued_for_pop and not \
+                        if not self.__symbol_table.is_used(symbol, scope) and \
+                                symbol in self.__declarations \
+                                and self.__declarations[symbol] not in \
+                                self.__queued_for_pop and not \
                                 self.__symbol_table.is_counter(symbol, scope):
                             self.remove_node(self.__declarations[symbol])
                             removed_node = self.__declarations[symbol]
 
-                            # ensure all instances of structs, .. get removed, as these can refer to the same node
+                            # ensure all instances of structs, .. get removed,
+                            # as these can refer to the same node
                             staged_for_pop = list()
                             for temp in self.__declarations:
                                 if self.__declarations[temp] == removed_node:
@@ -57,8 +67,10 @@ class ASTCleaner:
                                 self.__declarations.pop(temp)
 
[…]

### 2020-04-16 Tree/ASTConstructor.py

@@ -57,7 +57,8 @@ class ASTConstructor(CListener):
     def exitTranslationUnit(self, ctx: CParser.TranslationUnitContext):
         pass
 
-    def enterExternalDeclaration(self, ctx: CParser.ExternalDeclarationContext):
+    def enterExternalDeclaration(
+            self, ctx: CParser.ExternalDeclarationContext):
         pass
 
     def exitExternalDeclaration(self, ctx: CParser.ExternalDeclarationContext):
@@ -85,7 +86,9 @@ class ASTConstructor(CListener):
             new_node = self.grow_tree("Val = {}".format(ctx.Constant()), ctx)
             self.__node_stack.insert(0, new_node)
         elif ctx.BoolConstant():
-            new_node = self.grow_tree("Val = {}".format(ctx.BoolConstant()), ctx)
+            new_node = self.grow_tree(
+                "Val = {}".format(
+                    ctx.BoolConstant()), ctx)
             self.__node_stack.insert(0, new_node)
         elif ctx.StringLiteral():
             result = "Val = "
@@ -100,10 +103,10 @@ class ASTConstructor(CListener):
 
     def exitPrimaryExpression(self, ctx: CParser.PrimaryExpressionContext):
         top_node = self.__node_stack[0]
-        if type(top_node.get_ctx()) == CParser.PrimaryExpressionContext and (ctx.Identifier() or ctx.Constant()
-                                                                             or ctx.StringLiteral() or
-                                                                             (ctx.LeftParen() and ctx.expression())
-                                                                             or ctx.BoolConstant()):
+        if isinstance(
+            top_node.get_ctx(), CParser.PrimaryExpressionContext) and (
+            ctx.Identifier() or ctx.Constant() or ctx.StringLiteral() or (
+                ctx.LeftParen() and ctx.expression()) or ctx.BoolConstant()):
             if ctx.LeftParen() and ctx.expression():
                 self.grow_on_index("(", ctx, 0)
                 self.grow_on_index(")", ctx, -1)
@@ -137,8 +140,11 @@ class ASTConstructor(CListener):
 
     def exitPostfixExpression(self, ctx: CParser.PostfixExpressionContext):
         top_node = self.__node_stack[0]
-        if type(top_node.get_ctx()) == CParser.PostfixExpressionContext and not ctx.primaryExpression():
[…]

### 2020-04-16 Tree/ASTValidator.py

@@ -1,11 +1,13 @@
 import itertools
 
 """
-This class is intended to be called on a (be it cleaned or not) syntax tree. The class will iterator over the tree
-inside the validate function. on it' s path it will keep track of all variables (esp counters) and from where to where
-these variables are used. In the end it will return the functions that were found in the ast and whether or not these
-functions are conforming to the given conditions. For now all functions need to have a boolean return type and they
-need to have one counter (0 counters is considered trivial).
+This class is intended to be called on a (be it cleaned or not) syntax tree.
+The class will iterator over the tree inside the validate function. on it' s
+path it will keep track of all variables (esp counters) and from where to where
+these variables are used. In the end it will return the functions that were
+found in the ast and whether or not these functions are conforming to the
+given conditions. For now all functions need to have a boolean return type
+and they need to have one counter (0 counters is considered trivial).
 """
 
 
@@ -13,7 +15,8 @@ class ASTValidator:
     def __init__(self, root, symbol_table):
         self.__root = root
 
-        # counters used to generate unique names for functions, nodes and loop scopes
+        # counters used to generate unique names for functions, nodes and loop
+        # scopes
         self.__functions_counter = 0
         self.__node_counter = 0
         self.__loop_counter = 0
@@ -24,37 +27,67 @@ class ASTValidator:
         # symbol table object that keeps track of all variables
         self.__symbol_table = symbol_table
 
-        # dictionary that keeps track of the counters and parameters part of each function scope
+        # dictionary that keeps track of the counters and parameters part of
+        # each function scope
         self.__counters = dict()
         self.__parameters = dict()
 
         # dictionary that keeps track of all scopes
         self.__scopes = dict()
 
-        # this variables will be set to true in case we are assigning to a counter or function parameter
-        # the target assignment will keep track of what variable we are currently assigning too
+        # this variables will be set to true in case we are
+        # assigning to a counter or function parameter
+        # the target assignment will keep track of what variable we are
+        # currently assigning too
         self.__counter_assignment_operation = False
         self.__target_assignment_variable = list()
 
-        # this variable will be set to true in case we are evaluating a condition in a iteration or evaluation statement
+        # this variable will be set to true in case we are evaluating a
+        # condition in a iteration or evaluation statement
         self.__constrained_conditional_statement = False
 
-        # keep track of all nodes that defined unsupported counter operations (all operations except addition and
+        # keep track of all nodes that defined unsupported counter
+        # operations (all operations except addition and
         # assignment)
[…]

### 2020-04-16 Tree/AbstractSyntaxTree.py

@@ -67,7 +67,9 @@ class AbstractSyntaxTree:
                 break
 
         for lower_limit in reversed(backslashes):
-            if label[lower_limit-1] != "\\" and label[lower_limit+1] != "\\":
+            if label[lower_limit -
+                     1] != "\\" and label[lower_limit +
+                                          1] != "\\":
                 label = label[:lower_limit] + "\\" + label[lower_limit:]
 
         quotation_marks = list()
@@ -80,7 +82,7 @@ class AbstractSyntaxTree:
                 break
 
         for lower_limit in reversed(quotation_marks):
-            if label[lower_limit-1] != '\\':
+            if label[lower_limit - 1] != '\\':
                 label = label[:lower_limit] + "\\" + label[lower_limit:]
 
         self.__label = label
@@ -89,7 +91,8 @@ class AbstractSyntaxTree:
 
         for child in self.__children:
             AbstractSyntaxTree.node_count += 1
-            result += "Q{0} -> Q{1}\n\t\t".format(node_id, AbstractSyntaxTree.node_count)
+            result += "Q{0} -> Q{1}\n\t\t".\
+                format(node_id, AbstractSyntaxTree.node_count)
             result += child.to_dot()
 
         if not self.__parent and self.__label == "CompilationUnit":
